## Landings by species (tons) and countries in 21 (Northwest Atlantic) area.

```{r, results = "asis",echo = FALSE, warning = FALSE, message = FALSE, eval = T}

# table314 <- clOrg[Year %in% c(2014:2021) & Area==21,]
# table314$Stock[which(table314$Stock == '')] <- 'Other'
# table314$Division[which(is.na(table314$Division))] <- '21.3'
#
# table314 <- table314[, .(LandingWeight_ton = round(sum(LandingWeight_ton, na.rm = TRUE))),
#          by=c('Division', 'FlagCountry', 'Year')]


clOrg %>%
  filter(CLyear %in% params$allYears & substr(CLarea,1,2)=='21') %>%
  group_by(SpeciesLaName, CLvesselFlagCountry, CLyear) %>%
  summarise(LandingWeight_ton = round(sum(CLscientificWeight_ton, na.rm = TRUE))) %>%
  ungroup() %>%
  # replace 0 with NA where the record were submitted - data not porivded because of confidentiality reasons
  mutate(LandingWeight_ton = as.character(LandingWeight_ton)) %>%
  mutate(LandingWeight_ton =  ifelse(is.na(LandingWeight_ton), 'NA', LandingWeight_ton)) %>%
  mutate(LandingWeight_ton = ifelse(LandingWeight_ton == '0', '<1', LandingWeight_ton)) %>%
  pivot_wider(names_from = CLyear, values_from = LandingWeight_ton) -> table314

# Rearrange the columns
#table314 <- table314[,c(1,2,10,11,3,4,5,6,7,8,9)]
#table314$Stock[which(table314$Stock == '')] <- 'Other'

kable(table314)
write_csv(table314, paste(table_dir,'NAFO_landings_country_species.csv',
                      sep = ""))

```

\newpage
## Landings by species (tons), divisions and countries in 21 (Northwest Atlantic) area.

```{r, results = "asis",echo = FALSE, warning = FALSE, message = FALSE, eval = T}

clOrg %>%
# filter((Subpolygon!='Angola' | is.na(Subpolygon) )) %>%
  filter(CLyear %in% params$allYears & substr(CLarea,1,2)=='21') %>%
  group_by(SpeciesLaName, AreaMap, CLvesselFlagCountry, CLyear) %>%
  summarise(LandingWeight_ton = round(sum(CLscientificWeight_ton, na.rm = TRUE))) %>%
  ungroup() %>%
  # replace 0 with NA where the record were submitted - data not porivded because of confidentiality reasons
  mutate(LandingWeight_ton = as.character(LandingWeight_ton)) %>%
  mutate(LandingWeight_ton =  ifelse(is.na(LandingWeight_ton), 'NA', LandingWeight_ton)) %>%
  mutate(LandingWeight_ton = ifelse(LandingWeight_ton == '0', '<1', LandingWeight_ton)) %>%
  pivot_wider(names_from = CLyear, values_from = LandingWeight_ton) %>%
  # filter(Area == 21) %>%
    rename(Country = CLvesselFlagCountry)-> table314

# Rearrange the columns
# table314 <- table314[,c(1,2,3,11,12,4,5,6,7,8,9,10)]
# table314$Division[which(is.na(table314$Division))] <- '21.3'
# table314$Stock[which(table314$Stock == '')] <- 'Other'

kable(table314)
write_csv(table314, paste(table_dir,'NAFO_landings_country_area_species.csv',
                      sep = ""))

```


\newpage
## Landings by stocks (tons) in 21 (Northwest Atlantic) area.

```{r, results = "asis",echo = FALSE, warning = FALSE, message = FALSE, eval = T}
clOrg %>%
  filter(CLyear %in% params$allYears & substr(CLarea,1,2)=='21') %>%
  inner_join(NAFOstocksRef, by = c("SpeciesLaName","CLarea")) %>% 
  mutate(Stock = paste(SpeciesLaName, Stock, sep = " ")) %>% 
  group_by(Stock, CLyear) %>%
  summarise(LandingWeight_ton = round(sum(CLscientificWeight_ton, na.rm = TRUE))) %>%
  ungroup() %>%
  # replace 0 with NA where the record were submitted - data not porivded because of confidentiality reasons
  mutate(LandingWeight_ton = as.character(LandingWeight_ton)) %>%
  mutate(LandingWeight_ton =  ifelse(is.na(LandingWeight_ton), 'NA', LandingWeight_ton)) %>%
  mutate(LandingWeight_ton = ifelse(LandingWeight_ton == '0', '<1', LandingWeight_ton)) %>%
  pivot_wider(names_from = CLyear, values_from = LandingWeight_ton) -> tableNAFO1

kable(tableNAFO1)
write_csv(tableNAFO1, paste(table_dir,'NAFO_landings_stock.csv',
                      sep = ""))

```


\newpage
## Landings by stocks (tons) and countries in 21 (Northwest Atlantic) area.

```{r, results = "asis",echo = FALSE, warning = FALSE, message = FALSE, eval = T}
clOrg %>%
  filter(CLyear %in% params$allYears & substr(CLarea,1,2)=='21') %>%
  inner_join(NAFOstocksRef, by = c("SpeciesLaName","CLarea")) %>% 
  mutate(Stock = paste(SpeciesLaName, Stock, sep = " ")) %>% 
  group_by(Stock, CLvesselFlagCountry, CLyear) %>%
  summarise(LandingWeight_ton = round(sum(CLscientificWeight_ton, na.rm = TRUE))) %>%
  ungroup() %>%
  # replace 0 with NA where the record were submitted - data not porivded because of confidentiality reasons
  mutate(LandingWeight_ton = as.character(LandingWeight_ton)) %>%
  mutate(LandingWeight_ton =  ifelse(is.na(LandingWeight_ton), 'NA', LandingWeight_ton)) %>%
  mutate(LandingWeight_ton = ifelse(LandingWeight_ton == '0', '<1', LandingWeight_ton)) %>%
  pivot_wider(names_from = CLyear, values_from = LandingWeight_ton) -> tableNAFO2

# Rearrange the columns
#table314 <- table314[,c(1,2,10,11,3,4,5,6,7,8,9)]
#table314$Stock[which(table314$Stock == '')] <- 'Other'

kable(tableNAFO2)
write_csv(tableNAFO2, paste(table_dir,'NAFO_landings_stock_country.csv',
                      sep = ""))

```

\newpage
## Landings by stocks (tons), divisions and countries in 21 (Northwest Atlantic) area.

```{r, results = "asis",echo = FALSE, warning = FALSE, message = FALSE, eval = T}

clOrg %>%
# filter((Subpolygon!='Angola' | is.na(Subpolygon) )) %>%
  inner_join(NAFOstocksRef, by = c("SpeciesLaName","CLarea")) %>% 
  mutate(Stock = paste(SpeciesLaName, Stock, sep = " ")) %>% 
  group_by(Stock, AreaMap, CLvesselFlagCountry, CLyear) %>%
  summarise(LandingWeight_ton = round(sum(CLscientificWeight_ton, na.rm = TRUE))) %>%
  ungroup() %>%
  # replace 0 with NA where the record were submitted - data not porivded because of confidentiality reasons
  mutate(LandingWeight_ton = as.character(LandingWeight_ton)) %>%
  mutate(LandingWeight_ton =  ifelse(is.na(LandingWeight_ton), 'NA', LandingWeight_ton)) %>%
  mutate(LandingWeight_ton = ifelse(LandingWeight_ton == '0', '<1', LandingWeight_ton)) %>%
  pivot_wider(names_from = CLyear, values_from = LandingWeight_ton) %>%
  # filter(Area == 21) %>%
    rename(Country = CLvesselFlagCountry)-> table314

# Rearrange the columns
# table314 <- table314[,c(1,2,3,11,12,4,5,6,7,8,9,10)]
# table314$Division[which(is.na(table314$Division))] <- '21.3'
# table314$Stock[which(table314$Stock == '')] <- 'Other'

kable(table314)
write_csv(table314, paste(table_dir,'NAFO_landings_stock_area_country.csv',
                      sep = ""))

```


\newpage

## Effort (fishing days) in area 21 (Northwest Atlantic) by country

```{r, results = "asis",echo = FALSE, warning = FALSE, message = FALSE, eval = T}

 ceOrg %>%
   filter(CEyear %in% params$allYears) %>%
   filter(substr(CEarea,1,2) == "21") %>%
   filter(is.na(CEscientificDaysAtSea)) -> brakDanych

 ceOrg %>%
 # filter((Subpolygon!='Angola' | is.na(Subpolygon) )) %>%
   filter(CEyear %in% params$allYears)  %>%
   filter(substr(CEarea,1,2) == "21") %>%
   group_by(CEvesselFlagCountry, AreaMap, CEyear ) %>%
   summarise(FishingDays = sum(CEscientificDaysAtSea, na.rm = TRUE)) %>%
   ungroup() %>%
# replace 0 with NA where the record were submitted - data not porivded because of confidentiality reasons
   mutate(FishingDays = as.character(FishingDays)) %>%
   mutate(FishingDays =  ifelse(FishingDays=='0' | is.na(FishingDays) , 'NA', FishingDays)) %>%
   pivot_wider(names_from = CEyear, values_from = c(FishingDays))%>%
 # filter(Area %in% c(41, 47, 21, 88, 51, 58, 48, 57)) %>%
   rename(Country = CEvesselFlagCountry)-> table313

 # table313 <- table313[,c(1,2,11,3,4,5,6,7,8,9,10)]
 # table313$Division[which(is.na(table313$Division))] <- '21.3'

 kable(table313)
 write_csv(table313, paste(table_dir,'NAFO_effort_area_country.csv',
                      sep = ""))

 if(nrow(brakDanych)>0){
   cat('Number of records with missing FishingDays per FlagCountry' )

   ceOrg %>%
   filter(CEyear %in% params$allYears) %>%
   filter(substr(CEarea,1,2) == "21") %>%
   filter(is.na(CEscientificDaysAtSea)) %>% # KWDays FishingActivityCategoryEuropeanLvl6
   group_by(CEvesselFlagCountry) %>%
   summarise(numRecords = n())-> tabela

 kable(tabela)

 }else{

   cat('No missing data for Fishing Days')

 }

```
