## Effort by country {.tabset}
### number of trips
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6, fig.cap='**Figure 89:** Number of trips by Country.'}

barplot(data = ce, 
      x = "CEvesselFlagCountry",
      y = "CEnumberOfDominantTrips",
     # title = "Number of trips by Country",
      ylab = "Sum of Number of trips" )


```

### days at sea
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6, fig.cap='**Figure 90:** Days at Sea by Country.'}

barplot(data = ce, 
      x = "CEvesselFlagCountry",
      y = "CEscientificDaysAtSea",
     # title = "Days at Sea by Country",
      ylab = "Sum of days at Sea" )


```

### KW-days
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6, fig.cap='**Figure 91:** KW-Days * 1000 by Country.'}

barplot(data = ce, 
      x = "CEvesselFlagCountry",
      y = "CEscientifickWDaysAtSea_1000x",
     # title = "KW-Days*1000 at Sea by Country",
      ylab = "Sum of KW-Days*1000 at Sea")


```

### GT-days
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6, fig.cap='**Figure 92:** GT-Days * 1000 by Country.'}

barplot(data = ce, 
      x = "CEvesselFlagCountry",
      y = "CEgTDaysAtSea_1000x",
      #title = "GT-Days*1000 at Sea by Country",
      ylab = "Sum of GT-Days*1000 at Sea")


```

## Effort by fleet {.tabset}
### number of trips
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6, fig.cap='**Figure 93:** Number of trips by Fleet'}
sub_ce_top<- ce%>%
  group_by(CEyear, FlagCountry_Loa) %>%
  summarise(CEnumberOfDominantTrips = sum(CEnumberOfDominantTrips))%>%
  top_n(20, wt=CEnumberOfDominantTrips)
barplot(data = sub_ce_top, 
      x = "FlagCountry_Loa",
      y = "CEnumberOfDominantTrips",
     # title = "Number of trips by Fleet",
      ylab = "Sum of number of trips")
```

## Effort by area{.tabset}
### area
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6, fig.cap='**Figure 94:** Number of trips by Area.'}

barplot(data = ce, 
      x = "Area",
      y = "CEnumberOfDominantTrips",
      title = "Number of trips by Area",
      ylab = "Sum of Number of trips")

```

### area and country
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6, fig.cap='**Figure 96:** Number of trips by Country and Area.'}

barplot(data = ce,
      x = "Area",
      y = "CEnumberOfDominantTrips",
      group = "CEvesselFlagCountry",
      groupNiceName = 'Vessel flag country',
     # title = "Number of trips by Area and Country",
      ylab = "Proportion of Number of trips",
      asPct = T )

```

### area - map
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6, fig.cap='**Figure 97**: Sum of Trips Number by Area (all)'}
# do we need information on for how many rows(%) there was a missing CLscientificWeight_ton? <-------------------------- to do

# data prep
ce %>%
  mutate(AreaMap=substr(Area,1,2))%>%
  group_by(CEyear, AreaMap) %>% 
  summarise(CEnumberOfDominantTrips = sum(CEnumberOfDominantTrips)) %>%
  mutate(pr= CEnumberOfDominantTrips/sum(CEnumberOfDominantTrips, na.rm = TRUE)*100,
         analysis_type = 'sum',
         type_of_threshold = 'none',
         value_of_threshold = NA)-> df

# map
result = choroplethMap_func2(
  df,
  var_name = 'CEnumberOfDominantTrips',
  var_spatial_name = 'AreaMap',
  facet_name = 'CEyear',
  spatial_dataset_name = 'FAOshp',
  spatial_dataset_var_name = 'Area',
  spatial_dataset_labels = FALSE,
  saveResults = FALSE,
  outputPath,
  extraShp_name = NA,
  displayInR = TRUE,
  var_name_new = "Trips Number",
  addToTitle = NA
)
result[[1]]
```

## Effort by metier{.tabset}
### metier lvl5
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=7,fig.height=7, fig.cap='**Figure 98**: Number of trips by Metier Lvl5.'}
#data prep
sub_ce_top <- ce%>%
  mutate(CEmetier5 = substr(CEmetier6, 1, 7))%>%
  group_by(CEyear, CEmetier5) %>%
  summarise(CEnumberOfDominantTrips = sum(CEnumberOfDominantTrips)) %>%
  top_n(20)

barplot(data = sub_ce_top,
      x = "CEmetier5",
      y = "CEnumberOfDominantTrips",
     # title = "Number of trips by Metier Lvl5",
      ylab = "Sum of Number of trips")
```

### metier lvl5 and country
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=7,fig.height=7, fig.cap='**Figure 99**: Number of trips by Metier Lvl5 and Country.'}
#data prep
sub_ce_2 <- ce%>%
    mutate(CEmetier5 = substr(CEmetier6, 1, 7))%>%
  group_by(CEyear, CEmetier5, CEvesselFlagCountry) %>%
  summarise(CEnumberOfDominantTrips2 = sum(CEnumberOfDominantTrips))

sub_ce_top$Top <- "TOP"
sub_ce_2_top <- left_join(sub_ce_2,sub_ce_top,by="CEmetier5")

sub_ce_2_top <- sub_ce_2_top %>%
  filter(Top=='TOP')

barplot(data = sub_ce_2_top, 
      x = "CEmetier5",
      y = "CEnumberOfDominantTrips2",
      group = "CEvesselFlagCountry",
      groupNiceName = 'Vessel flag country',
      title = "Number of trips by Metier Lvl5 and Country",
      ylab = "Proportion of Number of trips",
      asPct = T)

```

### metier lvl6
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=7,fig.height=7, fig.cap='**Figure 100**: Number of trips by Metier Lvl6.'}
#data prep
sub_ce_top <- ce%>%
  group_by(CEyear, CEmetier6) %>%
  summarise(CEnumberOfDominantTrips = sum(CEnumberOfDominantTrips)) %>%
  top_n(20)

barplot(data = sub_ce_top,
      x = "CEmetier6",
      y = "CEnumberOfDominantTrips",
      title = "Number of trips by Metier Lvl5",
      ylab = "Sum of Number of trips")
```

### metier lvl6 and country
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=7,fig.height=7, fig.cap='**Figure 101**: Number of trips by Metier Lvl6 and Country.'}
#data prep
sub_ce_2 <- ce%>%
  group_by(CEyear, CEmetier6, CEvesselFlagCountry) %>%
  summarise(CEnumberOfDominantTrips2 = sum(CEnumberOfDominantTrips))

sub_ce_top$Top <- "TOP"
sub_ce_2_top <- left_join(sub_ce_2,sub_ce_top,by="CEmetier6")

sub_ce_2_top <- sub_ce_2_top %>%
  filter(Top=='TOP')

barplot(data = sub_ce_2_top, 
      x = "CEmetier6",
      y = "CEnumberOfDominantTrips2",
      group = "CEvesselFlagCountry",
      groupNiceName = 'Vessel flag country',
      title = "Number of trips by Metier Lvl6 and Country",
      ylab = "Proportion of Number of trips",
      asPct = T)

```

## Effort by harbour{.tabset}

### harbour
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=7,fig.height=7, fig.cap='**Figure 102**: Number of trips in the 20 main Harbours.'}
#data prep
sub_ce_top <- ce%>%
  group_by(CEyear, CElandingLocation) %>%
  summarise(CEnumberOfDominantTrips = sum(CEnumberOfDominantTrips)) %>%
  top_n(20)

barplot(data = sub_ce_top,
      x = "CElandingLocation",
      y = "CEnumberOfDominantTrips",
      #title = "Number of trips by Harbours",
      ylab = "Sum of Number of trips")
```

### map - harbour
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6, fig.cap='**Figure 103**: Sum of Trips Number by Harbour (all). Displaying top 20 Harbours.'}
sub_ce_top %>%  mutate(
         analysis_type = 'sum',
         type_of_threshold = 'none',
         value_of_threshold = NA
       )-> df

if(nrow(df)==0){
  c('No data')
}else{
result <- pointsMap_func2(df,
                          title = '',
                          var_name = 'CEnumberOfDominantTrips',
                          facet_name = 'CEyear',
                          var_spatial_name = 'CElandingLocation',
                          spatial_dataset_name = 'Harbours',
                          spatial_dataset_var_name = 'Harbour',
                          plot_labels = TRUE,
                          saveResults = FALSE,
                          #outputPath,
                          Catch_group_name = NA,
                          extraShp_name = 'Divisionshp',
                          newVarName = NA,
                          addToTitle = NA
                          #,
                          #RCGregion = 'BA'
                         )

  
result
}

```
## Effort abroad
Plot below shows the Trips Number between CEvesselFlagCountry (left) and Harbour Country * (right).
```{r , echo = FALSE, warning = FALSE, message = FALSE,results = "asis", dpi=100, fig.width=9,fig.height=9, fig.cap = '**Figure 104**:River plot of Trips Number between vessel Flag Country (left), Harbour Country (right). Width of line is proportional to number of trips. Harbour Country is the Country from the CElandingLocation.'}
    
ce %>%
  group_by(CEyear, HarbourCountry2, CEvesselFlagCountry) %>%
  summarise(CEnumberOfDominantTrips = sum(CEnumberOfDominantTrips)) %>% 
 filter(CEnumberOfDominantTrips!=0) -> ce_river

result<-func_riverplot(df = ce_river,
                       left = 'CEvesselFlagCountry',
                       right = 'HarbourCountry2',
                       threesteps = FALSE,
                       value = 'CEnumberOfDominantTrips')
result
```