## Overall landings
### Landings by country
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6,fig.cap = '**Figure 1**:Landings by country.'}

barplot(data = cl, 
      x = "CLvesselFlagCountry",
      y = "CLscientificWeight_1000ton",
     #title = paste('Landings by country, ', params$year, sep = ''),
      ylab = "Sum of Landings (1000 t)",
      col_cou = T
      )
```


### Landings by species {.tabset}
#### species
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6, fig.cap='**Figure 2**: Landings of the 20 main Species.'}

sub_cl<- cl%>%
  group_by(CLyear,SpeciesLaName) %>%
  summarise(CLscientificWeight_1000ton = sum(CLscientificWeight_1000ton)) %>%
  top_n(20, wt=CLscientificWeight_1000ton)
barplot(data = sub_cl, 
      x = "SpeciesLaName",
      y = "CLscientificWeight_1000ton",
      #title = "Landings (1000 t) by Species",
      ylab = "Sum of Landings (1000 t)")

```

#### species and country
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6, fig.cap='**Figure 3**: Proportion of countries landings per main species landed (top 20).'}

sub_cl_2<- cl%>%
  group_by(CLyear, SpeciesLaName, CLvesselFlagCountry) %>%
  summarise(CLscientificWeight_1000ton2 = sum(CLscientificWeight_1000ton))

sub_cl_top <- sub_cl %>%
  arrange(desc(CLscientificWeight_1000ton)) %>%
  top_n(20)

sub_cl_top$Top <- "TOP"
sub_cl_2_top <- left_join(sub_cl_2,sub_cl_top,by="SpeciesLaName")

sub_cl_2_top <- sub_cl_2_top %>%
  filter(Top=='TOP')

barplot(data = sub_cl_2_top,
      x = "SpeciesLaName",
      y = "CLscientificWeight_1000ton2",
      group = "CLvesselFlagCountry",
      groupNiceName = 'Vessel flag country',
      #title = "Landings (1000 t) by Species and Country",
      ylab = "Proportion of Landings (%)",
      asPct = T)
```

### Landings by species catch group {.tabset}
#### species catch group
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6, fig.cap='**Figure 4**: Sum of the landings by species catch group.'}

barplot(data = cl, 
      x = "CatchGroup",
      y = "CLscientificWeight_1000ton",
      #title = "Landings (1000 t) by Species Catch Group",
      ylab = "Landings (1000 t)")
```

#### species catch group and country
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6, fig.cap='**Figure 5**: Proportion of countries landings by species catch group.'}

barplot(data = cl, 
      x = "CatchGroup",
      y = "CLscientificWeight_1000ton",
      group = "CLvesselFlagCountry",
      groupNiceName = 'Vessel flag country',
      #title = "Landings by Species Catch Group and Country",
      ylab = "Proportion of Landings (%)",
      asPct = T)

```


### Landings by fleet
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6, fig.cap='**Figure 6**: Proportion of countries landings by vessel length category.'}
barplot(data = cl, 
      x = "CLvesselLengthCategory",
      y = "CLscientificWeight_1000ton",
      group = "CLvesselFlagCountry",
      groupNiceName = 'Vessel flag country',
      #title = "Landings by Vessel Length Category and Country",
      ylab = "Proportion of Landings (%)",
      asPct = T)

```

### Landings by area {.tabset}
#### Area
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6, fig.cap='**Figure 7**: Landings (all species) distribution by area.'}
barplot(data = cl%>%
          mutate(Area = substr(CLarea,1,2)), 
      x = "Area",
      y = "CLscientificWeight_1000ton",
      #title = "Landings (1000 t) by Area",
      ylab = "Sum of Landings (1000 t)")

```

#### area and country
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6, fig.cap='**Figure 8**: Proportion of countries total landings by area.'}
barplot(data = cl%>%
          mutate(Area = substr(CLarea,1,2)), 
      x = "Area",
      y = "CLscientificWeight_1000ton",
      group = "CLvesselFlagCountry",
      groupNiceName = 'Vessel flag country',
      #title = "Landings (1000 t) by Area and Country",
      ylab = "Proportion of Landings (%)",
      asPct = T)

```

#### country and area
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6, fig.cap='**Figure 9**: Proportion of the total landings per area, by country.'}
barplot(data = cl%>%
          mutate(Area = substr(CLarea,1,2)), 
      x = "CLvesselFlagCountry",
      y = "CLscientificWeight_1000ton",
      group = "Area",
      #title = "Landings (1000 t) by Country and Area",
      ylab = "Proportion of Landings (%)",
      asPct = T)


```


#### map - area
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6, fig.cap='**Figure 10**: Sum of landings(1000 t) by Area(all)'}
# do we need information on for how many rows(%) there was a missing CLscientificWeight_ton? <-------------------------- to do

# data prep
cl %>%
  mutate(AreaMap=substr(AreaMap,1,2))%>%
  group_by(CLyear, AreaMap) %>%
  summarise(CLscientificWeight_ton = sum(CLscientificWeight_ton)) %>%
  mutate(pr= CLscientificWeight_ton/sum(CLscientificWeight_ton, na.rm = TRUE)*100,
         analysis_type = 'sum',
         type_of_threshold = 'none',
         value_of_threshold = NA)-> df

# map
result = choroplethMap_func2(
  df,
  var_name = 'CLscientificWeight_ton',
  var_spatial_name = 'AreaMap',
  facet_name = 'CLyear',
  spatial_dataset_name = 'FAOshp',
  spatial_dataset_var_name = 'Area',
  spatial_dataset_labels = FALSE,
  saveResults = FALSE,
  outputPath,
  extraShp_name = NA,
  displayInR = TRUE,
  var_name_new = "Landing weight (ton)",
  addToTitle = NA
)
result[[1]]

```
### Landings by metier {.tabset}
#### metier lvl5
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=7,fig.height=7, fig.cap='**Figure 11**: Total landings by metier level 5 (top 20).'}
#data prep
sub_cl_top <- cl%>%
  mutate(CLmetier5 = substr(CLmetier6, 1, 7))%>%
  group_by(CLyear, CLmetier5) %>%
  summarise(CLscientificWeight_1000ton = sum(CLscientificWeight_1000ton)) %>%
  top_n(20)


barplot(data = sub_cl_top,
      x = "CLmetier5",
      y = "CLscientificWeight_1000ton",
     # title = "Landings (1000 t) by Metier Lvl5",
      ylab = "Proportion of Landings (1000 t)")
```

#### metier lvl5 and country
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=7,fig.height=7, fig.cap='**Figure 12**: Proportion of countries landings by metier level 5 (top 20).'}
#data prep
sub_cl_2<- cl%>%
  mutate(CLmetier5 = substr(CLmetier6, 1, 7))%>%
  group_by(CLyear, CLmetier5, CLvesselFlagCountry) %>%
  summarise(CLscientificWeight_1000ton2 = sum(CLscientificWeight_1000ton))

sub_cl_top$Top <- "TOP"
sub_cl_2_top <- left_join(sub_cl_2,sub_cl_top,by="CLmetier5")

sub_cl_2_top <- sub_cl_2_top %>%
  filter(Top=='TOP')

barplot(data = sub_cl_2_top, 
      x = "CLmetier5",
      y = "CLscientificWeight_1000ton2",
      group = "CLvesselFlagCountry",
      groupNiceName = 'Vessel flag country',
      #title = "Landings (1000 t) by Metier Lvl5 and Country",
      ylab = "Proportion of Landings (%)",
      asPct = T)

```

#### metier lvl6
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6, fig.cap='**Figure 13**: Total landings by metier level 6 (top 20).'}
sub_cl_top<- cl%>%
  group_by(CLyear, CLmetier6) %>%
  summarise(CLscientificWeight_1000ton = sum(CLscientificWeight_1000ton)) %>%
  top_n(20, wt=CLscientificWeight_1000ton)

barplot(data = sub_cl_top, 
      x = "CLmetier6",
      y = "CLscientificWeight_1000ton",
     # title = "Landings (1000 t) by Metier Lvl6",
      ylab = "Sum of Landings (1000 t)")
```

#### metier lvl6 and country
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6, fig.cap='**Figure 14**: Proportion of countries landings by metier level 6 (top 20).'}
sub_cl_2<- cl%>%
  group_by(CLyear, CLmetier6, CLvesselFlagCountry) %>%
  summarise(CLscientificWeight_1000ton2 = sum(CLscientificWeight_1000ton))

sub_cl_top$Top <- "TOP"
sub_cl_2_top <- left_join(sub_cl_2,sub_cl_top,by="CLmetier6")

sub_cl_2_top <- sub_cl_2_top %>%
  filter(Top=='TOP')

barplot(data = sub_cl_2_top, 
        x = "CLmetier6",
        y = "CLscientificWeight_1000ton2",
        #title = "Landings (1000 t) by Metier Lvl6 and Country",
        group = "CLvesselFlagCountry",
        groupNiceName = 'Vessel flag country',
        ylab = "Proportion of Landings (%)",
        asPct = T)
```

### Landings by harbour {.tabset}
#### harbour
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6, fig.cap='**Figure 15**: Total landings of the main harbours (top 20).'}
sub_cl_top<- cl%>%
  group_by(CLyear, CLlandingLocation) %>%
  summarise(CLscientificWeight_1000ton = sum(CLscientificWeight_1000ton)) %>%
  top_n(20, wt=CLscientificWeight_1000ton)

barplot(data = sub_cl_top, 
      x = "CLlandingLocation",
      y = "CLscientificWeight_1000ton",
      #title = "Landings (1000 t) by Harbours",
      ylab = "Sum of Landings (1000 t)")
```

#### harbour and flag country
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6, fig.cap='**Figure 16**: Proportion of flag country landings by harbour (top 20).'}
sub_cl_2 <- cl%>%
  group_by(CLyear, CLlandingLocation, CLvesselFlagCountry) %>%
  summarise(CLscientificWeight_1000ton2 = sum(CLscientificWeight_1000ton))

sub_cl_top$Top <- "TOP"
sub_cl_2_top <- left_join(sub_cl_2,sub_cl_top,by = "CLlandingLocation")

sub_cl_2_top <- sub_cl_2_top %>%
  filter(Top=='TOP')

barplot(data = sub_cl_2_top, 
        x = "CLlandingLocation",
        y = "CLscientificWeight_1000ton2",
       # title = "Landings (1000 t) by Harbour and Flag Country",
        group = "CLvesselFlagCountry",
       groupNiceName = 'Vessel flag country',
        ylab = "Proportion of Landings (1000 t)",
        asPct = T )
```

#### map - harbour
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6, fig.cap='**Figure 17**: Map with the landing weight by main harbours (top 20).'}
sub_cl_top %>%  mutate(
         analysis_type = 'sum',
         type_of_threshold = 'none',
         value_of_threshold = NA
       )-> df


result <- pointsMap_func2(df,
                          title = '',#'Landings (1000 t) by Harbour',
                          var_name = 'CLscientificWeight_1000ton',
                          facet_name = 'CLyear',
                          var_spatial_name = 'CLlandingLocation',
                          spatial_dataset_name = 'Harbours',
                          spatial_dataset_var_name = 'Harbour',
                          plot_labels = TRUE,
                          saveResults = FALSE,
                          #outputPath,
                          Catch_group_name = NA,
                          extraShp_name = 'Divisionshp',
                          newVarName = NA,
                          addToTitle = NA
                          # ,
                          # RCGregion = 'BA'
                         )

  
result


```

### Landings abroad
Plot below shows the CLscientificWeight_ton between CLvesselFlagCountry (left), Harbour Country * (center) and CLlandingCountry(right).

```{r , echo = FALSE, warning = FALSE, message = FALSE,results = "asis", dpi=100, fig.width=9,fig.height=9, fig.cap = '**Figure 18**:River plot of total landings (1000t) between vessel Flag Country (left), Harbour Country (center) and landing Country(right). Width of line is proportional to landings. Harbour Country is the Country from the CLlandingLocation.'}
    
cl %>%
  group_by(CLyear,CLlandingCountry, HarbourCountry2, CLvesselFlagCountry) %>%
  summarise(CLscientificWeight_ton = sum(CLscientificWeight_ton))-> cl_river

result<-func_riverplot(df = cl_river,
                       left = 'CLvesselFlagCountry',
                       center = 'HarbourCountry2',
                       right = 'CLlandingCountry',
                       threesteps = TRUE,
                       value = 'CLscientificWeight_ton')

result
```

