## Area 21 landings
### Landings by country, area 21
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6,fig.cap='**Figure 67**:Landings (1000 t) by Country'}

barplot(data = cl %>%
  filter(substr(AreaMap,1,2)==21), 
      x = "CLvesselFlagCountry",
      y = "CLscientificWeight_1000ton",
      #title = "Landings (1000 t) by Country",
      ylab = "Sum of Landings (1000 t)",
      col_cou = T)
```

### Landings by species, area 21 {.tabset}
#### species
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6, fig.cap='**Figure 68**: Landings of the 20 main Species.'}

sub_cl<- cl%>%
  filter(substr(AreaMap,1,2)==21)%>%
  group_by(CLyear,SpeciesLaName) %>%
  summarise(CLscientificWeight_1000ton = sum(CLscientificWeight_1000ton)) %>%
  top_n(20, wt=CLscientificWeight_1000ton)
barplot(data = sub_cl, 
      x = "SpeciesLaName",
      y = "CLscientificWeight_1000ton",
      #title = "Landings (1000 t) by Species",
      ylab = "Sum of Landings (1000 t)")

```

#### species catch group
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6, fig.cap='**Figure 69**: Sum of the landings by species catch group.'}

barplot(data = cl%>%
  filter(substr(AreaMap,1,2)==21), 
      x = "CatchGroup",
      y = "CLscientificWeight_1000ton",
      #title = "Landings (1000 t) by Species Catch Group",
      ylab = "Landings (1000 t)")
```

### Landings by division, area 21 {.tabset}
#### division
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6, fig.cap='**Figure 70**: Landings (all species) distribution by division'}
barplot(data = cl%>%
  filter(substr(AreaMap,1,2)==21)%>%
    rename(Division = AreaMap), 
      x = "Division",
      y = "CLscientificWeight_1000ton",
      #title = "Landings (1000 t) by Area",
      ylab = "Sum of Landings (1000 t)")

```

#### map - division
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6, fig.cap='**Figure 71**: Sum of landings(1000 t) by Area 21'}
# do we need information on for how many rows(%) there was a missing CLscientificWeight_ton? <-------------------------- to do

# data prep
cl %>%
  filter(substr(AreaMap,1,2)==21)%>%
  mutate(AreaMap = toupper(AreaMap)) %>% 
  rename(`Division ` = AreaMap)%>%
  group_by(CLyear, `Division `) %>%
  summarise(CLscientificWeight_ton = sum(CLscientificWeight_ton)) %>%
  mutate(pr= CLscientificWeight_ton/sum(CLscientificWeight_ton, na.rm = TRUE)*100,
         analysis_type = 'sum',
         type_of_threshold = 'none',
         value_of_threshold = NA)-> df
if (nrow(df)==0){
  c('No data')
}else{
  # map
result = choroplethMap_func2(
  df,
  var_name = 'CLscientificWeight_ton',
  var_spatial_name = 'Division ',
  facet_name = 'CLyear',
  spatial_dataset_name = 'Divisionshp',
  spatial_dataset_var_name = 'Division',
  spatial_dataset_labels = FALSE,
  saveResults = FALSE,
  outputPath,
  extraShp_name = NA,
  displayInR = TRUE,
  var_name_new = "Landing weight (ton)",
  addToTitle = NA
)
result[[1]]
}
```

### Landings by harbour, area 21 {.tabset}
#### harbour
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6, fig.cap='**Figure 72**: Total landings of the main harbours (top 20).'}
sub_cl_top<- cl%>%
  filter(substr(AreaMap,1,2)==21)%>%
  group_by(CLyear, CLlandingLocation) %>%
  summarise(CLscientificWeight_1000ton = sum(CLscientificWeight_1000ton)) %>%
  top_n(20, wt=CLscientificWeight_1000ton)

barplot(data = sub_cl_top, 
      x = "CLlandingLocation",
      y = "CLscientificWeight_1000ton",
      #title = "Landings (1000 t) by Harbours",
      ylab = "Sum of Landings (1000 t)")
```

#### map - harbour
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6, fig.cap='**Figure 73**: Map with the landing weight by main harbours (top 20).'}
sub_cl_top %>%  mutate(
         analysis_type = 'sum',
         type_of_threshold = 'none',
         value_of_threshold = NA
       )-> df
if(nrow(df)==0){
  c('No data')
}else{

result <- pointsMap_func2(df,
                          title = '',#'Landings (1000 t) by Harbour',
                          var_name = 'CLscientificWeight_1000ton',
                          facet_name = 'CLyear',
                          var_spatial_name = 'CLlandingLocation',
                          spatial_dataset_name = 'Harbours',
                          spatial_dataset_var_name = 'Harbour',
                          plot_labels = TRUE,
                          saveResults = FALSE,
                          #outputPath,
                          Catch_group_name = NA,
                          extraShp_name = 'Divisionshp',
                          newVarName = NA,
                          addToTitle = NA,
                          RCGregion = 'BA'
                         )

  
result
}

```

### Landings abroad, area 21
Plot below shows the CLscientificWeight_ton between CLvesselFlagCountry (left), Harbour Country * (center) and CLlandingCountry(right).

```{r , echo = FALSE, warning = FALSE, message = FALSE,results = "asis", dpi=100, fig.width=9,fig.height=9, fig.cap = '**Figure 74**:River plot of total landings (1000t) between vessel Flag Country (left), Harbour Country (center) and landing Country(right). Width of line is proportional to landings. Harbour Country is the Country from the CLlandingLocation.'}
    
cl %>%
  filter(substr(AreaMap,1,2)==21)%>%
  group_by(CLyear,CLlandingCountry, HarbourCountry2, CLvesselFlagCountry) %>%
  summarise(CLscientificWeight_ton = sum(CLscientificWeight_ton))-> cl_river

result<-func_riverplot(df = cl_river,
                       left = 'CLvesselFlagCountry',
                       center = 'HarbourCountry2',
                       right = 'CLlandingCountry',
                       threesteps = TRUE,
                       value = 'CLscientificWeight_ton')
result

```



