## Small pelagics landings
### Landings by country, small pelagics
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6, fig.cap = '**Figure 19**:Landings of small pelagic species by country.'}

barplot(data = cl %>%
  filter(CatchGroup=='small pelagic'), 
      x = "CLvesselFlagCountry",
      y = "CLscientificWeight_1000ton",
      #title = "Landings (1000 t) by Country",
      ylab = "Sum of Landings (1000 t)",
      col_cou = T )
```

### Landings by species, small pelagics {.tabset}
#### species
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6, fig.cap = '**Figure 20**: Landings of the main landed species (top 20) from the small pelagic species catch group.'}

smallPelag <- cl%>% filter(CatchGroup=='small pelagic')

sub_cl<- smallPelag %>%
  group_by(CLyear,SpeciesLaName) %>%
  summarise(CLscientificWeight_1000ton = sum(CLscientificWeight_1000ton)) %>%
  top_n(20, wt=CLscientificWeight_1000ton)

barplot(data = sub_cl, 
      x = "SpeciesLaName",
      y = "CLscientificWeight_1000ton",
      #title = "Landings (1000 t) by Species",
      ylab = "Landings (1000 t)")
```

#### species and country
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6, fig.cap = '**Figure 21**: Proportion of countries with small pelagics landings by species (top 20).'}
sub_cl_2<- smallPelag%>%
  group_by(CLyear, SpeciesLaName, CLlandingCountry) %>%
  summarise(CLscientificWeight_1000ton2 = sum(CLscientificWeight_1000ton))

sub_cl_top <- sub_cl %>%
  arrange(desc(CLscientificWeight_1000ton)) %>%
  top_n(20)

sub_cl_top$Top <- "TOP"
sub_cl_2_top <- left_join(sub_cl_2,sub_cl_top,by="SpeciesLaName")

sub_cl_2_top <- sub_cl_2_top %>%
  filter(Top=='TOP')

barplot(data = sub_cl_2_top,
      x = "SpeciesLaName",
      y = "CLscientificWeight_1000ton2",
      group = "CLlandingCountry",
      groupNiceName = 'Vessel flag country',
     # title = "Landings (1000 t) by Species and Country",
      ylab = "Proportion of Landings (%)",
      asPct = T)
```

### Landings by fleet, small pelagics {.tabset}
#### fleet
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6, fig.cap = '**Figure 22**: Landings of small pelagics by the combined country*vessel fleet segment (top 20).'}

sub_cl_top<- cl%>%
  filter(CatchGroup=='small pelagic')%>%
  group_by(CLyear, FlagCountry_Loa) %>%
  summarise(CLscientificWeight_1000ton = sum(CLscientificWeight_1000ton))%>%
  top_n(20, wt=CLscientificWeight_1000ton)

barplot(data = sub_cl_top, 
      x = "FlagCountry_Loa",
      y = "CLscientificWeight_1000ton",
     # title = "Landings (1000 t) by Species",
      ylab = "Landings (1000 t)")
```

### Landings by area, small pelagics {.tabset}
#### area
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6, fig.cap = '**Figure 23**: Landings distribution of small pelagics, by area.'}

barplot(data = cl%>%
          mutate(Area = substr(CLarea,1,2))%>%filter(CatchGroup == 'small pelagic'), 
      x = "Area",
      y = "CLscientificWeight_1000ton",
   #   title = "Landings (1000 t) by Area",
      ylab = "Landings (1000 t)")

```

#### area and country
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6, fig.cap = '**Figure 24**: Proportion of countries landings of small pelagics by area.'}
barplot(data = cl%>%
          mutate(Area = substr(CLarea,1,2))%>%
          filter(CatchGroup == 'small pelagic'), 
      x = "Area",
      y = "CLscientificWeight_1000ton",
      group = "CLvesselFlagCountry",
      groupNiceName = 'Vessel flag country',
    #  title = "Landings (1000 t) by Area and Country",
      ylab = "Proportion of Landings (%)",
      asPct = T)


```

#### country and area
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6, fig.cap = '**Figure 25**: Proportion of small pelagics landings per area, by country.'}
barplot(data = cl%>%
          mutate(Area = substr(CLarea,1,2))%>%
          filter(CatchGroup == 'small pelagic'),
      x = "CLlandingCountry",
      y = "CLscientificWeight_1000ton",
      group = "Area",
     # title = "Landings (1000 t) by Country and Area",
      ylab = "Proportion of Landings (%)",
      asPct = T)

```

<!-- #### map area not in RCG LDF-->
<!-- #### map area and flag country  not in RCG LDF--> 

### Landings by metier, small pelagics {.tabset}
#### metier lvl5
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=7,fig.height=7, fig.cap = '**Figure 26**: Small pelagics landings by metier level 5 (top 20).'}
#data prep
sub_cl_top <- cl%>%
  filter(CatchGroup == 'small pelagic')%>%
  mutate(CLmetier5 = substr(CLmetier6, 1, 7))%>%
  group_by(CLyear, CLmetier5) %>%
  summarise(CLscientificWeight_1000ton = sum(CLscientificWeight_1000ton)) %>%
  top_n(20)

barplot(data = sub_cl_top,
      x = "CLmetier5",
      y = "CLscientificWeight_1000ton",
    #  title = "Landings (1000 t) by Metier Lvl5",
      ylab = "Landings (1000 t)")
```

#### metier lvl5 and country
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=7,fig.height=7, fig.cap='**Figure 27**: Proportion of countries landings of small pelagics by metier level 5 (top 20).'}
#data prep
sub_cl_2 <- cl%>%
  filter(CatchGroup == 'small pelagic') %>%
    mutate(CLmetier5 = substr(CLmetier6, 1, 7))%>%
  group_by(CLyear, CLmetier5, CLvesselFlagCountry) %>%
  summarise(CLscientificWeight_1000ton2 = sum(CLscientificWeight_1000ton))

sub_cl_top$Top <- "TOP"
sub_cl_2_top <- left_join(sub_cl_2,sub_cl_top,by="CLmetier5")

sub_cl_2_top <- sub_cl_2_top %>%
  filter(Top=='TOP')

barplot(data = sub_cl_2_top, 
      x = "CLmetier5",
      y = "CLscientificWeight_1000ton2",
      group = "CLvesselFlagCountry",
      groupNiceName = 'Vessel flag country',
    # title = "Landings (1000 t) by Metier Lvl5 and Country",
      ylab = "Proportion of Landings (%)",
      asPct = T)


```

#### metier lvl6
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6, fig.cap = '**Figure 28**: Small pelagics landings by metier level 6 (top 20).'}
sub_cl_top <- cl%>%
  filter(CatchGroup == 'small pelagic')%>%
  group_by(CLyear, CLmetier6) %>%
  summarise(CLscientificWeight_1000ton = sum(CLscientificWeight_1000ton)) %>%
  top_n(20, wt=CLscientificWeight_1000ton)

barplot(data = sub_cl_top, 
      x = "CLmetier6",
      y = "CLscientificWeight_1000ton",
      title = "Landings (1000 t) by Metier Lvl6",
      ylab = "Sum of Landings (1000 t)")
```

#### metier lvl6 and country
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6, fig.cap='**Figure 29**: Proportion of countries landings of small pelagics by metier level 6 (top 20).'}
sub_cl_2<- cl%>%
  filter(CatchGroup == 'small pelagic') %>%
  group_by(CLyear, CLmetier6, CLvesselFlagCountry) %>%
  summarise(CLscientificWeight_1000ton2 = sum(CLscientificWeight_1000ton))

sub_cl_top$Top <- "TOP"
sub_cl_2_top <- left_join(sub_cl_2,sub_cl_top, by = "CLmetier6")

sub_cl_2_top <- sub_cl_2_top %>%
  filter(Top=='TOP')

barplot(data = sub_cl_2_top, 
        x = "CLmetier6",
        y = "CLscientificWeight_1000ton2",
    #  title = "Landings (1000 t) by Metier Lvl6 and Country",
        group = "CLvesselFlagCountry",
    groupNiceName = 'Vessel flag country',
        ylab = "Proportion of Landings (%)",
        asPct = T)
```


### Landings by harbour, small pelagics {.tabset}
#### harbour
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6, fig.cap='**Figure 30**: Small pelagics landings in the main harbours (top 20).'}
sub_cl_top  <- cl %>%
  filter(CatchGroup == 'small pelagic') %>%
  group_by(CLyear, CLlandingLocation) %>%
  summarise(CLscientificWeight_1000ton = sum(CLscientificWeight_1000ton)) %>%
  top_n(20, wt=CLscientificWeight_1000ton)

barplot(data = sub_cl_top, 
      x = "CLlandingLocation",
      y = "CLscientificWeight_1000ton",
   # title = "Landings (1000 t) by Harbours",
      ylab = "Landings (1000 t)")
```

#### harbour and flag country
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6, fig.cap='**Figure 31**: Proportion of small pelagics landings by flag country and harbour.'}
sub_cl_2<- cl%>%
  filter(CatchGroup == 'small pelagic')%>%
  group_by(CLyear, CLlandingLocation, CLvesselFlagCountry) %>%
  summarise(CLscientificWeight_1000ton2 = sum(CLscientificWeight_1000ton))

sub_cl_top$Top <- "TOP"

sub_cl_2_top <- left_join(sub_cl_2,sub_cl_top,by = "CLlandingLocation")

sub_cl_2_top <- sub_cl_2_top %>%
  filter(Top=='TOP')

barplot(data = sub_cl_2_top, 
        x = "CLlandingLocation",
        y = "CLscientificWeight_1000ton2",
       # title = "Landings (1000 t) by Harbour and Flag Country",
       groupNiceName = 'Vessel flag country',
        group = "CLvesselFlagCountry",
        ylab = "Proportion of Landings (%)",
        asPct = T)
```

#### map - harbour
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6, fig.cap='**Figure 32**: Map with the landing weight of small pelagics by main harbours (top 20).'}
sub_cl_top %>%  mutate(
         analysis_type = 'sum',
         type_of_threshold = 'none',
         value_of_threshold = NA
       )-> df


result <- pointsMap_func2(df,
                          title = '',# 'Landings (1000 t) by Harbour',
                          var_name = 'CLscientificWeight_1000ton',
                          facet_name = 'CLyear',
                          var_spatial_name = 'CLlandingLocation',
                          spatial_dataset_name = 'Harbours',
                          spatial_dataset_var_name = 'Harbour',
                          plot_labels = TRUE,
                          saveResults = FALSE,
                          #outputPath,
                          Catch_group_name = NA,
                          extraShp_name = 'Divisionshp',
                          newVarName = NA,
                          addToTitle = NA#,
                          #RCGregion = 'BA'
                         )

  
result


```

### Landings abroad, small pelagics
Plot below shows the Landing (1000t) of small pelagic between CLvesselFlagCountry (left), Harbour Country * (center) and CLlandingCountry(right).
```{r riverplot aborad sp, echo = FALSE, warning = FALSE, message = FALSE,results = "asis", dpi=100, fig.width=9,fig.height=9, fig.cap = '**Figure 33**:River plot of Landings (1000t) of small pelagic between vessel Flag Country (left), Harbour Country (center) and landing Country(right). Width of line is proportional to landings. Harbour Country is the Country from the CLlandingLocation.'}
    
cl %>%
  filter(CatchGroup == 'small pelagic')%>%
  group_by(CLyear,CLlandingCountry, HarbourCountry2, CLvesselFlagCountry) %>%
  summarise(CLscientificWeight_ton = sum(CLscientificWeight_ton))-> cl_river

result<-func_riverplot(df = cl_river,
                       left = 'CLvesselFlagCountry',
                       center = 'HarbourCountry2',
                       right = 'CLlandingCountry',
                       threesteps = TRUE,
                       value = 'CLscientificWeight_ton')
result
```

