# Landings abroad, small pelagics{.tabset}

The plot below shows the flow of the small pelagics landings between the vessel Flag Country (left), Harbour Country (center) and the Landing Country (right). Width of each line is proportional to landings. Harbour Country is the country code obtained from the CLlandingLocation.

## Clupea harengus{.tabset}
### `r params$year-2`
```{r echo=FALSE, fig.height=6, fig.width=12, message=FALSE, warning=FALSE, dpi=100, results="asis", cache=FALSE}

cl %>%
  filter(CatchGroup == 'small pelagic',
         CLspeciesFaoCode %in% c('HER'),
         CLyear == params$year-2)%>%
  group_by(CLyear,CLlandingCountry, HarbourCountry2, CLvesselFlagCountry) %>%
  summarise(CLscientificWeight_ton = sum(CLscientificWeight_ton))-> cl_river

func_riverplot(df = cl_river,
                       left = 'CLvesselFlagCountry',
                       center = 'HarbourCountry2',
                       right = 'CLlandingCountry',
                       threesteps = TRUE,
                       value = 'CLscientificWeight_ton')

```

### `r params$year-1`
```{r echo=FALSE, fig.height=6, fig.width=12, message=FALSE, warning=FALSE, dpi=100, results="asis", cache=FALSE}

cl %>%
  filter(CatchGroup == 'small pelagic',
         CLspeciesFaoCode %in% c('HER'),
         CLyear == params$year-1)%>%
  group_by(CLyear,CLlandingCountry, HarbourCountry2, CLvesselFlagCountry) %>%
  summarise(CLscientificWeight_ton = sum(CLscientificWeight_ton))-> cl_river

func_riverplot(df = cl_river,
                       left = 'CLvesselFlagCountry',
                       center = 'HarbourCountry2',
                       right = 'CLlandingCountry',
                       threesteps = TRUE,
                       value = 'CLscientificWeight_ton')

```

### `r params$year`
```{r echo=FALSE, fig.height=6, fig.width=12, message=FALSE, warning=FALSE, dpi=100, results="asis", cache=FALSE}

cl %>%
  filter(CatchGroup == 'small pelagic',
         CLspeciesFaoCode %in% c('HER'),
         CLyear == params$year)%>%
  group_by(CLyear,CLlandingCountry, HarbourCountry2, CLvesselFlagCountry) %>%
  summarise(CLscientificWeight_ton = sum(CLscientificWeight_ton))-> cl_river

func_riverplot(df = cl_river,
                       left = 'CLvesselFlagCountry',
                       center = 'HarbourCountry2',
                       right = 'CLlandingCountry',
                       threesteps = TRUE,
                       value = 'CLscientificWeight_ton')

```

## Sprattus sprattus {.tabset}
### `r params$year-2`
```{r echo=FALSE, fig.height=6, fig.width=12, message=FALSE, warning=FALSE, dpi=100, results="asis", cache=FALSE}

cl %>%
  filter(CatchGroup == 'small pelagic',
         CLspeciesFaoCode %in% c('SPR'),
         CLyear == params$year-2)%>%
  group_by(CLyear,CLlandingCountry, HarbourCountry2, CLvesselFlagCountry) %>%
  summarise(CLscientificWeight_ton = sum(CLscientificWeight_ton))-> cl_river

result<-func_riverplot(df = cl_river,
                       left = 'CLvesselFlagCountry',
                       center = 'HarbourCountry2',
                       right = 'CLlandingCountry',
                       threesteps = TRUE,
                       value = 'CLscientificWeight_ton')
result
```

### `r params$year-1`
```{r echo=FALSE, fig.height=6, fig.width=12, message=FALSE, warning=FALSE, dpi=100, results="asis", cache=FALSE}

cl %>%
  filter(CatchGroup == 'small pelagic',
         CLspeciesFaoCode %in% c('SPR'),
         CLyear == params$year-1)%>%
  group_by(CLyear,CLlandingCountry, HarbourCountry2, CLvesselFlagCountry) %>%
  summarise(CLscientificWeight_ton = sum(CLscientificWeight_ton))-> cl_river

result<-func_riverplot(df = cl_river,
                       left = 'CLvesselFlagCountry',
                       center = 'HarbourCountry2',
                       right = 'CLlandingCountry',
                       threesteps = TRUE,
                       value = 'CLscientificWeight_ton')
result
```

### `r params$year`
```{r echo=FALSE, fig.height=6, fig.width=12, message=FALSE, warning=FALSE, dpi=100, results="asis", cache=FALSE}

cl %>%
  filter(CatchGroup == 'small pelagic',
         CLspeciesFaoCode %in% c('SPR'),
         CLyear == params$year)%>%
  group_by(CLyear,CLlandingCountry, HarbourCountry2, CLvesselFlagCountry) %>%
  summarise(CLscientificWeight_ton = sum(CLscientificWeight_ton))-> cl_river

result<-func_riverplot(df = cl_river,
                       left = 'CLvesselFlagCountry',
                       center = 'HarbourCountry2',
                       right = 'CLlandingCountry',
                       threesteps = TRUE,
                       value = 'CLscientificWeight_ton')
result
```