## Sampling (CS){.tabset}

### Hierarchies
The table below presents number of sampling schemes with small pelagic catches. Country vs hierarchy, including national and regional routine. The number of routines related to regional sampling scheme is presented in brackets.

```{r echo=FALSE, fig.height=6, fig.width=12, message=FALSE, warning=FALSE, dpi=100, results="asis", cache=FALSE}
#prepare subset of data
#all national and regional routines
cs |>
  filter(CatchGroup == 'small pelagic',
         SAcatchCat %in% c('Lan', 'Catch')) |>
  select(DEhierarchy, SDctry, DEsampScheme) |>
  distinct() |>
  group_by(SDctry, DEhierarchy) |>
  count() |>
  arrange(DEhierarchy) |>
  pivot_wider(names_from = DEhierarchy, values_from = n) |>
  rename(`Country/Hierarchy` = SDctry) -> SDsummary

cs |>
  filter(CatchGroup == 'small pelagic',
         SAcatchCat %in% c('Lan', 'Catch')) |>
  select(SDctry, DEsampScheme) |>
  distinct() |>
  group_by(SDctry) |>
  count() |>
  rename(`Country/Hierarchy` = SDctry,
         Total = n) -> summarizedCol

SDsummary <- SDsummary |>
  left_join(summarizedCol, by = "Country/Hierarchy")

summarizedRow <- cs |>
  filter(CatchGroup == 'small pelagic',
         SAcatchCat %in% c('Lan', 'Catch')) |>
  select(DEhierarchy, DEsampScheme) |>
  distinct() |>
  group_by(DEhierarchy) |>
  count() |>
  arrange(DEhierarchy) |>
  pivot_wider(names_from = DEhierarchy, values_from = n)|>
  mutate(`Country/Hierarchy` = "Total")

summarizedRowTotal <- cs |>
  filter(CatchGroup == 'small pelagic',
         SAcatchCat %in% c('Lan', 'Catch')) |>
  select(DEsampScheme) |>
  distinct() |>
  count() |>
  rename(Total = n)

cbind(summarizedRow,summarizedRowTotal) -> summarizedRow
SDsummary <- bind_rows(SDsummary, summarizedRow)


SDsummary <- SDsummary |>
  mutate(across(everything(), ~ replace_na(as.character(.), "")))
# only regional routines

cs |>
  select(DEhierarchy, SDctry, DEsampScheme,DEsampSchemeType,SAcatchCat) |>
  filter(DEsampSchemeType %in% c('RegPilCF','RegPilIB','RegRouCF'),
         SAcatchCat %in% c('Lan', 'Catch')) |>
  select(DEhierarchy, SDctry, DEsampScheme) |>
  distinct() |>
  group_by(SDctry, DEhierarchy) |>
  count() |>
  arrange(DEhierarchy) |>
  pivot_wider(names_from = DEhierarchy, values_from = n) |>
  rename(`Country/Hierarchy` = SDctry) -> SDsummaryType

cs |>
  select(DEhierarchy, SDctry, DEsampScheme,DEsampSchemeType,SAcatchCat) |>
  filter(DEsampSchemeType %in% c('RegPilCF','RegPilIB','RegRouCF'),
         SAcatchCat %in% c('Lan', 'Catch')) |>
  select(SDctry, DEsampScheme) |>
  distinct() |>
  group_by(SDctry) |>
  count() |>
  rename(`Country/Hierarchy` = SDctry,
         Total = n) -> summarizedCol

SDsummaryType <- SDsummaryType |>
  left_join(summarizedCol, by = "Country/Hierarchy")

summarizedRow <- cs |>
  select(DEhierarchy, SDctry, DEsampScheme,DEsampSchemeType,SAcatchCat) |>
  filter(DEsampSchemeType %in% c('RegPilCF','RegPilIB','RegRouCF'),
         SAcatchCat %in% c('Lan', 'Catch')) |>
  distinct() |>
  group_by(DEhierarchy) |>
  count() |>
  arrange(DEhierarchy) |>
  pivot_wider(names_from = DEhierarchy, values_from = n)|>
  mutate(`Country/Hierarchy` = "Total")

summarizedRowTotal <- cs |>
  filter(CatchGroup == 'small pelagic',
         DEsampSchemeType %in% c('RegPilCF','RegPilIB','RegRouCF'),
         SAcatchCat %in% c('Lan', 'Catch')) |>
  select(DEsampScheme) |>
  distinct() |>
  count() |>
  rename(Total = n)

cbind(summarizedRow,summarizedRowTotal) -> summarizedRow
SDsummaryType <- bind_rows(SDsummaryType, summarizedRow)

SDsummaryType <- SDsummaryType |>
  mutate(across(everything(), ~ replace_na(as.character(.), "")))

# merge tables with prefix. I want numbers of regional routine in brackets
combined <- SDsummary |>
  left_join(SDsummaryType, by = "Country/Hierarchy", suffix = c("", ".y"))

combined <- combined |>
  mutate(across(ends_with(".y"), ~ paste0("(", replace_na(as.character(.), "0"), ")")))

# merge cells from both tables
for(col in colnames(SDsummary)[-1]) {
  combined[[col]] <- paste0(combined[[col]], combined[[paste0(col, ".y")]])
}

# delete columns with ".y"
combined <- combined |>
  select(-ends_with(".y"))|>
  mutate(across(everything(), ~ gsub("\\(NA\\)", "", .)),
         across(everything(), ~ gsub("\\(0\\)", "", .)),
         across(everything(), ~ gsub("\\(\\)", "", .)))

kable(combined, align = "c")|>
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE) |>
  column_spec(1, width = "4cm")|>
  column_spec(2:ncol(combined), width = "3cm")

```

### Fishing Trips {.tabset}
The total number of fishing trips, including national and regional routines. The number of records related to regional sampling schemes is represented by points on the plot.

#### Clupea harengus
```{r echo=FALSE, fig.height=6, fig.width=12, message=FALSE, warning=FALSE, dpi=100, results="asis", cache=FALSE}

cs_rcg |>
  filter(
    SAcatchCat %in% c('Lan', 'Catch'),!is.na(FTid) &
      SAid != "",
    DEhierarchy != 13,
    DEsampScheme == 'Baltic SPF regional',
    SpeciesLaName %in% c('Clupea harengus')
  ) |>
     select(
       FTid,
       FTsampType,
       DEyear,
       Area,
       DEsampScheme,
       SpeciesLaName
     ) |>
  distinct()|>
    rename(
      Year = DEyear,
      Trip_id = FTid,
      SamplingPerformed= FTsampType
    ) |>
    group_by(Year,
             Area,
             SamplingPerformed) |>
    summarise(
      NoTrip = n_distinct(Trip_id, na.rm = TRUE)) -> samplingRegional

cs_rcg |>
  filter(
    SAcatchCat %in% c('Lan', 'Catch'),
    !is.na(FTid) & SAid != "",
    DEhierarchy != 13,
    SpeciesLaName %in% c('Clupea harengus'))|>
     select(
       FTid,
       FTsampType,
       DEyear,
       Area,
       SpeciesLaName
     ) |>
  distinct()|>
    rename(
      Year = DEyear,
      Trip_id = FTid,
      SamplingPerformed= FTsampType
    ) |>
    group_by(Year,
             Area,
             SamplingPerformed) |>
    summarise(
      NoTrip_all = n_distinct(Trip_id, na.rm = TRUE)) -> samplingAll
      
samplingAll %>%
    full_join(samplingRegional) -> samplingNoTrips

samplingNoTrips |>
  group_by(Year,SamplingPerformed,Area) |>
  summarise(
    NoTrip_regional = sum(NoTrip, na.rm=TRUE),
    NoTrip_all = sum(NoTrip_all, na.rm=TRUE)
  ) -> samplingNoTrips

ggplot(samplingNoTrips, aes(y = factor(Area), x = factor(SamplingPerformed))) +  ## global aes
    facet_wrap( ~ Year, ncol = 3) +
    geom_tile(aes(fill = NoTrip_all), na.rm = TRUE) +         ## to get the rect filled
    geom_point(data = subset(samplingNoTrips,NoTrip_regional != 0),aes(size = NoTrip_regional), shape = 1, stroke = 1)  + 
    scale_fill_distiller(
      palette = "Spectral",
      direction = -1,
      trans = 'log10',
      na.value = "transparent"
    ) +
    labs(
       x ='Sampling performed',
       y = 'Area',
       fill = "All Trips",
       title = "Baltic SPF regional - Clupea harengus",
     ) +
        geom_text(aes(label = ifelse(NoTrip_regional == 0, "", NoTrip_regional)),
                      nudge_x =  0.08,
                  hjust = 0,
                  size = 2)+
        geom_text(aes(label = NoTrip_all),
                    hjust = 0,         
            nudge_x = -0.45,   
            size = 2)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
    theme_bw()
```

#### Sprattus sprattus
```{r echo=FALSE, fig.height=6, fig.width=12, message=FALSE, warning=FALSE, dpi=100, results="asis", cache=FALSE}
cs_rcg |>
  filter(
    SAcatchCat %in% c('Lan', 'Catch'),!is.na(FTid) &
      SAid != "",
    DEhierarchy != 13,
    DEsampScheme == 'Baltic SPF regional',
    SpeciesLaName %in% c('Sprattus sprattus')
  ) |>
     select(
       FTid,
       FTsampType,
       DEyear,
       Area,
       DEsampScheme,
       SpeciesLaName
     ) |>
  distinct()|>
    rename(
      Year = DEyear,
      Trip_id = FTid,
      SamplingPerformed= FTsampType
    ) |>
    group_by(Year,
             Area,
             SamplingPerformed) |>
    summarise(
      NoTrip = n_distinct(Trip_id, na.rm = TRUE)) -> samplingRegional

cs_rcg |>
  filter(
    SAcatchCat %in% c('Lan', 'Catch'),
    !is.na(FTid) & SAid != "",
    DEhierarchy != 13,
    SpeciesLaName %in% c('Sprattus sprattus'))|>
     select(
       FTid,
       FTsampType,
       DEyear,
       Area,
       SpeciesLaName
     ) |>
  distinct()|>
    rename(
      Year = DEyear,
      Trip_id = FTid,
      SamplingPerformed= FTsampType
    ) |>
    group_by(Year,
             Area,
             SamplingPerformed) |>
    summarise(
      NoTrip_all = n_distinct(Trip_id, na.rm = TRUE)) -> samplingAll
      
samplingAll %>%
    full_join(samplingRegional) -> samplingNoTrips

samplingNoTrips |>
  group_by(Year,SamplingPerformed,Area) |>
  summarise(
    NoTrip_regional = sum(NoTrip, na.rm=TRUE),
    NoTrip_all = sum(NoTrip_all, na.rm=TRUE)
  ) -> samplingNoTrips

ggplot(samplingNoTrips, aes(y = factor(Area), x = factor(SamplingPerformed))) +  ## global aes
    facet_wrap( ~ Year, ncol = 3) +
    geom_tile(aes(fill = NoTrip_all), na.rm = TRUE) +         ## to get the rect filled
    geom_point(data = subset(samplingNoTrips,NoTrip_regional != 0),aes(size = NoTrip_regional), shape = 1, stroke = 1)  + 
    scale_fill_distiller(
      palette = "Spectral",
      direction = -1,
      trans = 'log10',
      na.value = "transparent"
    ) +
    labs(
       x ='Sampling performed',
       y = 'Area',
       fill = "All Trips",
       title = "Baltic SPF regional - Sprattus sprattus",
     ) +
        geom_text(aes(label = ifelse(NoTrip_regional == 0, "", NoTrip_regional)),
                      nudge_x =  0.08,
                  hjust = 0,
                  size = 2)+
        geom_text(aes(label = NoTrip_all),
                    hjust = 0,         
            nudge_x = -0.45,   
            size = 2)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
    theme_bw()
```