## Sampling (CS){.tabset}

### Hierarchies
The table below presents number of sampling schemes Country vs hierarchy, including national and regional routine. The number of routines related to regional sampling scheme is presented in brackets.

```{r echo=FALSE, fig.height=6, fig.width=12, message=FALSE, warning=FALSE, dpi=100, results="asis", cache=FALSE}
#prepare subset of data
#all national and regional routines
cs |>
  filter(CatchGroup == 'small pelagic',
         SAcatchCat %in% c('Lan', 'Catch')) |>
  select(DEhierarchy, SDctry, DEsampScheme) |>
  distinct() |>
  group_by(SDctry, DEhierarchy) |>
  count() |>
  arrange(DEhierarchy) |>
  pivot_wider(names_from = DEhierarchy, values_from = n) |>
  rename(`Country/Hierarchy` = SDctry) -> SDsummary

cs |>
  filter(CatchGroup == 'small pelagic',
         SAcatchCat %in% c('Lan', 'Catch')) |>
  select(SDctry, DEsampScheme) |>
  distinct() |>
  group_by(SDctry) |>
  count() |>
  rename(`Country/Hierarchy` = SDctry,
         Total = n) -> summarizedCol

SDsummary <- SDsummary |>
  left_join(summarizedCol, by = "Country/Hierarchy")

summarizedRow <- cs |>
  filter(CatchGroup == 'small pelagic',
         SAcatchCat %in% c('Lan', 'Catch')) |>
  select(DEhierarchy, DEsampScheme) |>
  distinct() |>
  group_by(DEhierarchy) |>
  count() |>
  arrange(DEhierarchy) |>
  pivot_wider(names_from = DEhierarchy, values_from = n)|>
  mutate(`Country/Hierarchy` = "Total")

summarizedRowTotal <- cs |>
  filter(CatchGroup == 'small pelagic',
         SAcatchCat %in% c('Lan', 'Catch')) |>
  select(DEsampScheme) |>
  distinct() |>
  count() |>
  rename(Total = n)

cbind(summarizedRow,summarizedRowTotal) -> summarizedRow
SDsummary <- bind_rows(SDsummary, summarizedRow)


SDsummary <- SDsummary |>
  mutate(across(everything(), ~ replace_na(as.character(.), "")))
# only regional routines

cs |>
  select(DEhierarchy, SDctry, DEsampScheme,DEsampSchemeType,SAcatchCat) |>
  filter(DEsampSchemeType %in% c('RegPilCF','RegPilIB','RegRouCF'),
         SAcatchCat %in% c('Lan', 'Catch')) |>
  select(DEhierarchy, SDctry, DEsampScheme) |>
  distinct() |>
  group_by(SDctry, DEhierarchy) |>
  count() |>
  arrange(DEhierarchy) |>
  pivot_wider(names_from = DEhierarchy, values_from = n) |>
  rename(`Country/Hierarchy` = SDctry) -> SDsummaryType

cs |>
  select(DEhierarchy, SDctry, DEsampScheme,DEsampSchemeType,SAcatchCat) |>
  filter(DEsampSchemeType %in% c('RegPilCF','RegPilIB','RegRouCF'),
         SAcatchCat %in% c('Lan', 'Catch')) |>
  select(SDctry, DEsampScheme) |>
  distinct() |>
  group_by(SDctry) |>
  count() |>
  rename(`Country/Hierarchy` = SDctry,
         Total = n) -> summarizedCol

SDsummaryType <- SDsummaryType |>
  left_join(summarizedCol, by = "Country/Hierarchy")

summarizedRow <- cs |>
  select(DEhierarchy, SDctry, DEsampScheme,DEsampSchemeType,SAcatchCat) |>
  filter(DEsampSchemeType %in% c('RegPilCF','RegPilIB','RegRouCF'),
         SAcatchCat %in% c('Lan', 'Catch')) |>
  distinct() |>
  group_by(DEhierarchy) |>
  count() |>
  arrange(DEhierarchy) |>
  pivot_wider(names_from = DEhierarchy, values_from = n)|>
  mutate(`Country/Hierarchy` = "Total")

summarizedRowTotal <- cs |>
  filter(CatchGroup == 'small pelagic',
         DEsampSchemeType %in% c('RegPilCF','RegPilIB','RegRouCF'),
         SAcatchCat %in% c('Lan', 'Catch')) |>
  select(DEsampScheme) |>
  distinct() |>
  count() |>
  rename(Total = n)

cbind(summarizedRow,summarizedRowTotal) -> summarizedRow
SDsummaryType <- bind_rows(SDsummaryType, summarizedRow)

SDsummaryType <- SDsummaryType |>
  mutate(across(everything(), ~ replace_na(as.character(.), "")))

# merge tables with prefix. I want numbers of regional routine in brackets
combined <- SDsummary |>
  left_join(SDsummaryType, by = "Country/Hierarchy", suffix = c("", ".y"))

combined <- combined |>
  mutate(across(ends_with(".y"), ~ paste0("(", replace_na(as.character(.), "0"), ")")))

# merge cells from both tables
for(col in colnames(SDsummary)[-1]) {
  combined[[col]] <- paste0(combined[[col]], combined[[paste0(col, ".y")]])
}

# delete columns with ".y"
combined <- combined |>
  select(-ends_with(".y"))|>
  mutate(across(everything(), ~ gsub("\\(NA\\)", "", .)),
         across(everything(), ~ gsub("\\(0\\)", "", .)),
         across(everything(), ~ gsub("\\(\\)", "", .)))

kable(combined, align = "c")|>
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE) |>
  column_spec(1, width = "4cm")|>
  column_spec(2:ncol(combined), width = "3cm")

```

### Samples
The total number of records in Sample Details (SD) by hierarchy, including national and regional routines. The number of records related to regional sampling schemes is presented in brackets.
```{r echo=FALSE, fig.height=6, fig.width=12, message=FALSE, warning=FALSE, dpi=100, results="asis", cache=FALSE}

#   cs_rcg |>
#       SAcatchCat %in% c('Lan', 'Catch'),
#       !is.na(SAid) &
#         SAid != "",
#       DEhierarchy != 13,
#       DEsampScheme == 'Baltic SPF regional',
#       SpeciesLaName %in% c('Clupea harengus')
#     ) |>
#     select(
#       FTid,
#       FOid,
#       LEid,
#       DEhierarchy,
#       metier6,
#       DEyear,
#       SDctry,
#       VDlenCat,
#       SAsampWtLive,
#       Area,
#       SpeciesLaName
#     ) |>
#     mutate(Trip_id = ifelse((!is.na(FTid) &
#                                FTid != "") &
#                               (is.na(LEid) |
#                                  LEid == ""), FTid, LEid)) |>
#     mutate(Trip_id = as.character(ifelse(
#       Trip_id == "" & DEhierarchy == 13, FOid, Trip_id
#     ))) |>
#     rename(
#       MetierLvl6 = metier6,
#       Year = DEyear,
#       FlagCountry = SDctry,
#       VesselLengthCategory = VDlenCat
#     ) |>
#     distinct() |>
#     group_by(Year,
#              FlagCountry,
#              Area,
#              SpeciesLaName,
#              MetierLvl6,
#              VesselLengthCategory) |>
#     summarise(
#       NoPSU = n_distinct(Trip_id, na.rm = TRUE),
#       WeigthKg = sum(SAsampWtLive / 1000, na.rm =  TRUE)
#     ) -> samplingPart
# 
# barplot(data = samplingPart, 
#       x = "SpeciesLaName",
#       y = "CLscientificWeight_1000ton",
#       ylab = "Landings (1000 t)")
# 

```