# Total landings and number of samples collected - Regional routine {.tabset}
The matrices below show the total landing in tons and the number of samples collected in the Baltic SPF Regional in the years `r params$year - 2` - `r params$year` for the two main small pelagic species: Clupea harengus and Sprattus sprattus. For each species, two plots have been prepared: one group by area and gear, and the other group by country and gear.

## Clupea harengus - Area/Gear
```{r echo=FALSE, fig.height=6, fig.width=12, message=FALSE, warning=FALSE, dpi=100, results="asis", cache=FALSE}
  
  cl_data <- cl_rcg
  
  cs |>
    filter(
      SAcatchCat %in% c('Lan', 'Catch'),
      !is.na(SAid) &
        SAid != "",
      DEhierarchy != 13,
      DEsampScheme == 'Baltic SPF regional',
      SpeciesLaName %in% c('Clupea harengus')
    ) |>
    select(
      FTid,
      FOid,
      LEid,
      DEhierarchy,
      metier6,
      DEyear,
      SDctry,
      VDlenCat,
      SAsampWtLive,
      Area,
      SpeciesLaName
    ) |>
    mutate(Trip_id = ifelse((!is.na(FTid) &
                               FTid != "") &
                              (is.na(LEid) |
                                 LEid == ""), FTid, LEid)) |>
    mutate(Trip_id = as.character(ifelse(
      Trip_id == "" & DEhierarchy == 13, FOid, Trip_id
    ))) |>
    rename(
      MetierLvl6 = metier6,
      Year = DEyear,
      FlagCountry = SDctry,
      VesselLengthCategory = VDlenCat
    ) |>
    distinct() |>
    group_by(Year,
             FlagCountry,
             Area,
             SpeciesLaName,
             MetierLvl6,
             VesselLengthCategory) |>
    summarise(
      NoPSU = n_distinct(Trip_id, na.rm = TRUE),
      WeigthKg = sum(SAsampWtLive / 1000, na.rm =  TRUE)
    ) -> samplingPart
  
  cl_data |>
    rename(
      MetierLvl6 = CLmetier6,
      Year = CLyear,
      FlagCountry = CLvesselFlagCountry,
      VesselLengthCategory = CLvesselLengthCategory,
      Area = CLarea
    ) |>
    filter(
      Year %in% unique(samplingPart$Year),
      SpeciesLaName %in% unique(samplingPart$SpeciesLaName)
    ) |>
    group_by(Year,
             FlagCountry,
             Area,
             SpeciesLaName,
             MetierLvl6,
             VesselLengthCategory) |>
    summarise(LandingsT = sum(CLscientificWeight_ton, na.rm = TRUE)) -> LandingsPart
  
  samplingPart %>%
    full_join(LandingsPart) -> samplingVSlandings
  
  samplingVSlandings |>
    mutate(Gear = str_sub(MetierLvl6, end = 3)) %>%
    group_by(
      Area,
      Gear,
      Year#,
     # FlagCountry
    ) %>%
    summarise(
      NoPSU = sum(NoPSU, na.rm = TRUE),
      LandingsT = sum(LandingsT, na.rm = TRUE)
    ) |>
    mutate(NoPSU = ifelse(NoPSU == 0, NA, NoPSU)) ->
    samplingVSlandingsF_HER
  
  
  ggplot(samplingVSlandingsF_HER, aes(y = factor(Area), x = factor(Gear))) +  ## global aes
    facet_wrap( ~ Year, ncol = 3) +
    geom_tile(aes(fill = LandingsT), na.rm = TRUE) +         ## to get the rect filled
    geom_point(aes(size = NoPSU), shape = 1, stroke = 1)  +    ## geom_point for circle illusion
    scale_fill_distiller(
      palette = "Spectral",
      direction = -1,
      trans = 'log10',
      na.value = "transparent"
    ) +
    labs(
       x ='Gear',
       y = 'Area',
       fill = "Landings (t)",
       size = "No. of PSU",
       title = "Baltic SPF regional - Clupea harengus",
     ) +
    theme_bw()+
    theme(axis.text.x = element_text(angle = 45, hjust = 1))

```

## Clupea harengus - Country/Gear
```{r echo=FALSE, fig.height=6, fig.width=12, message=FALSE, warning=FALSE, dpi=100, results="asis", cache=FALSE}
  
  cl_data <- cl_rcg
  
  cs |>
    filter(
      SAcatchCat %in% c('Lan', 'Catch'),
      !is.na(SAid) &
        SAid != "",
      DEhierarchy != 13,
      DEsampScheme == 'Baltic SPF regional',
      SpeciesLaName %in% c('Clupea harengus')
    ) |>
    select(
      FTid,
      FOid,
      LEid,
      DEhierarchy,
      metier6,
      DEyear,
      SDctry,
      VDlenCat,
      SAsampWtLive,
      Area,
      SpeciesLaName
    ) |>
    mutate(Trip_id = ifelse((!is.na(FTid) &
                               FTid != "") &
                              (is.na(LEid) |
                                 LEid == ""), FTid, LEid)) |>
    mutate(Trip_id = as.character(ifelse(
      Trip_id == "" & DEhierarchy == 13, FOid, Trip_id
    ))) |>
    rename(
      MetierLvl6 = metier6,
      Year = DEyear,
      FlagCountry = SDctry,
      VesselLengthCategory = VDlenCat
    ) |>
    distinct() |>
    group_by(Year,
             FlagCountry,
             Area,
             SpeciesLaName,
             MetierLvl6,
             VesselLengthCategory) |>
    summarise(
      NoPSU = n_distinct(Trip_id, na.rm = TRUE),
      WeigthKg = sum(SAsampWtLive / 1000, na.rm =  TRUE)
    ) -> samplingPart
  
  cl_data |>
    rename(
      MetierLvl6 = CLmetier6,
      Year = CLyear,
      FlagCountry = CLvesselFlagCountry,
      VesselLengthCategory = CLvesselLengthCategory,
      Area = CLarea
    ) |>
    filter(
      Year %in% unique(samplingPart$Year),
      SpeciesLaName %in% unique(samplingPart$SpeciesLaName)
    ) |>
    group_by(Year,
             FlagCountry,
             Area,
             SpeciesLaName,
             MetierLvl6,
             VesselLengthCategory) |>
    summarise(LandingsT = sum(CLscientificWeight_ton, na.rm = TRUE)) -> LandingsPart
  
  samplingPart %>%
    full_join(LandingsPart) -> samplingVSlandings
  
  samplingVSlandings |>
    mutate(Gear = str_sub(MetierLvl6, end = 3)) %>%
    group_by(
      #Area,
      Gear,
      Year,
      FlagCountry
    ) %>%
    summarise(
      NoPSU = sum(NoPSU, na.rm = TRUE),
      LandingsT = sum(LandingsT, na.rm = TRUE)
    ) |>
    mutate(NoPSU = ifelse(NoPSU == 0, NA, NoPSU)) ->
    samplingVSlandingsF_HER
  
  
  ggplot(samplingVSlandingsF_HER, aes(y = factor(FlagCountry), x = factor(Gear))) +  ## global aes
    facet_wrap( ~ Year, ncol = 3) +
    geom_tile(aes(fill = LandingsT), na.rm = TRUE) +         ## to get the rect filled
    geom_point(aes(size = NoPSU), shape = 1, stroke = 1)  +    ## geom_point for circle illusion
    scale_fill_distiller(
      palette = "Spectral",
      direction = -1,
      trans = 'log10',
      na.value = "transparent"
    ) +
    labs(
       x ='Gear',
       y = 'Country',
       fill = "Landings (t)",
       size = "No. of PSU",
       title = "Baltic SPF regional - Clupea harengus",
     ) +
    theme_bw()+
    theme(axis.text.x = element_text(angle = 45, hjust = 1))

```

## Sprattus sprattus - Area/Gear
```{r echo=FALSE, fig.height=6, fig.width=12, message=FALSE, warning=FALSE, dpi=100, results="asis", cache=FALSE}
  
  cl_data <- cl_rcg
  
  cs |>
    filter(
      SAcatchCat %in% c('Lan', 'Catch'),
      !is.na(SAid) &
        SAid != "",
      DEhierarchy != 13,
      DEsampScheme == 'Baltic SPF regional',
      SpeciesLaName %in% c('Sprattus sprattus')
    ) |>
    select(
      FTid,
      FOid,
      LEid,
      DEhierarchy,
      metier6,
      DEyear,
      SDctry,
      VDlenCat,
      SAsampWtLive,
      Area,
      SpeciesLaName
    ) |>
    mutate(Trip_id = ifelse((!is.na(FTid) &
                               FTid != "") &
                              (is.na(LEid) |
                                 LEid == ""), FTid, LEid)) |>
    mutate(Trip_id = as.character(ifelse(
      Trip_id == "" & DEhierarchy == 13, FOid, Trip_id
    ))) |>
    rename(
      MetierLvl6 = metier6,
      Year = DEyear,
      FlagCountry = SDctry,
      VesselLengthCategory = VDlenCat
    ) |>
    distinct() |>
    group_by(Year,
             FlagCountry,
             Area,
             SpeciesLaName,
             MetierLvl6,
             VesselLengthCategory) |>
    summarise(
      NoPSU = n_distinct(Trip_id, na.rm = TRUE),
      WeigthKg = sum(SAsampWtLive / 1000, na.rm =  TRUE)
    ) -> samplingPart
  
  cl_data |>
    rename(
      MetierLvl6 = CLmetier6,
      Year = CLyear,
      FlagCountry = CLvesselFlagCountry,
      VesselLengthCategory = CLvesselLengthCategory,
      Area = CLarea
    ) |>
    filter(
      Year %in% unique(samplingPart$Year),
      SpeciesLaName %in% unique(samplingPart$SpeciesLaName)
    ) |>
    group_by(Year,
             FlagCountry,
             Area,
             SpeciesLaName,
             MetierLvl6,
             VesselLengthCategory) |>
    summarise(LandingsT = sum(CLscientificWeight_ton, na.rm = TRUE)) -> LandingsPart
  
  samplingPart %>%
    full_join(LandingsPart) -> samplingVSlandings
  
  samplingVSlandings |>
    mutate(Gear = str_sub(MetierLvl6, end = 3)) %>%
    group_by(
      Area,
      Gear,
      Year#,
      #FlagCountry
    ) %>%
    summarise(
      NoPSU = sum(NoPSU, na.rm = TRUE),
      LandingsT = sum(LandingsT, na.rm = TRUE)
    ) |>
    mutate(NoPSU = ifelse(NoPSU == 0, NA, NoPSU)) ->
    samplingVSlandingsF_SPR
  
  
  ggplot(samplingVSlandingsF_SPR, aes(y = factor(Area), x = factor(Gear))) +  ## global aes
    facet_wrap( ~ Year, ncol = 3) +
    geom_tile(aes(fill = LandingsT), na.rm = TRUE) +         ## to get the rect filled
    geom_point(aes(size = NoPSU), shape = 1, stroke = 1)  +    ## geom_point for circle illusion
    scale_fill_distiller(
      palette = "Spectral",
      direction = -1,
      trans = 'log10',
      na.value = "transparent"
    ) +
    labs(
       x ='Gear',
       y = 'Area',
       fill = "Landings (t)",
       size = "No. of PSU",
       title = "Baltic SPF regional - Sprattus sprattus",
     ) +
    theme_bw()

```

## Sprattus sprattus - Country/Gear
```{r echo=FALSE, fig.height=6, fig.width=12, message=FALSE, warning=FALSE, dpi=100, results="asis", cache=FALSE}
  
  cl_data <- cl_rcg
  
  cs |>
    filter(
      SAcatchCat %in% c('Lan', 'Catch'),
      !is.na(SAid) &
        SAid != "",
      DEhierarchy != 13,
      DEsampScheme == 'Baltic SPF regional',
      SpeciesLaName %in% c('Sprattus sprattus')
    ) |>
    select(
      FTid,
      FOid,
      LEid,
      DEhierarchy,
      metier6,
      DEyear,
      SDctry,
      VDlenCat,
      SAsampWtLive,
      Area,
      SpeciesLaName
    ) |>
    mutate(Trip_id = ifelse((!is.na(FTid) &
                               FTid != "") &
                              (is.na(LEid) |
                                 LEid == ""), FTid, LEid)) |>
    mutate(Trip_id = as.character(ifelse(
      Trip_id == "" & DEhierarchy == 13, FOid, Trip_id
    ))) |>
    rename(
      MetierLvl6 = metier6,
      Year = DEyear,
      FlagCountry = SDctry,
      VesselLengthCategory = VDlenCat
    ) |>
    distinct() |>
    group_by(Year,
             FlagCountry,
             Area,
             SpeciesLaName,
             MetierLvl6,
             VesselLengthCategory) |>
    summarise(
      NoPSU = n_distinct(Trip_id, na.rm = TRUE),
      WeigthKg = sum(SAsampWtLive / 1000, na.rm =  TRUE)
    ) -> samplingPart
  
  cl_data |>
    rename(
      MetierLvl6 = CLmetier6,
      Year = CLyear,
      FlagCountry = CLvesselFlagCountry,
      VesselLengthCategory = CLvesselLengthCategory,
      Area = CLarea
    ) |>
    filter(
      Year %in% unique(samplingPart$Year),
      SpeciesLaName %in% unique(samplingPart$SpeciesLaName)
    ) |>
    group_by(Year,
             FlagCountry,
             Area,
             SpeciesLaName,
             MetierLvl6,
             VesselLengthCategory) |>
    summarise(LandingsT = sum(CLscientificWeight_ton, na.rm = TRUE)) -> LandingsPart
  
  samplingPart %>%
    full_join(LandingsPart) -> samplingVSlandings
  
  samplingVSlandings |>
    mutate(Gear = str_sub(MetierLvl6, end = 3)) %>%
    group_by(
      #Area,
      Gear,
      Year,
      FlagCountry
    ) %>%
    summarise(
      NoPSU = sum(NoPSU, na.rm = TRUE),
      LandingsT = sum(LandingsT, na.rm = TRUE)
    ) |>
    mutate(NoPSU = ifelse(NoPSU == 0, NA, NoPSU)) ->
    samplingVSlandingsF_SPR
  
  
  ggplot(samplingVSlandingsF_SPR, aes(y = factor(FlagCountry), x = factor(Gear))) +  ## global aes
    facet_wrap( ~ Year, ncol = 3) +
    geom_tile(aes(fill = LandingsT), na.rm = TRUE) +         ## to get the rect filled
    geom_point(aes(size = NoPSU), shape = 1, stroke = 1)  +    ## geom_point for circle illusion
    scale_fill_distiller(
      palette = "Spectral",
      direction = -1,
      trans = 'log10',
      na.value = "transparent"
    ) +
    labs(
       x ='Gear',
       y = 'Country',
       fill = "Landings (t)",
       size = "No. of PSU",
       title = "Baltic SPF regional - Sprattus sprattus",
     ) +
    theme_bw()

```
