---
title: "RDBES Catch and Effort Overview Long Distance Fisheries"
date: "`r format(Sys.time(), '%d.%m.%Y')`"
output:
  html_document:
    toc: true
    fig_caption: yes
    
params:
  eval: TRUE
  set_subtitle: "Title"
  year: 2000
  allYears: 2000
  region: '' 
  logo_path: '' 
  data_dir: ''
  table_dir: '' 
  CLfileName: ''
  CEfileName: ''
---

---
subtitle: `r paste(params$region, params$year, sep = ", ")`
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
options(knitr.kable.NA = '')
options(scipen=999)
```

```{r, echo=FALSE}
htmltools::img(src = knitr::image_uri(params$logo_path),
             alt = 'logo',
             style = 'position:absolute; top:0; right:0; padding:10px;',width="300px", height="100px")
```


```{r eval_params, echo=FALSE, message=FALSE, warning=FALSE}
#DEFINE EVAL_PARAMETERS IF NEEDED

## establish conditions  - can use it if for example some chunks should be run only for selected Regions
# eval_region_LDF <- params$region=='LDF' # when added to the chunk header, the chunk will be run only for LDF report

```

```{r GlobalSettings, echo=FALSE}
# DEFINE GLOBAL PARAMETERS/FUNCTIONS FOR DISPLAYING TABLES/PLOTS/MAPS/...

```

```{r mapData,include = F}
# LOAD DATA NEEDED FOR MAPS (shp, rdata, ...) FOR ALL RCGs
source("scripts/prepareSpatialData.R")

```

```{r NAFOstocks, include = F}

# to delete? why is it commented?
# write.csv(cl_rcg[substr(CLarea,1,2)=="21",
#                  .(t=sum(CLscientificWeight_ton)),
#                  by=.(SpeciesLaName, CLarea)],
#           file="NAFO_cl_summary.csv")
# openxlsx::write.xlsx(cl_rcg[substr(CLarea,1,2)=="21",
#                  .(t=sum(CLscientificWeight_ton)),
#                  by=.(CLarea, CLmetier6, SpeciesLaName)],
#           file="Area21_cl_summary.xlsx")
NAFOstocksRef <- read.csv("../../data/NAFO_species_area_stock.csv")
if(nrow(NAFOstocksRef)!=nrow(unique(NAFOstocksRef[,c("SpeciesLaName","CLarea")]))){
  stop("ERROR. NAFO stocks reference table not unique")
}

```


```{r, results='asis', echo = FALSE,  warning=FALSE, message=FALSE}

source('scripts/disclaimerText.R')
```

# Landings (CL)

```{r, child = 'child_rmd/Landings_Overall.Rmd'}
``` 

```{r, child = 'child_rmd/Landings_SmallPelagics.Rmd'}
``` 

```{r, child = 'child_rmd/Landings_34.Rmd'}
``` 

```{r, child = 'child_rmd/Landings_47.Rmd'}
``` 

```{r, child = 'child_rmd/Landings_87.Rmd'}
``` 

```{r, child = 'child_rmd/Landings_21.Rmd'}
``` 

```{r, child = 'child_rmd/Landings_Canaries.Rmd'}
``` 

```{r, child = 'child_rmd/Landings_Madeira.Rmd'}
``` 

# Effort (CE)

```{r, child = 'child_rmd/Effort.Rmd'}
``` 



# Tables for the report

```{r, results = "asis", eval = T, echo = FALSE, warning = FALSE, message = FALSE}
cl_rcg %>% 
  select(CLvesselFlagCountry, CLyear, CLarea, AreaMap, CLjurisdictionArea, CLspeciesFaoCode,CLmetier6, CLscientificWeight_ton, CLspeciesCode, SpeciesLaName, Species3ALPHA, CatchGroup)%>% #usunelam stock z pierwotnej wersji
  mutate(Division=AreaMap)-> clOrg

ce_rcg %>% 
  select(CEvesselFlagCountry, CEyear, CEarea, AreaMap, CEjurisdictionArea, 
         CEmetier6, CEscientificDaysAtSea)%>%
  mutate(Division=AreaMap)-> ceOrg


wormsScientific = read_csv("../../data/worms_3alpha.csv")
wormsScientific %>%
  filter(!is.na(AphiaID)) %>%
  group_by(AphiaID) %>% 
  mutate(duplikaty = rank(Scientific_name, ties.method = "first")) %>% # in this file there are duplicated values for worms codes, maybe better to try with fishpi
  filter(duplikaty ==1) %>% 
  select(AphiaID, Scientific_name, Alpha = '3A_CODE') -> wormsScientific

# Angola for LTU
clOrg %>% 
  mutate(CLjurisdictionArea = ifelse(CLvesselFlagCountry=='LTU' & CLarea==47 & is.na(CLjurisdictionArea) & CLyear %in% c(2015, 2016), 'Angola',CLjurisdictionArea
                             ) )->clOrg # check CLarea is correct here

clOrg %>% 
  #left_join(wormsScientific, by = c("CLspeciesCode" = "AphiaID")) %>%
  mutate(Species2 = ifelse(!is.na(Species3ALPHA),
                           paste(SpeciesLaName, ' (', Species3ALPHA, ')', sep = ''), 
                           paste(SpeciesLaName))
  )->cl2 # data for annex



```

```{r, child = 'child_rmd/Tables_Section_4_1.Rmd'}
``` 

```{r, child = 'child_rmd/Tables_Section_4_2.Rmd'}
``` 

```{r, child = 'child_rmd/Tables_Section_4_3.Rmd'}
``` 

# Annex 2 - Landings by species by area reported by MS


```{r, results = "asis",echo = FALSE, warning = FALSE, message = FALSE, eval = T}
# wormsAlpha = read_csv("D:/Do przegrania na PC/IntersessionalWork/RCG LDF/data/worms_3alpha.csv")
# wormsAlpha %>%
#   filter(!is.na(AphiaID)) %>%
#   group_by(AphiaID) %>% 
#   mutate(duplikaty = rank(Scientific_name, ties.method = "first")) %>% # w pliku sa duplikaty dla kodow wormsowych, w przyszlym roku sprobowac z fishpi
#   filter(duplikaty ==1) %>% 
#   select(AphiaID, Alpha = '3A_CODE') -> wormsAlpha
# 
# cl %>% 
#   filter(Year == 2020) %>% nrow()-> clTest
# cl %>% 
#   filter(Year == 2020)%>% left_join(wormsAlpha, by = c("SpeciesAphiaID" = "AphiaID"))  %>% nrow()->clWormsTest
# 
# if (clTest!= clWormsTest){
#   cat('Sth wrong when mergind CL with Worms codes file. To be checked!')
# }
# 
cl %>%
  filter(CLyear == params$year)%>%
 # left_join(wormsAlpha, by = c("SpeciesAphiaID" = "AphiaID")) %>%
 # filter(is.na(Alpha)) %>% distinct(Species, SpeciesAphiaID) %>% arrange(Species)
  mutate(Species3ALPHA = case_when(
    CLspeciesCode==299565~'MKW',# Muraena augusti (MKW)
    CLspeciesCode==151174~'VMA',# Scomber colias (VMA)
    TRUE~Species3ALPHA
  )) %>%
  mutate(Species2 = ifelse(!is.na(Species3ALPHA),
                           paste(SpeciesLaName, ' (', Species3ALPHA, ')', sep = ''),
                           paste(SpeciesLaName))
  )-> cl2
```

```{r, child = 'child_rmd/Annex2_CECAF.Rmd'}
``` 

```{r, child = 'child_rmd/Annex2_SPRFMO.Rmd'}
``` 

```{r, child = 'child_rmd/Annex2_47.Rmd'}
``` 

```{r, child = 'child_rmd/Annex2_21.Rmd'}
```

```{r, child = 'child_rmd/Annex2_FrenchOutermostRegions.Rmd'}
```

```{r, child = 'child_rmd/Annex2_GlobalTables.Rmd'}
```

# Annex A. Reading the graphs
## Barplots

In (bar)plots, subtitles indicate if all RDB data could be used and are displayed.  Some data can not be displayed in the plots, e.g. due to missing or incorrect values or due to missing referring data (e.g. if no statistical rectangle is given or harbor names are missing, landings in the respective plots can’t be displayed).
The factor x:% in subtitle indicates the percentage of RDB data that are displayed  in the x-variable. y:% in subtitle indicates the percentage of RDB data in the respective y-variable. z:% in subtitle indicate the percentage of complete (i.e., non-missing) RDBES rows in variable. 

## Maps

The maps are generated based on complete and available data from the RDBES. The subtitles of the header state the subselection that is displayed (e.g. “all Data”, “pelagics”, etc.).  if data cannot be shown on a map (e.g. due to missing information on the area or harbor code), the missing values is given in the figure text below. 

```{r, child = 'child_rmd/Appendix.Rmd'}
```
