---
title: "Sampling Overview"
date: "`r format(Sys.time(), '%d.%m.%Y')`"
output:
  html_document:
    toc: true
    fig_caption: yes
    
params:
  set_subtitle: "Title"
  region: 'BA'
  year: 2024
  logo_path: "../../data/logo/logo RCG BALTIC.PNG"
  data_dir: '../../data_RDBES/002_prepared/20250212/RCG_BA'
  RDBES_download_date: '01/01/2000'
  CSfileName: 'RDBES_RCG_NA_CS_2024_2024_prepared_20250425'
  
---

---
subtitle: `r paste(dplyr::case_when(params$region=='BA'~'Baltic',params$region=='NA'~'North Atlantic',params$region=='NSEA'~'North Sea and Eastern Arctic'), params$year, sep = ", ")`
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
```

```{r, echo=FALSE}
  htmltools::img(src = knitr::image_uri(params$logo_path), 
               alt = 'logo', 
               style = 'position:absolute; top:0; right:0; padding:10px;',width="300px", height="100px")
```

```{r Define_eval, echo=FALSE, message=FALSE, warning=FALSE}
# DEFINE EVAL_PARAMETERS

 ## establish conditions  - can use it if for example some chunks should be run only for selected Regions, e.g. only Bal
 eval_region_BA <- params$region=='BA' # when added to the chunk header, the chunk will be run only for BA report
 eval_region_NA <- params$region=='NA' # when added to the chunk header, the chunk will be run only for NA report
 eval_region_NSEA <- params$region=='NSEA' # when added to the chunk header, the chunk will be run only for NSEA report

```

```{r GlobalSettings, echo=FALSE}
# DEFINE GLOBAL PARAMETERS/FUNCTIONS FOR DISPLAYING TABLES/PLOTS/MAPS/...

```


```{r mapData, echo=FALSE}
# LOAD DATA NEEDED FOR MAPS (shp, rdata, ...) FOR ALL RCGs
UNLOCODE %>%
  mutate(Harbour = loCode) %>%
  filter(!is.na(Harbour)) %>%
  select(Harbour, lat, lon) -> Harbours
```

```{r mapDataBA, include = F, eval=eval_region_BA}
# LOAD PREPARE DATA NEEDED FOR MAPS (shp, rdata, ...) ONLY FOR RCG BA
StatRectshp  = sf::st_read("../../data/shapefiles/RCG_BA_ICESrect.shp")# for BA maps on DIVISIONS level -> WATCH OUT ...28.1/...28.2

FAOshp  = sf::st_read("../../data/shapefiles/RCG_BA_FAOareas.shp") %>% filter(F_LEVEL == 'SUBDIVISION') # for BA maps on DIVISIONS level -> WATCH OUT ...28.1/...28.2
```

```{r mapDataNA,include = F, eval=eval_region_NA}
# LOAD DATA NEEDED FOR MAPS (shp, rdata, ...) ONLY FOR RCG NA
StatRectshp  = sf::st_read("../../data/shapefiles/RCG_NA_ICESrect.shp")

FAOshp  = sf::st_read("../../data/shapefiles/RCG_NA_FAOareas.shp") %>% filter(F_LEVEL == 'DIVISION') # for NA maps on DIVISIONS level

```

```{r mapDataNSEA, include = F, eval=eval_region_NSEA}
# LOAD DATA NEEDED FOR MAPS (shp, rdata, ...) ONLY FOR RCG NSEA
StatRectshp  = sf::st_read("../../data/shapefiles/RCG_NSEA_ICESrect.shp")

FAOshp  = sf::st_read("../../data/shapefiles/RCG_NSEA_FAOareas.shp") %>%  filter(F_LEVEL == 'DIVISION' |
                                                                                   F_LEVEL == 'SUBAREA' |
                                                                                   F_CODE == '27.3.a.20' | 
                                                                                   F_CODE == '27.3.a.21')

```

```{r mapDataPrepare, echo=FALSE, warning = FALSE, message = FALSE}
# PREPARE DATA NEEDED FOR MAPS (shp, rdata, ...)
#StatRectshp %>% mutate(StatisticalRectangle = ICESNAME) -> StatRectshp
StatRectshp = cbind(StatRectshp,  sf::st_coordinates(sf::st_centroid(StatRectshp$geometry))) %>% rename(lon = X, lat = Y)

FAOshp = cbind(FAOshp,  sf::st_coordinates(sf::st_centroid(FAOshp$geometry))) %>% rename(lon = X, lat = Y)

if(params$region=='BA'){ # fixed wrong calculation of centroid of 27.3.d.30
  FAOshp = FAOshp %>%   
    mutate(lon = ifelse(F_CODE=='27.3.d.30', 19.5 ,lon), lat =  ifelse(F_CODE=='27.3.d.30',62 ,lat))

}

```


**Disclaimer**
The tables and figures of the overviews presented in this document are made for the coordination of EU regional fisheries data collection purposes and are not designed for any other use. Data used for producing the outputs are extracted from the Regional Database and Estimating System (RDBES). Dates of data extractions are stated in Appendix A. Due to different aggregations and reporting authorities, data can differ from those used e.g. for assessments or technical reports. 

Member States (MS) are responsible for uploading latest data and the latest year should be viewed as provisional. Data can be resubmitted by a MS for more than one previous year so there might be differences in earlier year reports, if countries update back in time. Responsibility for the quality of the data and comparability to other data sources lies with the MS that provided these data. The upload logs presented by MS regarding the data submitted to RDBES should be found in the SharePoint for Intersessional Work, under the folder "Data".

The respective scripts and calculations used for data displaying are publicly available via the RCG GitHub (https://github.com/ices-eg/RCG-RDBES-Overviews) and subject to change as the work of the group progresses.

# Introduction
The present Sampling Overview displays summary information on the statistics for EU sampling of commercial landings included in the [Regional Data Base and Estimation System (RDBES)](https://www.ices.dk/data/data-portals/Pages/rdbes.aspx), which is used to store detailed commercial fisheries and sampling data.

The RDBES is hosted at the International Council for Exploration of the Sea (ICES) and its data is property of EU Member States with usage governed by the Data use license for the Regional Database (RDB). It is a regionally coordinated database platform covering fisheries by region (e.g. North Atlantic Ocean, North Sea, Baltic Sea) and is a main resource used by the Regional Coordination Groups [(RCG)](https://www.fisheries-rcg.eu/rcg-nansea/) to coordinate data collection of EU fisheries. 

The RDBES should be seen as part of the movements towards statistically Sound Sampling Schemes (4S), greater regional coordination, transparent Assessment Framework (TAF) and improved estimates to ICES assessments. In that context, the RDBES aims also: 

1. To ensure that data can be made available for the coordination of regional fisheries data sampling plans, in particular for the EU DC-MAP Regional Coordination Groups (RCGs),
2. To provide a regional estimation system such that statistical estimates of quantities of interest can be produced from sample data,
3. To increase the data quality, documentation of data and ensuring of approved estimation methods are used,
4. To serve and facilitate the production of fisheries management advice and status reports,
5. To increase the awareness of fisheries data collected by the users of the RDBES and the overall usage of these data.

The RDBES data model is an evolution of the work already done in defining and using the current Regional Database (RDB) and the COST data models and functions.  The current RDB data model provides a common data structure to describe commercial sampling data at a disaggregated level, and commercial landings and effort data at an aggregated level.  The significant difference in the new RDBES model is that it provides a common structure to describe both the disaggregated sampling data and, most importantly, how it was sampled.

To allow for the variety of sampling designs used in different institutes and countries the RDBES identifies a number of different sampling hierarchies, which represent the different hierarchical sampling techniques that are used in practice.  Two types of hierarchy are used in the model. The upper hierarchies describe how a sample is selected, and they are numbered from 1 to 13. The lower hierarchies describe what type of length-frequency or biological variables are measured for that sample, and they are named with the letters from A to D.  All hierarchies are defined in terms of the tables they consist of and the relationships between them. 

## Reading the graphs
### Barplots
put some text here

### Maps
put some text here

# Commercial fishery sampling overview

## General information
Following report base on `r params$year` sampling data uploaded to the RDBES data portal.

### Sample information
**Table 1.** The total number of records in Sample Details (SD) by hierarchies including national and regional routines. The number of records related to regional sampling schames is presented in brackets.
```{r sample_information, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6}

source("scripts/SD.R")

#print result
kable(combined, align = "c")|>
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE) |>
  column_spec(1, width = "4cm")|>
  column_spec(2:ncol(combined), width = "3cm")

```

### Samples data 
#### Number of species in Sample (SA)
**Table 2** Number of unique species in Sample (SA) by hierarchies. In the Total column and row, there are unique species counts depending on the aggregation specified in the table.

```{r sample_data, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width = 6, fig.height = 6}

source("scripts/SAspecies.R")

kable(SAsummary, align = "c")|>
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE) |>
  column_spec(1, width = "4cm")|>
  column_spec(2:ncol(combined), width = "3cm")
```

#### Number of records in Frequency Measure (FM) and Biological Measurement (BV) 
**Table 3** Number of records in Frequency Measure (FM) by hierarchies. The table shows the number of records in FM for hierarchies A and B. Hierarchy B is shown in brackets.
```{r FM, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width = 6, fig.height = 6}

source("scripts/FMBVrecords.R")

#print result
kable(combined, align = "c")|>
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE) |>
  column_spec(1, width = "4cm")|>
  column_spec(2:ncol(combined), width = "3cm")
```

**Table 4** Number of records in Biological Measurement (BV) under Frequency Measure(lower hierarchy A) and Sample (SA)(lower hierarchy C). Number of records under Sample (SA)(hierarchy C) is shown in brackets.
```{r BV, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width = 6, fig.height = 6}

source("scripts/BVrecords.R")

# delete columns with ".y"
combined <- combined |>
  select(-ends_with(".y"))|>
  mutate(across(everything(), ~ gsub("\\(NA\\)", "", .)),
         across(everything(), ~ gsub("\\(0\\)", "", .)),
         across(everything(), ~ gsub("\\(\\)", "", .)))

#print result
kable(combined, align = "c")|>
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE) |>
  column_spec(1, width = "4cm")|>
  column_spec(2:ncol(combined), width = "3cm")
```

**Table 5** Types of biological measurement measured in Biological Measurement (BV) with number of records.
 
```{r BVtypeMeas, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width = 6, fig.height = 6}

source("scripts/BVtypeMeasSummary.R")

kable(BVtypeMeasSummary,format.args = list( big.mark = " "))

```


without NAs
```{r BVtypeMeaTest, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width = 6, fig.height = 6}

cs|> 
  select(BVtypeMeas, BVid,BVvalueMeas) |>
  filter(!is.na(BVid) & BVid !="" & !is.na(BVvalueMeas) & BVvalueMeas != "") |>
  distinct() |>
  group_by(BVtypeMeas) |>
  count() |>
  arrange(desc(n)) |>
  pivot_wider(names_from = BVtypeMeas, values_from = n) |>
  rowwise() |>
  mutate(Total = sum(c_across(where(is.numeric)), na.rm = TRUE)) -> BVtypeMeasSummarytest

kable(BVtypeMeasSummarytest,format.args = list( big.mark = " "))



```
### Frequency Measured data 
####	Number of measured individuals
```{r FMnumberAtUnit, echo=FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width = 6, fig.height = 6, fig.cap="**Figure 1** add caption."}
sub_cs<- cs |>
  select(SDctry,FMnumAtUnit,FMid,FMtypeMeas) |>
  filter(!is.na(FMid) & FMid!="",
         grepl("Length", FMtypeMeas)) |>
  distinct() |>
  group_by(SDctry,FMnumAtUnit) |>
  summarise(NumLengthFish = sum(FMnumAtUnit)) |>
  top_n(20, wt=NumLengthFish)

barplot(data = sub_cs, 
      x = "SDctry",
      y = "NumLengthFish",
      ylab = "Number of fish measured")
```

####	Type of Length Measured
```{r TypeLength, echo=FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width = 6, fig.height = 6, fig.cap="**Figure 1** add caption."}
sub_cs <- cs |>
  select(SpeciesLaName, FMnumAtUnit,FMid,FMtypeMeas) |>
  filter(!is.na(FMid) & FMid!="") |>
  distinct() |>
  group_by(SpeciesLaName, FMtypeMeas) |>
  summarise(NumLengthFish = sum(FMnumAtUnit, na.rm=T)) |>
  group_by(SpeciesLaName) |>
  mutate(NMeas = length(FMtypeMeas)) |>
  filter(NMeas>1) |>
  pivot_wider(names_from = FMtypeMeas, values_from = NumLengthFish) |>
  select(-NMeas) 

# I group all species having pinched length and total length. They are all spanish 
# For NA and NSEA
  sub_cs_Pinched <- sub_cs |>
  filter(!is.na(LengthTotal) & !is.na(LengthPinchedTail)) |>
  mutate(SpeciesLaName = paste(nrow(sub_cs), " species (may include stock assesed sp"))|>
  summarise_all(sum)


sub_cs_Rest <- sub_cs |>
  filter(!(!is.na(LengthTotal) & !is.na(LengthPinchedTail)))

sub_cs <- rbind(sub_cs_Pinched, sub_cs_Rest)

#print result
kable(sub_cs, align = "c")|>
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE) 



```





### Biological data 
#### Number of aged individuals 
```{r age, echo=FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width = 6, fig.height = 6, fig.cap="**Figure 2** add caption."}
sub_cs<- cs |>
  select(SDctry,BVvalueMeas,BVid,BVtypeMeas) |>
  filter(!is.na(BVid) & BVid!="",
         grepl("Age", BVtypeMeas),
         BVvalueMeas != "") |>
  distinct() |>
  group_by(SDctry) |>
  count() |>
  rename(NumAgeFish = n) |>
  top_n(20, wt=NumAgeFish)

barplot(data = sub_cs, 
      x = "SDctry",
      y = "NumAgeFish",
      ylab = "Number of fish with age")
```

#### Number of weight individuals 
```{r weight, echo=FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width = 6, fig.height = 6, fig.cap="**Figure 3** Records with weight. If fish have many types of weight in this statistics it will be counted as one."}
sub_cs<- cs |>
  select(SDctry,BVvalueMeas,BVfishId,BVid,BVtypeMeas) |>
  filter(!is.na(BVfishId) & BVfishId!="",
         grepl("Weight", BVtypeMeas),
         BVvalueMeas != "") |>
  mutate(BVtypeMeas = substr(BVtypeMeas,1,6)) |>
  distinct() |>
  group_by(SDctry) |>
  count() |>
  rename(NumWeightFish = n) |>
  top_n(20, wt=NumWeightFish)

barplot(data = sub_cs, 
      x = "SDctry",
      y = "NumWeightFish",
      ylab = "Number of fish with weight")
```

#### Number of maturity individuals 
```{r maturity, echo=FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width = 6, fig.height = 6, fig.cap="**Figure 4** add caption."}
sub_cs<- cs |>
  select(SDctry,BVvalueMeas,BVid,BVtypeMeas) |>
  filter(!is.na(BVid) & BVid!="",
         grepl("Maturity", BVtypeMeas),
         BVvalueMeas != "") |>
  distinct() |>
  group_by(SDctry) |>
  count() |>
  rename(NumMaturityFish = n) |>
  top_n(20, wt=NumMaturityFish)

barplot(data = sub_cs, 
      x = "SDctry",
      y = "NumMaturityFish",
      ylab = "Number of fish with maturity")
```

#### Number of sex individuals 
```{r sex, echo=FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width = 6, fig.height = 6, fig.cap="**Figure 5** add caption."}
sub_cs<- cs |>
  select(SDctry,BVvalueMeas,BVid,BVtypeMeas) |>
  filter(!is.na(BVid) & BVid!="",
         grepl("Sex", BVtypeMeas),
         BVvalueMeas != "") |>
  distinct() |>
  group_by(SDctry) |>
  count() |>
  rename(NumSexFish = n) |>
  top_n(20, wt=NumSexFish)

barplot(data = sub_cs, 
      x = "SDctry",
      y = "NumSexFish",
      ylab = "Number of fish with sex")
```


### Number of fish analyzed in all types of biological measurements

```{r BVfishid, echo=FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width = 6, fig.height = 6}
# testowo do wyrzucenia jak wyjaśni się kwestia z długością
sub_cs<- cs |>
    filter(!is.na(BVid) & BVid!="",
         !is.na(SAid) & SAid!="",
         !is.na(BVfishId) & BVfishId!="",
         BVvalueMeas !="") |>
  select(BVfishId,BVtypeMeas,SAid,BVid,SDctry,BVvalueMeas) |>
  mutate(FishId = paste0(SAid,"_",BVfishId),
         BVFishidlen=nchar(as.character(BVfishId))) |>
  distinct() |>
  group_by(BVtypeMeas) |>
  count() |>
  rename(NumFish = n) |>
  top_n(20, wt=NumFish)
#od tego
# sub_cs<- cs |>
#     filter(!is.na(BVid) & BVid!="",
#          !is.na(SAid) & SAid!="",
#          !is.na(BVfishId) & BVfishId!="",
#          BVvalueMeas !="") |>
#     mutate(FishId = paste0(SAid,"_",BVfishId)) |>
#   select(FishId,BVtypeMeas,SAlowHierarchy) |>
#   distinct()|>
#   group_by(FishId,SAlowHierarchy) |>
#   arrange(BVtypeMeas) |>
#   mutate(temp = BVtypeMeas) |>
#   pivot_wider(names_from = BVtypeMeas, values_from = temp)|>
#   mutate(across(everything(), ~ replace_na(as.character(.), "_")))
# 
# # do tego
# a <- colnames(sub_cs[,3:ncol(sub_cs)])
# sub_csa <- sub_cs |>
#   distinct()|>
#   rowwise() %>%
#   mutate(temp1 = paste(c_across(all_of(a)), collapse = "_")) |> #colnames(sub_cs[,3:ncol(sub_cs)])
#   group_by(temp1,SAlowHierarchy) |>
#   count() |>
#   arrange(desc(n)) |>
#   arrange(SAlowHierarchy) |>
#   pivot_wider(names_from = SAlowHierarchy, values_from = n) |>
#   mutate(across(everything(), ~ replace_na(as.character(.), "")))
# #liczby muszą się zgadzać ale nadal coś tam jest namieszane liczba rekordów jest inna niż w tabelach wyżej

#print result
kable(sub_cs, align = "c")|>
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE) 
```
## Biological information per species
BVfishid number of fish analyzed in top 3/4 types of biological measurements

<!-- cs |> -->
<!--   group_by(DEhierarchy,SDctry)|> -->
<!--   count() -> temp_n_records -->

<!-- cs |> -->
<!--   group_by(DEhierarchy,SDctry, FTsampType)|> -->
<!--   count() -> temp_n_rec -->

<!-- kable(temp_n_records) -->
<!-- kable(temp_n_rec) -->
Some results from summaryBiologicalVar function ->


## Biological information by species
## Appendix A