---
title: "RDBES Sampling Overview"
date: "`r format(Sys.time(), '%d.%m.%Y')`"
output:
  html_document:
    toc: true
    fig_caption: yes
    
params:
  set_subtitle: "Title"
  region: 'BA'
  year: 2024
  logo_path: "../../data/logo/logo RCG BALTIC.PNG" # logo RCG NA NS_EA.PNG OR logo RCG BALTIC.PNG
  data_dir_CS: '../../data_RDBES/002_prepared/20250521/RCG_BA'
  data_dir_CL: '../../data_RDBES/002_prepared/20250527/RCG_BA'
  data_dir_CE: '../../data_RDBES/002_prepared/20250527/RCG_BA'
  RDBES_download_date: '20/05/2025'
  CSfileName: 'RDBES_RCG_BA_CS_2024_2024_prepared_20250521'
  CLfileName: 'RDBES_RCG_BA_CL_2024_2024_prepared_20250527'
  CEfileName: 'RDBES_RCG_BA_CE_2024_2024_prepared_20250527'

  
---

---
subtitle: `r paste(dplyr::case_when(params$region=='BA'~'Baltic',params$region=='NA'~'North Atlantic',params$region=='NSEA'~'North Sea and Eastern Arctic'), params$year, sep = ", ")`
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
```

```{r, echo=FALSE}
  htmltools::img(src = knitr::image_uri(params$logo_path), 
               alt = 'logo', 
               style = 'position:absolute; top:0; right:0; padding:10px;',width="300px", height="100px")
```

```{r Define_eval, echo=FALSE, message=FALSE, warning=FALSE}
# DEFINE EVAL_PARAMETERS

 ## establish conditions  - can use it if for example some chunks should be run only for selected Regions, e.g. only Bal
 eval_region_BA <- params$region=='BA' # when added to the chunk header, the chunk will be run only for BA report
 eval_region_NA <- params$region=='NA' # when added to the chunk header, the chunk will be run only for NA report
 eval_region_NSEA <- params$region=='NSEA' # when added to the chunk header, the chunk will be run only for NSEA report

```

```{r GlobalSettings, echo=FALSE}
# DEFINE GLOBAL PARAMETERS/FUNCTIONS FOR DISPLAYING TABLES/PLOTS/MAPS/...

```


```{r mapData, echo=FALSE}
# LOAD DATA NEEDED FOR MAPS (shp, rdata, ...) FOR ALL RCGs
UNLOCODE %>%
  mutate(Harbour = loCode) %>%
  filter(!is.na(Harbour)) %>%
  select(Harbour, lat, lon) -> Harbours
```

```{r mapDataBA, include = F, eval=eval_region_BA}
# LOAD PREPARE DATA NEEDED FOR MAPS (shp, rdata, ...) ONLY FOR RCG BA
StatRectshp  = sf::st_read("../../data/shapefiles/RCG_BA_ICESrect.shp")# for BA maps on DIVISIONS level -> WATCH OUT ...28.1/...28.2

FAOshp  = sf::st_read("../../data/shapefiles/RCG_BA_FAOareas.shp") %>% filter(F_LEVEL == 'SUBDIVISION') # for BA maps on DIVISIONS level -> WATCH OUT ...28.1/...28.2
```

```{r mapDataNA,include = F, eval=eval_region_NA}
# LOAD DATA NEEDED FOR MAPS (shp, rdata, ...) ONLY FOR RCG NA
StatRectshp  = sf::st_read("../../data/shapefiles/RCG_NA_ICESrect.shp")

FAOshp  = sf::st_read("../../data/shapefiles/RCG_NA_FAOareas.shp") %>% filter(F_LEVEL == 'DIVISION') # for NA maps on DIVISIONS level

```

```{r mapDataNSEA, include = F, eval=eval_region_NSEA}
# LOAD DATA NEEDED FOR MAPS (shp, rdata, ...) ONLY FOR RCG NSEA
StatRectshp  = sf::st_read("../../data/shapefiles/RCG_NSEA_ICESrect.shp")

FAOshp  = sf::st_read("../../data/shapefiles/RCG_NSEA_FAOareas.shp") %>%  filter(F_LEVEL == 'DIVISION' |
                                                                                   F_LEVEL == 'SUBAREA' |
                                                                                   F_CODE == '27.3.a.20' | 
                                                                                   F_CODE == '27.3.a.21')

```

```{r mapDataPrepare, echo=FALSE, warning = FALSE, message = FALSE}
# PREPARE DATA NEEDED FOR MAPS (shp, rdata, ...)
#StatRectshp %>% mutate(StatisticalRectangle = ICESNAME) -> StatRectshp
StatRectshp = cbind(StatRectshp,  sf::st_coordinates(sf::st_centroid(StatRectshp$geometry))) %>% rename(lon = X, lat = Y)

FAOshp = cbind(FAOshp,  sf::st_coordinates(sf::st_centroid(FAOshp$geometry))) %>% rename(lon = X, lat = Y)

if(params$region=='BA'){ # fixed wrong calculation of centroid of 27.3.d.30
  FAOshp = FAOshp %>%   
    mutate(lon = ifelse(F_CODE=='27.3.d.30', 19.5 ,lon), lat =  ifelse(F_CODE=='27.3.d.30',62 ,lat))

}

```


**Disclaimer**
The tables and figures of the overviews presented in this document are made for the coordination of EU regional fisheries data collection purposes and are not designed for any other use. Data used for producing the outputs are extracted from the Regional Database and Estimating System (RDBES). Dates of data extractions are stated in Appendix A. Due to different aggregations and reporting authorities, data can differ from those used e.g. for assessments or technical reports. 

Member States (MS) are responsible for uploading latest data and the latest year should be viewed as provisional. Data can be resubmitted by a MS for more than one previous year so there might be differences in earlier year reports, if countries update back in time. Responsibility for the quality of the data and comparability to other data sources lies with the MS that provided these data. The upload logs presented by MS regarding the data submitted to RDBES should be found in the SharePoint for Intersessional Work, under the folder "Data".

The respective scripts and calculations used for data displaying are publicly available via the RCG GitHub (https://github.com/ices-eg/RCG-RDBES-Overviews) and subject to change as the work of the group progresses.

# Introduction
The present Sampling Overview displays summary information on the statistics for EU sampling of commercial landings included in the [Regional Data Base and Estimation System (RDBES)](https://www.ices.dk/data/data-portals/Pages/rdbes.aspx), which is used to store detailed commercial fisheries and sampling data.

The RDBES is hosted at the International Council for Exploration of the Sea (ICES) and its data is property of EU Member States with usage governed by the Data use license for the Regional Database (RDB). It is a regionally coordinated database platform covering fisheries by region (e.g. North Atlantic Ocean, North Sea, Baltic Sea) and is a main resource used by the Regional Coordination Groups [(RCG)](https://www.fisheries-rcg.eu/rcg-nansea/) to coordinate data collection of EU fisheries. 

The RDBES should be seen as part of the movements towards statistically Sound Sampling Schemes (4S), greater regional coordination, transparent Assessment Framework (TAF) and improved estimates to ICES assessments. In that context, the RDBES aims also: 

1. To ensure that data can be made available for the coordination of regional fisheries data sampling plans, in particular for the EU DC-MAP Regional Coordination Groups (RCGs),
2. To provide a regional estimation system such that statistical estimates of quantities of interest can be produced from sample data,
3. To increase the data quality, documentation of data and ensuring of approved estimation methods are used,
4. To serve and facilitate the production of fisheries management advice and status reports,
5. To increase the awareness of fisheries data collected by the users of the RDBES and the overall usage of these data.

The RDBES data model is an evolution of the work already done in defining and using the Regional Database (RDB) and the COST data models and functions.  The RDB data model provided a common data structure to describe commercial sampling data at a disaggregated level, and commercial landings and effort data at an aggregated level.  The significant difference for the new RDBES model is that this provides a common structure to describe both the disaggregated sampling data and, most importantly, how it was sampled.

To allow for the variety of sampling designs used in different institutes and countries the RDBES identifies a number of different sampling hierarchies, which represent the different hierarchical sampling techniques that are used in practice.  Two types of hierarchies are used in the model. The upper hierarchies describe how a sample is selected, and they are numbered from 1 to 13. The lower hierarchies describe what type of length-frequency or biological variables are measured for that sample, and they are named with the letters from A to D.  All hierarchies are defined in terms of the tables they consist of and the relationships between them. 

## Reading the graphs
### Barplots
Inventory data are displayed using barplots where it's presented the desired quantitative sampling variable by a certain categorical variable on the X-axis (e.g. country).

### Maps
No spatial information is available yet. 

# Commercial fishery sampling overview

## General information
This report is based on `r params$year` sampling data uploaded to the RDBES data portal.

### Sample information

**Table 1.** The total number of records in Sample Details (SD) by hierarchy, including national and regional routines. The number of records related to regional sampling schemes is presented in brackets.

```{r sample_information, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6}

source("scripts/SD.R")

#print result
kable(combined, align = "c")|>
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE) |>
  column_spec(1, width = "4cm")|>
  column_spec(2:ncol(combined), width = "3cm")

```
<br>

### Samples data 
#### Number of species in Sample (SA)
**Table 2** Number of unique species in Sample table (SA) by hierarchy. The 'Total' column and row refer to unique species counts by country and hierarchy, respectively.

```{r sample_data, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width = 6, fig.height = 6}

source("scripts/SAspecies.R")

kable(SAsummary, align = "c")|>
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE) |>
  column_spec(1, width = "4cm")|>
  column_spec(2:ncol(combined), width = "3cm")
```
<br>

#### Number of records in Frequency Measure (FM) and Biological Variables (BV) 
**Table 3** Number of records in Frequency Measure (FM) by hierarchy. The table shows the number of records in FM for hierarchies A and B. Hierarchy B is shown in brackets.
```{r FM, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width = 6, fig.height = 6}

source("scripts/FMBVrecords.R")

#print result
kable(combined, align = "c")|>
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE) |>
  column_spec(1, width = "4cm")|>
  column_spec(2:ncol(combined), width = "3cm")
```
<br>

**Table 4** Number of records in Biological Variable (BV) under Frequency Measure (FM) (lower hierarchy A) and Sample (SA). The number of records under Sample (SA) is shown in brackets.
```{r BV, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width = 6, fig.height = 6}

source("scripts/BVrecords.R")

# delete columns with ".y"
combined <- combined |>
  select(-ends_with(".y"))|>
  mutate(across(everything(), ~ gsub("\\(NA\\)", "", .)),
         across(everything(), ~ gsub("\\(0\\)", "", .)),
         across(everything(), ~ gsub("\\(\\)", "", .)))

#print result
kable(combined, align = "c")|>
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE) |>
  column_spec(1, width = "4cm")|>
  column_spec(2:ncol(combined), width = "3cm")

```

<br>

**Table 5** Total number of records by biological variable, present in table BV. a) includes NA reported values; b) without NA's.

##### a)
 
```{r BVtypeMeas, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width = 6, fig.height = 6}

source("scripts/BVtypeMeasSummary.R")

kable(BVtypeMeasSummary,format.args = list( big.mark = " "))

```


##### b) 

```{r BVtypeMeaTest, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width = 6, fig.height = 6}

cs|> 
  select(BVtypeMeas, BVid,BVvalueMeas) |>
  filter(!is.na(BVid) & BVid !="" & !is.na(BVvalueMeas) & BVvalueMeas != "") |>
  distinct() |>
  group_by(BVtypeMeas) |>
  count() |>
  arrange(desc(n)) |>
  pivot_wider(names_from = BVtypeMeas, values_from = n) |>
  rowwise() |>
  mutate(Total = sum(c_across(where(is.numeric)), na.rm = TRUE)) -> BVtypeMeasSummarytest

kable(BVtypeMeasSummarytest,format.args = list( big.mark = " "))



```
<br>

### Frequency Measure data 

<br>

####	Number of measured individuals

```{r FMnumberAtUnit, echo=FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width = 6, fig.height = 6, fig.cap="**Figure 1** Number of individuals measured by country. (source data: FM)"}
sub_cs<- cs |>
  select(SDctry,FMnumAtUnit,FMid,FMtypeMeas) |>
  filter(!is.na(FMid) & FMid!="",
         grepl("Length", FMtypeMeas)) |>
  distinct() |>
  group_by(SDctry,FMnumAtUnit) |>
  summarise(NumLengthFish = sum(FMnumAtUnit)) |>
  top_n(20, wt=NumLengthFish)

## Option 1: this one orders the x-axis from the higher to the lower bars

# barplot(data = sub_cs,
#       x = "SDctry",
#       y = "NumLengthFish",
#       ylab = "Number of individuals measured") 

## Option 2: this one keeps the x-axis ordered alphabetically
barplot1(data = sub_cs,
						 x = "SDctry",
						 y = "NumLengthFish",
						 xlab = "Country",
						 ylab = "Number of individuals measured",
						 title = ""
						 )
```
<br>

####	Type of Length Measured
<br>

**Table 6** Species that have more than one type of length measurement in the Frequency Measure table.

```{r TypeLength, echo=FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width = 6, fig.height = 6, fig.cap=""}
sub_cs <- cs |>
  select(SpeciesLaName, FMnumAtUnit, FMid, FMtypeMeas) |>
  filter(!is.na(FMid) & FMid!="") |>
  distinct() |>
  group_by(SpeciesLaName, FMtypeMeas) |>
  summarise(NumLengthFish = sum(FMnumAtUnit, na.rm=T)) |>
  group_by(SpeciesLaName) |>
  mutate(NMeas = length(FMtypeMeas)) |>
  filter(NMeas>1) |>
  pivot_wider(names_from = FMtypeMeas, values_from = NumLengthFish) |>
  select(-NMeas) 

data.table(sub_cs)

```
<br>


### Biological data 
<br>

#### Number of aged individuals 
```{r age, echo=FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width = 6, fig.height = 6, fig.cap="**Figure 2** Number of individuals aged by country. (source data: BV)"}

sub_cs<- cs |>
  select(SDctry,BVvalueMeas,BVid,BVtypeMeas) |>
  filter(!is.na(BVid) & BVid!="",
         grepl("Age", BVtypeMeas),
         BVvalueMeas != "") |>
  distinct() |>
  group_by(SDctry) |>
  count() |>
  rename(NumAgeFish = n) |>
  top_n(20, wt=NumAgeFish)

## Option 1:
# barplot(data = sub_cs, 
#       x = "SDctry",
#       y = "NumAgeFish",
#       ylab = "Number of individuals with age") 

## Option 2:
barplot1(data = sub_cs,
						 x = "SDctry",
						 y = "NumAgeFish",
						 xlab = "Country",
						 ylab = "Number of individuals with age",
						 title = ""
						 )

     
```
<br>

#### Number of weighted individuals 
```{r weight, echo=FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width = 6, fig.height = 6, fig.cap="**Figure 3** Number of records with weight. If individuals have different types of weight, it will be counted as one.(source data: BV)"}

sub_cs<- cs |>
  select(SDctry,BVvalueMeas,BVfishId,BVid,BVtypeMeas) |>
  filter(!is.na(BVfishId) & BVfishId!="",
         grepl("Weight", BVtypeMeas),
         BVvalueMeas != "") |>
  mutate(BVtypeMeas = substr(BVtypeMeas,1,6)) |>
  distinct() |>
  group_by(SDctry) |>
  count() |>
  rename(NumWeightFish = n) |>
  top_n(20, wt=NumWeightFish)

## Option 1:
# barplot(data = sub_cs, 
#       x = "SDctry",
#       y = "NumWeightFish",
#       ylab = "Number of individuals with weight")


## Option 2: country-specific
barplot1(data = sub_cs,
						 x = "SDctry",
						 y = "NumWeightFish",
						 xlab = "Country",
						 ylab = "Number of individuals with weight",
						 title = ""
						 )


```
<br>

#### Number of individuals with maturity 

```{r maturity, echo=FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width = 6, fig.height = 6, fig.cap="**Figure 4** Number of individuals with maturity by country. (source data: BV)."}
sub_cs<- cs |>
  select(SDctry,BVvalueMeas,BVid,BVtypeMeas) |>
  filter(!is.na(BVid) & BVid!="",
         grepl("Maturity", BVtypeMeas),
         BVvalueMeas != "") |>
  distinct() |>
  group_by(SDctry) |>
  count() |>
  rename(NumMaturityFish = n) |>
  top_n(20, wt=NumMaturityFish)

## Option 1: 
# barplot(data = sub_cs, 
#       x = "SDctry",
#       y = "NumMaturityFish",
#       ylab = "Number of individuals with maturity")

## Option 2:
barplot1(data = sub_cs,
						 x = "SDctry",
						 y = "NumMaturityFish",
						 xlab = "Country",
						 ylab = "Number of individuals with maturity",
						 title = ""
						 )


```
<br>

#### Number of sexed individuals

```{r sex, echo=FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width = 6, fig.height = 6, fig.cap="**Figure 5** Number of sexed individuals. (source data: BV)."}

sub_cs<- cs |>
  select(SDctry,BVvalueMeas,BVid,BVtypeMeas) |>
  filter(!is.na(BVid) & BVid!="",
         grepl("Sex", BVtypeMeas),
         BVvalueMeas != "") |>
  distinct() |>
  group_by(SDctry) |>
  count() |>
  rename(NumSexFish = n) |>
  top_n(20, wt=NumSexFish)

## Option 1: 
# barplot(data = sub_cs, 
#       x = "SDctry",
#       y = "NumSexFish",
#       ylab = "Number of individuals with sex")

## Option 2:
barplot1(data = sub_cs,
						 x = "SDctry",
						 y = "NumSexFish",
						 xlab = "Country",
						 ylab = "Number of individuals with sex",
						 title = ""
						 )


```

<br>

### Number of individuals in all types of biological variables

The table below summarises all the information (number of individuals) reported by biological variable. (source data: BV)

```{r BVfishid, echo=FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width = 6, fig.height = 6}
# testowo do wyrzucenia jak wyjaśni się kwestia z długością
sub_cs<- cs |>
    filter(!is.na(BVid) & BVid!="",
         !is.na(SAid) & SAid!="",
         !is.na(BVfishId) & BVfishId!="",
         BVvalueMeas !="") |>
  select(BVfishId,BVtypeMeas,SAid,BVid,SDctry,BVvalueMeas) |>
  mutate(FishId = paste0(SAid,"_",BVfishId),
         BVFishidlen=nchar(as.character(BVfishId))) |>
  distinct() |>
  group_by(BVtypeMeas) |>
  count() |>
  rename(NumFish = n) |>
  top_n(20, wt=NumFish)

#od tego
# sub_cs<- cs |>
#     filter(!is.na(BVid) & BVid!="",
#          !is.na(SAid) & SAid!="",
#          !is.na(BVfishId) & BVfishId!="",
#          BVvalueMeas !="") |>
#     mutate(FishId = paste0(SAid,"_",BVfishId)) |>
#   select(FishId,BVtypeMeas,SAlowHierarchy) |>
#   distinct()|>
#   group_by(FishId,SAlowHierarchy) |>
#   arrange(BVtypeMeas) |>
#   mutate(temp = BVtypeMeas) |>
#   pivot_wider(names_from = BVtypeMeas, values_from = temp)|>
#   mutate(across(everything(), ~ replace_na(as.character(.), "_")))
# 
# # do tego
# a <- colnames(sub_cs[,3:ncol(sub_cs)])
# sub_csa <- sub_cs |>
#   distinct()|>
#   rowwise() %>%
#   mutate(temp1 = paste(c_across(all_of(a)), collapse = "_")) |> #colnames(sub_cs[,3:ncol(sub_cs)])
#   group_by(temp1,SAlowHierarchy) |>
#   count() |>
#   arrange(desc(n)) |>
#   arrange(SAlowHierarchy) |>
#   pivot_wider(names_from = SAlowHierarchy, values_from = n) |>
#   mutate(across(everything(), ~ replace_na(as.character(.), "")))
# #liczby muszą się zgadzać ale nadal coś tam jest namieszane liczba rekordów jest inna niż w tabelach wyżej

#print result
kable(sub_cs, align = "c")|>
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE) 
```

<br>
## Biological information per species
BVfishid number of fish analyzed in top 3/4 types of biological measurements

<!-- cs |> -->
<!--   group_by(DEhierarchy,SDctry)|> -->
<!--   count() -> temp_n_records -->

<!-- cs |> -->
<!--   group_by(DEhierarchy,SDctry, FTsampType)|> -->
<!--   count() -> temp_n_rec -->

<!-- kable(temp_n_records) -->
<!-- kable(temp_n_rec) -->

<br>

## Sampling coverage

The figures below present the total landings and the number of Primary Sampling Units (PSU) collected (trips (FT), fishing operation (FO) or landing events (LE), depending on the hierarchy used).

### Area vs Gear

```{r , echo=FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width = 6, fig.height = 6}
  
  cl_data <- cl_rcg
  cl_data$Region <- ifelse(cl_data$Region=="NA"|is.na(cl_data$Region),'NATL',cl_data$Region)
  
  cs |>
    filter(SAcatchCat %in% c('Lan', 'Catch'),!is.na(SAid) &
             SAid != "",
           DEhierarchy != 13) |>
    select(FTid,FOid,LEid,DEhierarchy,metier6,DEyear,SDctry,VDlenCat,SAsampWtLive,Area,SpeciesLaName)|>
    mutate(Trip_id = ifelse((!is.na(FTid) &
                               FTid != "") &
                              (is.na(LEid) | LEid == ""), FTid, LEid)) |>
    mutate(Trip_id = as.character(ifelse(
      Trip_id == "" & DEhierarchy == 13, FOid, Trip_id
    ))) |>
    rename(
      MetierLvl6 = metier6,
      Year = DEyear,
      FlagCountry = SDctry,
      VesselLengthCategory = VDlenCat
    ) |>
    distinct()|>
    group_by(Year,
             FlagCountry,
             Area,
             SpeciesLaName,
             MetierLvl6,
             VesselLengthCategory) |>
    summarise(NoPSU = n_distinct(Trip_id, na.rm = TRUE),  ## suggest to use NoSamples because they can come from different sources (FT, FO and LE) (ACFernandes)
              WeigthKg = sum(SAsampWtLive/1000, na.rm =  TRUE)) -> samplingPart
  
  cl_data |>
    rename(MetierLvl6=CLmetier6,
           Year = CLyear,
           FlagCountry = CLvesselFlagCountry,
           VesselLengthCategory = CLvesselLengthCategory,
           Area = CLarea) |>
    filter(Year %in% unique(samplingPart$Year)) |>
    group_by(Year, FlagCountry, Area, 
              SpeciesLaName, 
             MetierLvl6, VesselLengthCategory )|>
    summarise(LandingsT = sum(CLscientificWeight_ton, na.rm=TRUE))-> LandingsPart
  # 
  # 
  samplingPart %>%
    full_join(LandingsPart)-> samplingVSlandings
  
  samplingVSlandings |>
    mutate(Gear = str_sub(MetierLvl6, end = 3)) %>%
    group_by(Area, Gear
             # ,SpeciesLaName, 
             # FlagCountry
             ) %>%
    summarise(
      NoPSU = sum(NoPSU, na.rm = TRUE), ## suggest to use NoSamples because they can come from different sources (FT, FO and LE) (ACFernandes)
      LandingsT = sum(LandingsT, na.rm = TRUE)
    ) |>
    mutate(NoPSU = ifelse(NoPSU == 0, NA, NoPSU)) ->
    samplingVSlandingsF
  
  
  ggplot(samplingVSlandingsF, aes(y = factor(Area),#FlagCountry),
                                  x = factor(Gear))) +        ## global aes
    geom_tile(aes(fill = LandingsT), na.rm = TRUE) +         ## to get the rect filled
    geom_point(aes(
      size = NoPSU),
      shape =1,
      stroke = 1, na.rm=T)  +    ## geom_point for circle illusion (ACF added na.rm=T)
    scale_fill_distiller(palette = "Spectral", direction = -1, trans = 'log10', na.value="transparent") +
    theme_bw() +
    theme(
     axis.text.x = element_text(angle = 45, hjust = 1),
     legend.position = "right"
    ) +
    labs(
     x ='Gear',
     y = 'Area',
     fill = "Landings (t)",
     size = "No. of PSU",
     title = "Sampling vs Landings by Area and Gear"
    )
     
```
 
<br>
  
  
### Total landings and number of samples collected - Regional routine
  
```{r eval=eval_region_BA, echo=FALSE, fig.height=6, fig.width=6, message=FALSE, warning=FALSE, dpi=100, results="asis"}
  
  cl_data <- cl_rcg
  
  cs |>
    filter(
      SAcatchCat %in% c('Lan', 'Catch'),
      !is.na(SAid) &
        SAid != "",
      DEhierarchy != 13,
      DEsampScheme == 'Baltic SPF regional',
      SpeciesLaName %in% c('Clupea harengus', 'Sprattus sprattus')
    ) |>
    select(
      FTid,
      FOid,
      LEid,
      DEhierarchy,
      metier6,
      DEyear,
      SDctry,
      VDlenCat,
      SAsampWtLive,
      Area,
      SpeciesLaName
    ) |>
    mutate(Trip_id = ifelse((!is.na(FTid) &
                               FTid != "") &
                              (is.na(LEid) |
                                 LEid == ""), FTid, LEid)) |>
    mutate(Trip_id = as.character(ifelse(
      Trip_id == "" & DEhierarchy == 13, FOid, Trip_id
    ))) |>
    rename(
      MetierLvl6 = metier6,
      Year = DEyear,
      FlagCountry = SDctry,
      VesselLengthCategory = VDlenCat
    ) |>
    distinct() |>
    group_by(Year,
             FlagCountry,
             Area,
             SpeciesLaName,
             MetierLvl6,
             VesselLengthCategory) |>
    summarise(
      NoPSU = n_distinct(Trip_id, na.rm = TRUE),
      WeigthKg = sum(SAsampWtLive / 1000, na.rm =  TRUE)
    ) -> samplingPart
  
  cl_data |>
    rename(
      MetierLvl6 = CLmetier6,
      Year = CLyear,
      FlagCountry = CLvesselFlagCountry,
      VesselLengthCategory = CLvesselLengthCategory,
      Area = CLarea
    ) |>
    filter(
      Year %in% unique(samplingPart$Year),
      SpeciesLaName %in% unique(samplingPart$SpeciesLaName)
    ) |>
    group_by(Year,
             FlagCountry,
             Area,
             SpeciesLaName,
             MetierLvl6,
             VesselLengthCategory) |>
    summarise(LandingsT = sum(CLscientificWeight_ton, na.rm = TRUE)) -> LandingsPart
  
  samplingPart %>%
    full_join(LandingsPart) -> samplingVSlandings
  
  samplingVSlandings |>
    mutate(Gear = str_sub(MetierLvl6, end = 3)) %>%
    group_by(
      #Area,
      Gear,
      SpeciesLaName,
      FlagCountry
    ) %>%
    summarise(
      NoPSU = sum(NoPSU, na.rm = TRUE),
      LandingsT = sum(LandingsT, na.rm = TRUE)
    ) |>
    mutate(NoPSU = ifelse(NoPSU == 0, NA, NoPSU)) ->
    samplingVSlandingsF
  
  
  ggplot(samplingVSlandingsF, aes(y = factor(FlagCountry), x = factor(Gear))) +  ## global aes
    facet_wrap( ~ SpeciesLaName, ncol = 1) +
    geom_tile(aes(fill = LandingsT), na.rm = TRUE) +         ## to get the rect filled
    geom_point(aes(size = NoPSU), shape = 1, stroke = 1)  +    ## geom_point for circle illusion
    scale_fill_distiller(
      palette = "Spectral",
      direction = -1,
      trans = 'log10',
      na.value = "transparent"
    ) +
    labs(
       x ='Gear',
       y = 'Country',
       fill = "Landings (t)",
       size = "No. of PSU",
       title = "Baltic SPF regional",
     ) +
    theme_bw()

```
 
```{r eval=eval_region_NA, echo=FALSE, fig.height=6, fig.width=6, message=FALSE, warning=FALSE, dpi=100, results="asis"}
cat('Regional routine is not yet performed in the North Atlantic, North Sea & Eastern Arctic.')
```

## Biological information by species

Not performed this year.

<br>


## Appendix A. Dates of data extraction

The data referring to the present year was collected under the RCG 2025 data call for the 2024 data for the Baltic Sea, North Sea, Eastern Arctic and the North Atlantic regions and the last downloaded from the system was performed on the 20th of May 2025 with the exception of information detailed in section “Overall fleet evolution” which was extracted from the EU Fleet Register (https://webgate.ec.europa.eu/fleet-europa/index_en) on the 4th of February 2025.

