---
title: "RDBES Catch and Effort Overview"
date: "`r format(Sys.time(), '%d.%m.%Y')`"
output:
  html_document:
    toc: true
    fig_caption: yes
    
params:
  set_subtitle: "Title"
  region: 'BA'
  year: 2023
  logo_path: "../../data/logo/logo RCG BALTIC.PNG"
  data_dir: '../../data_RDBES/002_prepared/20250212/RCG_BA'
  RDBES_download_date: '01/01/2000'
  CSfileName: 'RDBES_RCG_BA_CS_2023_2023_prepared_20250212'
  
---

---
subtitle: `r paste(dplyr::case_when(params$region=='BA'~'Baltic',params$region=='NA'~'North Atlantic',params$region=='NSEA'~'North Sea and Eastern Arctic'), params$year, sep = ", ")`
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
```

```{r, echo=FALSE}
  htmltools::img(src = knitr::image_uri(params$logo_path), 
               alt = 'logo', 
               style = 'position:absolute; top:0; right:0; padding:10px;',width="300px", height="100px")
```

```{r Define_eval, echo=FALSE, message=FALSE, warning=FALSE}
# DEFINE EVAL_PARAMETERS

 ## establish conditions  - can use it if for example some chunks should be run only for selected Regions, e.g. only Bal
 eval_region_BA <- params$region=='BA' # when added to the chunk header, the chunk will be run only for BA report
 eval_region_NA <- params$region=='NA' # when added to the chunk header, the chunk will be run only for NA report
 eval_region_NSEA <- params$region=='NSEA' # when added to the chunk header, the chunk will be run only for NSEA report

```

```{r GlobalSettings, echo=FALSE}
# DEFINE GLOBAL PARAMETERS/FUNCTIONS FOR DISPLAYING TABLES/PLOTS/MAPS/...

```


```{r mapData, echo=FALSE}
# LOAD DATA NEEDED FOR MAPS (shp, rdata, ...) FOR ALL RCGs
UNLOCODE %>%
  mutate(Harbour = loCode) %>%
  filter(!is.na(Harbour)) %>%
  select(Harbour, lat, lon) -> Harbours
```

```{r mapDataBA, include = F, eval=eval_region_BA}
# LOAD PREPARE DATA NEEDED FOR MAPS (shp, rdata, ...) ONLY FOR RCG BA
StatRectshp  = sf::st_read("../../data/shapefiles/RCG_BA_ICESrect.shp")# for BA maps on DIVISIONS level -> WATCH OUT ...28.1/...28.2

FAOshp  = sf::st_read("../../data/shapefiles/RCG_BA_FAOareas.shp") %>% filter(F_LEVEL == 'SUBDIVISION') # for BA maps on DIVISIONS level -> WATCH OUT ...28.1/...28.2
```

```{r mapDataNA,include = F, eval=eval_region_NA}
# LOAD DATA NEEDED FOR MAPS (shp, rdata, ...) ONLY FOR RCG NA
StatRectshp  = sf::st_read("../../data/shapefiles/RCG_NA_ICESrect.shp")

FAOshp  = sf::st_read("../../data/shapefiles/RCG_NA_FAOareas.shp") %>% filter(F_LEVEL == 'DIVISION') # for NA maps on DIVISIONS level

```

```{r mapDataNSEA, include = F, eval=eval_region_NSEA}
# LOAD DATA NEEDED FOR MAPS (shp, rdata, ...) ONLY FOR RCG NSEA
StatRectshp  = sf::st_read("../../data/shapefiles/RCG_NSEA_ICESrect.shp")

FAOshp  = sf::st_read("../../data/shapefiles/RCG_NSEA_FAOareas.shp") %>%  filter(F_LEVEL == 'DIVISION' |
                                                                                   F_LEVEL == 'SUBAREA' |
                                                                                   F_CODE == '27.3.a.20' | 
                                                                                   F_CODE == '27.3.a.21')

```

```{r mapDataPrepare, echo=FALSE, warning = FALSE, message = FALSE}
# PREPARE DATA NEEDED FOR MAPS (shp, rdata, ...)
#StatRectshp %>% mutate(StatisticalRectangle = ICESNAME) -> StatRectshp
StatRectshp = cbind(StatRectshp,  sf::st_coordinates(sf::st_centroid(StatRectshp$geometry))) %>% rename(lon = X, lat = Y)

FAOshp = cbind(FAOshp,  sf::st_coordinates(sf::st_centroid(FAOshp$geometry))) %>% rename(lon = X, lat = Y)

if(params$region=='BA'){ # fixed wrong calculation of centroid of 27.3.d.30
  FAOshp = FAOshp %>%   
    mutate(lon = ifelse(F_CODE=='27.3.d.30', 19.5 ,lon), lat =  ifelse(F_CODE=='27.3.d.30',62 ,lat))

}

```


**Disclaimer**
The tables and figures of the overviews presented in this document are made for the coordination of EU regional fisheries data collection purposes and are not designed for any other use. Data used for producing the outputs are extracted from the Regional Database and Estimating System (RDBES) and EU Fleet Register. Dates of data extractions are stated in Appendix A. Due to different aggregations and reporting authorities, data can differ from those used e.g. for assessments or technical reports. 

Member States (MS) are responsible for uploading latest data and the latest year should be viewed as provisional. Data can be resubmitted by a MS for more than one previous year so there might be differences in earlier year reports, if countries update back in time. Responsibility for the quality of the data and comparability to other data sources lies with the MS that provided these data. The upload logs presented by MS regarding the data submitted to RDBES should be found in the SharePoint for Intersessional Work, under the folder "Data".

The respective scripts and calculations used for data displaying are publicly available via the RCG GitHub (https://github.com/ices-eg/RCG-RDBES-Overviews) and subject to change as the work of the group progresses.

# Introduction
put some text

## Reading the graphs
### Barplots
put some text here

### Maps
put some text here

# Commercial fishery sampling overview

## General information
Following report base on `r params$year` sampling data uploaded to the RDBES data portal.

```{r general_table, echo=FALSE}
cs |>
  group_by(DEhierarchy,SDctry)|>
  count() -> temp_n_records

cs |>
  group_by(DEhierarchy,SDctry, FTsampType)|>
  count() -> temp_n_rec

kable(temp_n_records)
kable(temp_n_rec)

```

Some results from summaryBiologicalVar function ->

```{r, echo=FALSE}
# result <- summaryBiologicalVar(
#   cs_rcg,
#   var = 'Age',
#   year = yearSelected,
#   outputType = 'plot',
#   statistics = TRUE
# )
# result
# result1 <- summaryBiologicalVar(
#   cs_rcg,
#   var = 'Age',
#   year = yearSelected,
#   outputType = 'table',
#   statistics = TRUE
# )
# result1
```

## Appendix A