---
title: "RDBES Catch and Effort Overview"
date: "`r format(Sys.time(), '%d.%m.%Y')`"
output:
  html_document:
    toc: true
    
params:
  set_subtitle: "Title"
  region: 'BA'
  year: 2021
  logo_path: "../../data/logo/logo RCG BALTIC.PNG"
  data_dir: '../../data_RDBES/002_prepared/20240129/RCG_BA'
  data_dir_fleet: '../../RegionalOverviews/data/fleet_reg/output/2021'
  RDBES_download_date: '01/01/2000'
  CLfileName: 'RDBES_RCG_BA_CL_2021_2021_prepared_20240129'
  CEfileName: 'RDBES_RCG_BA_CE_2021_2021_prepared_20240129'
  
---

---
subtitle: `r paste(dplyr::case_when(params$region=='BA'~'Baltic',params$region=='NA'~'North Atlantic',params$region=='NSEA'~'North Sea and Eastern Arctic'), params$year, sep = ", ")`
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
```

```{r, echo=FALSE}
  htmltools::img(src = knitr::image_uri(params$logo_path), 
               alt = 'logo', 
               style = 'position:absolute; top:0; right:0; padding:10px;',width="300px", height="100px")
```

```{r loadPackages, echo=FALSE, message=FALSE, warning=FALSE}
# LOAD PACKAGES AND DEFINE EVAL_PARAMETERS IF NEEDED

library(tidyverse)
# library(car)
# library(ggrepel)
# library(knitr)
# library(kableExtra)
library(data.table)
library(rnaturalearth)
# library(magrittr)
# library(plotly)
# library(leaflet)
library(ggplot2)
library(patchwork)
library(networkD3)

 ## establish conditions  - can use it if for example some chunks should be run only for selected Regions, e.g. only Bal
 eval_region_BA <- params$region=='BA' # when added to the chunk header, the chunk will be run only for BA report
 eval_region_NA <- params$region=='NA' # when added to the chunk header, the chunk will be run only for NA report
 eval_region_NSEA <- params$region=='NSEA' # when added to the chunk header, the chunk will be run only for NSEA report

```

```{r GlobalSettings, echo=FALSE}
# DEFINE GLOBAL PARAMETERS/FUNCTIONS FOR DISPLAYING TABLES/PLOTS/MAPS/...

```

```{r loadFunctions, echo=FALSE}
# LOAD FUNCTIONS GENERATING PLOTS/MAPS
source("../../funs_RDBES/choroplethMap_func2.R", local = knitr::knit_global())

#load barplot fuction
source("../../funs_RDBES/func_barplot.R", local = knitr::knit_global())

```

```{r mapData, echo=FALSE}
# LOAD DATA NEEDED FOR MAPS (shp, rdata, ...) FOR ALL RCGs

```

```{r mapDataBA, include = F, eval=eval_region_BA}
# LOAD PREPARE DATA NEEDED FOR MAPS (shp, rdata, ...) ONLY FOR RCG BA
StatRectshp  = sf::st_read("../../data/shapefiles/RCG_BA_ICESrect.shp")# for BA maps on DIVISIONS level -> WATCH OUT ...28.1/...28.2

FAOshp  = sf::st_read("../../data/shapefiles/RCG_BA_FAOareas.shp") %>% filter(F_LEVEL == 'SUBDIVISION') # for BA maps on DIVISIONS level -> WATCH OUT ...28.1/...28.2
```

```{r mapDataNA,include = F, eval=eval_region_NA}
# LOAD DATA NEEDED FOR MAPS (shp, rdata, ...) ONLY FOR RCG NA
StatRectshp  = sf::st_read("../../data/shapefiles/RCG_NA_ICESrect.shp")

FAOshp  = sf::st_read("../../data/shapefiles/RCG_NA_FAOareas.shp") %>% filter(F_LEVEL == 'DIVISION') # for NA maps on DIVISIONS level

```

```{r mapDataNSEA, include = F, eval=eval_region_NSEA}
# LOAD DATA NEEDED FOR MAPS (shp, rdata, ...) ONLY FOR RCG NSEA
StatRectshp  = sf::st_read("../../data/shapefiles/RCG_NSEA_ICESrect.shp")

FAOshp  = sf::st_read("../../data/shapefiles/RCG_NSEA_FAOareas.shp") %>%  filter(F_LEVEL == 'DIVISION' |
                                                                                   F_LEVEL == 'SUBAREA' |
                                                                                   F_CODE == '27.3.a.20' | 
                                                                                   F_CODE == '27.3.a.21')

```

```{r mapDataPrepare, echo=FALSE, warning = FALSE, message = FALSE}
# PREPARE DATA NEEDED FOR MAPS (shp, rdata, ...)
#StatRectshp %>% mutate(StatisticalRectangle = ICESNAME) -> StatRectshp
StatRectshp = cbind(StatRectshp,  sf::st_coordinates(sf::st_centroid(StatRectshp$geometry))) %>% rename(lon = X, lat = Y)

FAOshp = cbind(FAOshp,  sf::st_coordinates(sf::st_centroid(FAOshp$geometry))) %>% rename(lon = X, lat = Y)

if(params$region=='BA'){ # fixed wrong calculation of centroid of 27.3.d.30
  FAOshp = FAOshp %>%   
    mutate(lon = ifelse(F_CODE=='27.3.d.30', 19.5 ,lon), lat =  ifelse(F_CODE=='27.3.d.30',62 ,lat))

}

```

```{r loadPrepareData, echo=FALSE}
# LOAD AND PREPARE DATA
source('scripts/loadData.R', local = knitr::knit_global())
  
```

```{r fleetRegisterData, echo=FALSE}
# LOAD AND PREPARE FLEET REGISTER DATA

```

**Disclaimer**
The tables and figures of the overviews presented in this document are made for the coordination of EU regional fisheries data collection purposes and are not designed for any other use. Data used for producing the outputs are extracted from the Regional Database and Estimating System (RDBES) and EU Fleet Register. Dates of data extractions are stated in Appendix A. Due to different aggregations and reporting authorities, data can differ from those used e.g. for assessments or technical reports. 

Member States (MS) are responsible for uploading latest data and the latest year should be viewed as provisional. Data can be resubmitted by a MS for more than one previous year so there might be differences in earlier year reports, if countries update back in time. Responsibility for the quality of the data and comparability to other data sources lies with the MS that provided these data. The upload logs presented by MS regarding the data submitted to RDB can be found in the Share Point for Intersessional Work, under the folder "Data".

The respective scripts and calculations used for data displaying are publicly available via the RCG GitHub (https://github.com/ices-eg/RCGs) and subject to change as the work of the group progresses.

# Introduction
put some text here

## Reading the graphs
### Barplots
put some text here

### Maps
put some text here

# Overall fleet evolution (All RCGs){.tabset}
The tables included in this section present a summary of the information on licensed vessels from the European Union Fleet Register.

## Number of vessels
**Table 1.** Number of EU licensed vessels by flag country and vessel length class present in the EU fleet register (license indicator == “Y” in 1st January `r params$year`. Parentheses: variation relative to `r params$year-1`; red = number decreases; green = number increases; white = number maintains).
```{r echo=FALSE, message=FALSE, warning = FALSE, out.width="90%", out.height="90%"}

res_fleetreg<-table(Fleet$vesLenCat, Fleet$Country_Code,Fleet$Status)
pyear<-as.data.frame.matrix(rbind(res_fleetreg[,,1],apply(res_fleetreg[,,1],2,sum)))
year<-as.data.frame.matrix(rbind(res_fleetreg[,,2],apply(res_fleetreg[,,2],2,sum)))
year_pyear<-as.data.frame.matrix(rbind((res_fleetreg[,,2]-res_fleetreg[,,1]),apply((res_fleetreg[,,2]-res_fleetreg[,,1]),2,sum)))
ft<-func_table2(year,year_pyear)
autofit(ft)
```

## Power 
**Table 2.** Power (1000*kW) of EU licensed vessels by flag country and vessel length class present in the EU fleet register (license indicator == “Y” in 1st January `r params$year`. Parentheses: variation relative to `r params$year-1`).
```{r echo=FALSE, message=FALSE, warning = FALSE, out.width="90%", out.height="90%"}
res_fleetreg_pwr<-tapply(Fleet$Power_Main, list(Fleet$vesLenCat,Fleet$Country_Code, Fleet$Status), sum)
res_fleetreg_pwr[is.na(res_fleetreg_pwr)]<-0
  pyear<-as.data.frame.matrix(round(rbind(res_fleetreg_pwr[,,1],apply(res_fleetreg_pwr[,,1],2,sum))/1000,1))
  year<-as.data.frame.matrix(round(rbind(res_fleetreg_pwr[,,2],apply(res_fleetreg_pwr[,,2],2,sum))/1000,1))
  year_pyear<-as.data.frame.matrix(round(rbind((res_fleetreg_pwr[,,2]-res_fleetreg_pwr[,,1]),apply((res_fleetreg_pwr[,,2]-res_fleetreg_pwr[,,1]),2,sum))/1000,1))
ft<-func_table2(year,year_pyear)
autofit(ft)
```


## Gross tonnage
**Table 3.** Gross Tonnage(1000*GT) of EU licensed vessels by flag country and vessel length class present in the EU fleet register (license indicator == “Y” in 1st January `r params$year`. Parentheses: variation relative to `r params$year-1`).
```{r echo=FALSE, message=FALSE, warning = FALSE, out.width="90%", out.height="90%"}
res_fleetreg_gt<-tapply(Fleet$Ton_Gt, list(Fleet$vesLenCat,Fleet$Country_Code, Fleet$Status), sum)  
res_fleetreg_gt[is.na(res_fleetreg_gt)]<-0
pyear<-as.data.frame.matrix(round(rbind(res_fleetreg_gt[,,1],apply(res_fleetreg_gt[,,1],2,sum))/1000,1))
  year<-as.data.frame.matrix(round(rbind(res_fleetreg_gt[,,2],apply(res_fleetreg_gt[,,2],2,sum))/1000,1))
  year_pyear<-as.data.frame.matrix(round(rbind((res_fleetreg_gt[,,2]-res_fleetreg_gt[,,1]),apply((res_fleetreg_gt[,,2]-res_fleetreg_gt[,,1]),2,sum))/1000,1))
ft<-func_table2(year,year_pyear)
autofit(ft)
```

# Landings (CL)

## Overall landings

### Landings by species {.tabset}
#### species
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6}

sub_cl<- cl%>%
  group_by(CLyear,SpeciesLaName) %>%
  summarise(CLscientificWeight_1000ton = sum(CLscientificWeight_1000ton)) %>%
  top_n(20, wt=CLscientificWeight_1000ton)
barplot(data = sub_cl, 
      x = "SpeciesLaName",
      y = "CLscientificWeight_1000ton",
      title = "Landings (1000 t) by Species",
      ylab = "Sum of Landings (1000 t)")


```

#### species and country
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6}

sub_cl_2<- cl%>%
  group_by(CLyear, SpeciesLaName, CLlandingCountry) %>%
  summarise(CLscientificWeight_1000ton_total = sum(CLscientificWeight_1000ton))

sub_cl_top <- sub_cl %>%
  arrange(desc(CLscientificWeight_1000ton)) %>%
  top_n(20)

sub_cl_top$Top <- "TOP"
sub_cl_2_top <- left_join(sub_cl_2,sub_cl_top,by="SpeciesLaName")

sub_cl_2_top <- sub_cl_2_top %>%
  filter(Top=='TOP')

barplot(data = sub_cl_2_top,
      x = "SpeciesLaName",
      y = "CLscientificWeight_1000ton",
      group = "CLlandingCountry",
      title = "Landings (1000 t) by Species and Country",
      ylab = "Proportion of Landings (1000 t)",
      asPct = T)
```

### Landings by catch_group {.tabset}
#### catch group
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6}

barplot(data = cl, 
      x = "CatchGroup",
      y = "CLscientificWeight_1000ton",
      title = "Landings (1000 t) by Catch Group",
      ylab = "Proportion of Landings (1000 t)")
```

#### catch_group and country
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6}

barplot(data = cl, 
      x = "CatchGroup",
      y = "CLscientificWeight_1000ton",
      group = "CLlandingCountry",
      title = "Landings (1000 t) by Catch Group and Country",
      ylab = "Proportion of Landings (1000 t)",
      asPct = T)

```


### Landings by fleet
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6}
barplot(data = cl, 
      x = "CLvesselLengthCategory",
      y = "CLscientificWeight_1000ton",
      group = "CLlandingCountry",
      title = "Landings (1000 t) by Vessel Length Category and Country",
      ylab = "Proportion of Landings (1000 t)",
      asPct = T)

```

### Landings by area {.tabset}
#### area
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6}
barplot(data = cl, 
      x = "CLarea",
      y = "CLscientificWeight_1000ton",
      title = "Landings (1000 t) by Area",
      ylab = "Sum of Landings (1000 t)")

```

#### area and country
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6}
barplot(data = cl, 
      x = "CLarea",
      y = "CLscientificWeight_1000ton",
      group = "CLlandingCountry",
      title = "Landings (1000 t) by Area and Country",
      ylab = "Proportion of Landings (1000 t)",
      asPct = T)

```

#### country and area
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6}
barplot(data = cl, 
      x = "CLlandingCountry",
      y = "CLscientificWeight_1000ton",
      group = "CLarea",
      title = "Landings (1000 t) by Country and Area",
      ylab = "Proportion of Landings (1000 t)",
      asPct = T)

```

### Landings by metier {.tabset}
#### metier lvl5
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=7,fig.height=7}
#data prep
sub_cl_top <- cl%>%
  mutate(CLmetier5 = substr(CLmetier6, 1, 7))%>%
  group_by(CLyear, CLmetier5) %>%
  summarise(CLscientificWeight_1000ton = sum(CLscientificWeight_1000ton)) %>%
  top_n(20)


barplot(data = sub_cl_top,
      x = "CLmetier5",
      y = "CLscientificWeight_1000ton",
      title = "Landings (1000 t) by Metier Lvl5",
      ylab = "Proportion of Landings (1000 t)")
```

#### metier lvl5 and country
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=7,fig.height=7}
#data prep
sub_cl_2<- cl%>%
  mutate(CLmetier5 = substr(CLmetier6, 1, 7))%>%
  group_by(CLyear, CLmetier5, CLlandingCountry) %>%
  summarise(CLscientificWeight_1000ton_total = sum(CLscientificWeight_1000ton))

sub_cl_top$Top <- "TOP"
sub_cl_2_top <- left_join(sub_cl_2,sub_cl_top,by="CLmetier5")

sub_cl_2_top <- sub_cl_2_top %>%
  filter(Top=='TOP')

barplot(data = sub_cl_2_top, 
      x = "CLmetier5",
      y = "CLscientificWeight_1000ton",
      group = "CLlandingCountry",
      title = "Landings (1000 t) by Metier Lvl5 and Country",
      ylab = "Proportion of Landings (1000 t)",
      asPct = T)

```

#### metier lvl6
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6}
sub_cl_top<- cl%>%
  group_by(CLyear, CLmetier6) %>%
  summarise(CLscientificWeight_1000ton = sum(CLscientificWeight_1000ton)) %>%
  top_n(20, wt=CLscientificWeight_1000ton)

barplot(data = sub_cl_top, 
      x = "CLmetier6",
      y = "CLscientificWeight_1000ton",
      title = "Landings (1000 t) by Metier Lvl6",
      ylab = "Sum of Landings (1000 t)")
```

#### metier lvl6 and country
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6}
sub_cl_2<- cl%>%
  group_by(CLyear, CLmetier6, CLlandingCountry) %>%
  summarise(CLscientificWeight_1000ton_total = sum(CLscientificWeight_1000ton))

sub_cl_top$Top <- "TOP"
sub_cl_2_top <- left_join(sub_cl_2,sub_cl_top,by="CLmetier6")

sub_cl_2_top <- sub_cl_2_top %>%
  filter(Top=='TOP')

barplot(data = sub_cl_2_top, 
        x = "CLmetier6",
        y = "CLscientificWeight_1000ton_total",
        title = "Landings (1000 t) by Metier Lvl6 and Country",
        group = "CLlandingCountry",
        ylab = "Proportion of Landings (1000 t)",
        asPct = T)
```

### Landings by harbour {.tabset}
#### harbour
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6}
sub_cl_top<- cl%>%
  group_by(CLyear, CLlandingLocation) %>%
  summarise(CLscientificWeight_1000ton = sum(CLscientificWeight_1000ton)) %>%
  top_n(20, wt=CLscientificWeight_1000ton)

barplot(data = sub_cl_top, 
      x = "CLlandingLocation",
      y = "CLscientificWeight_1000ton",
      title = "Landings (1000 t) by Harbours",
      ylab = "Sum of Landings (1000 t)")
```

#### harbour and flag country
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6}
sub_cl_2 <- cl%>%
  group_by(CLyear, CLlandingLocation, CLvesselFlagCountry) %>%
  summarise(CLscientificWeight_1000ton_total = sum(CLscientificWeight_1000ton))

sub_cl_top$Top <- "TOP"
sub_cl_2_top <- left_join(sub_cl_2,sub_cl_top,by = "CLlandingLocation")

sub_cl_2_top <- sub_cl_2_top %>%
  filter(Top=='TOP')

barplot(data = sub_cl_2_top, 
        x = "CLlandingLocation",
        y = "CLscientificWeight_1000ton_total",
        title = "Landings (1000 t) by Harbour and Flag Country",
        group = "CLvesselFlagCountry",
        ylab = "Proportion of Landings (1000 t)",
        asPct = T)
```

#### map - harbour
#### map - harbour and flag country

### Landings abroad
```{r riverplot aborad, echo = FALSE, warning = FALSE, message = FALSE,results = "asis", dpi=100, fig.width=9,fig.height=9}
paste("River plot of CLscientificWeight_ton between CLvesselFlagCountry (left) and CLlandingCountry (right). Width of line is proportional to landings", sep="")  
    
cl %>%
  group_by(CLyear, CLlandingCountry, CLvesselFlagCountry) %>%
  summarise(CLscientificWeight_ton = sum(CLscientificWeight_ton))-> cl_river

result<-func_riverplot(df = cl_river,
            left = 'CLvesselFlagCountry',
            right = 'CLlandingCountry',
            value = 'CLscientificWeight_ton')
result
```

### Spatial distribution of landings

```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6}
# do we need information on for how many rows(%) there was a missing CLscientificWeight_ton? <-------------------------- to do

# data prep
cl %>%
  group_by(CLyear, CLstatisticalRectangle) %>%
  summarise(CLscientificWeight_ton = sum(CLscientificWeight_ton)) %>%
  mutate(pr= CLscientificWeight_ton/sum(CLscientificWeight_ton, na.rm = TRUE)*100,
         analysis_type = 'sum',
         type_of_threshold = 'none',
         value_of_threshold = NA)-> df

# map
result = choroplethMap_func2(
  df,
  var_name = 'CLscientificWeight_ton',
  var_spatial_name = 'CLstatisticalRectangle',
  facet_name = 'CLyear',
  spatial_dataset_name = 'StatRectshp',
  spatial_dataset_var_name = 'ICESNAME',
  spatial_dataset_labels = FALSE,
  saveResults = FALSE,
  outputPath,
  displayInR = TRUE,
  extraShp_name = 'FAOshp',
  var_name_new = NA,
  addToTitle = NA,
  RCGregion = 'BA'
)

result[[1]]
```


## Small pelagics landings
### Landings by country, small pelagics
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6}

barplot(data = cl %>%
  filter(CatchGroup=='small pelagic'), 
      x = "CLlandingCountry",
      y = "CLscientificWeight_1000ton",
      title = "Landings (1000 t) by Country",
      ylab = "Sum of Landings (1000 t)",
      col_cou = T )
```

### Landings by species, small pelagics {.tabset}
#### species
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6}

barplot(data = cl%>%
  filter(CatchGroup=='small pelagic'), 
      x = "SpeciesLaName",
      y = "CLscientificWeight_1000ton",
      title = "Landings (1000 t) by Species",
      ylab = "Sum of Landings (1000 t)")
```

#### species and country
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6}
barplot(data = cl%>%filter(CatchGroup=='small pelagic'), 
      x = "SpeciesLaName",
      y = "CLscientificWeight_1000ton",
      group = "CLlandingCountry",
      title = "Landings (1000 t) by Species and Country",
      ylab = "Proportion of Landings (1000 t)",
      asPct = T)
```

### Landings by fleet, small pelagics {.tabset}
#### fleet
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6}

sub_cl_top<- cl%>%
  filter(CatchGroup=='small pelagic')%>%
  group_by(CLyear, FlagCountry_Loa) %>%
  summarise(CLscientificWeight_1000ton = sum(CLscientificWeight_1000ton))%>%
  top_n(20, wt=CLscientificWeight_1000ton)

barplot(data = sub_cl_top, 
      x = "FlagCountry_Loa",
      y = "CLscientificWeight_1000ton",
      title = "Landings (1000 t) by Species",
      ylab = "Sum of Landings (1000 t)")
```

#### country and fleet
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6}

barplot(data = cl%>%filter(CatchGroup=='small pelagic'),
      x = "CLvesselLengthCategory",
      y = "CLscientificWeight_1000ton",
      group = "CLlandingCountry",
      title = "Landings (1000 t) by Vessel Length Category and Country",
      ylab = "Proportion of Landings (1000 t)",
      asPct = T)
```

#### fleet and country
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6}

barplot(data = cl%>%filter(CatchGroup=='small pelagic'),
      x = "CLlandingCountry",
      y = "CLscientificWeight_1000ton",
      group = "CLvesselLengthCategory",
      title = "Landings (1000 t) by Country and Vessel Length Category",
      ylab = "Proportion of Landings (1000 t)",
      asPct = T)
```

### Landings by area, small pelagics {.tabset}
#### area
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6}
barplot(data = cl%>%filter(CatchGroup == 'small pelagic'), 
      x = "CLarea",
      y = "CLscientificWeight_1000ton",
      title = "Landings (1000 t) by Area",
      ylab = "Sum of Landings (1000 t)")

```

#### area and country
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6}
barplot(data = cl%>%filter(CatchGroup == 'small pelagic'), 
      x = "CLarea",
      y = "CLscientificWeight_1000ton",
      group = "CLlandingCountry",
      title = "Landings (1000 t) by Area and Country",
      ylab = "Proportion of Landings (1000 t)",
      asPct = T)

```

#### country and area
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6}
barplot(data = cl%>%filter(CatchGroup == 'small pelagic'),
      x = "CLlandingCountry",
      y = "CLscientificWeight_1000ton",
      group = "CLarea",
      title = "Landings (1000 t) by Country and Area",
      ylab = "Proportion of Landings (1000 t)",
      asPct = T)

```

#### map area
#### map area and flag country

### Landings by metier, small pelagics {.tabset}
#### metier lvl5
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=7,fig.height=7}
#data prep
sub_cl_top <- cl%>%
  filter(CatchGroup == 'small pelagic')%>%
  mutate(CLmetier5 = substr(CLmetier6, 1, 7))%>%
  group_by(CLyear, CLmetier5) %>%
  summarise(CLscientificWeight_1000ton = sum(CLscientificWeight_1000ton)) %>%
  top_n(20)

barplot(data = sub_cl_top,
      x = "CLmetier5",
      y = "CLscientificWeight_1000ton",
      title = "Landings (1000 t) by Metier Lvl5",
      ylab = "Proportion of Landings (1000 t)")
```

#### metier lvl5 and country
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=7,fig.height=7}
#data prep
sub_cl_2 <- cl%>%
  filter(CatchGroup == 'small pelagic') %>%
    mutate(CLmetier5 = substr(CLmetier6, 1, 7))%>%
  group_by(CLyear, CLmetier5, CLlandingCountry) %>%
  summarise(CLscientificWeight_1000ton_total = sum(CLscientificWeight_1000ton))

sub_cl_top$Top <- "TOP"
sub_cl_2_top <- left_join(sub_cl_2,sub_cl_top,by="CLmetier5")

sub_cl_2_top <- sub_cl_2_top %>%
  filter(Top=='TOP')

barplot(data = sub_cl_2_top, 
      x = "CLmetier5",
      y = "CLscientificWeight_1000ton",
      group = "CLlandingCountry",
      title = "Landings (1000 t) by Metier Lvl5 and Country",
      ylab = "Proportion of Landings (1000 t)",
      asPct = T)

```

#### metier lvl6
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6}
sub_cl_top <- cl%>%
  filter(CatchGroup == 'small pelagic')%>%
  group_by(CLyear, CLmetier6) %>%
  summarise(CLscientificWeight_1000ton = sum(CLscientificWeight_1000ton)) %>%
  top_n(20, wt=CLscientificWeight_1000ton)

barplot(data = sub_cl_top, 
      x = "CLmetier6",
      y = "CLscientificWeight_1000ton",
      title = "Landings (1000 t) by Metier Lvl6",
      ylab = "Sum of Landings (1000 t)")
```

#### metier lvl6 and country
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6}
sub_cl_2<- cl%>%
  filter(CatchGroup == 'small pelagic') %>%
  group_by(CLyear, CLmetier6, CLlandingCountry) %>%
  summarise(CLscientificWeight_1000ton_total = sum(CLscientificWeight_1000ton))

sub_cl_top$Top <- "TOP"
sub_cl_2_top <- left_join(sub_cl_2,sub_cl_top, by = "CLmetier6")

sub_cl_2_top <- sub_cl_2_top %>%
  filter(Top=='TOP')

barplot(data = sub_cl_2_top, 
        x = "CLmetier6",
        y = "CLscientificWeight_1000ton_total",
        title = "Landings (1000 t) by Metier Lvl6 and Country",
        group = "CLlandingCountry",
        ylab = "Proportion of Landings (1000 t)",
        asPct = T)
```


### Landings by harbour, small pelagics {.tabset}
#### harbour
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6}
sub_cl_top  <- cl %>%
  filter(CatchGroup == 'small pelagic') %>%
  group_by(CLyear, CLlandingLocation) %>%
  summarise(CLscientificWeight_1000ton = sum(CLscientificWeight_1000ton)) %>%
  top_n(20, wt=CLscientificWeight_1000ton)

barplot(data = sub_cl_top, 
      x = "CLlandingLocation",
      y = "CLscientificWeight_1000ton",
      title = "Landings (1000 t) by Harbours",
      ylab = "Sum of Landings (1000 t)")
```

#### harbour and flag country
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6}
sub_cl_2<- cl%>%
  filter(CatchGroup == 'small pelagic')%>%
  group_by(CLyear, CLlandingLocation, CLvesselFlagCountry) %>%
  summarise(CLscientificWeight_1000ton_total = sum(CLscientificWeight_1000ton))

sub_cl_top$Top <- "TOP"

sub_cl_2_top <- left_join(sub_cl_2,sub_cl_top,by = "CLlandingLocation")

sub_cl_2_top <- sub_cl_2_top %>%
  filter(Top=='TOP')

barplot(data = sub_cl_2_top, 
        x = "CLlandingLocation",
        y = "CLscientificWeight_1000ton_total",
        title = "Landings (1000 t) by Harbour and Flag Country",
        group = "CLvesselFlagCountry",
        ylab = "Proportion of Landings (1000 t)",
        asPct = T)
```

#### map - harbour
#### map - harbour and flag country

### Landings abroad, small pelagics
```{r riverplot aborad sp, echo = FALSE, warning = FALSE, message = FALSE,results = "asis", dpi=100, fig.width=9,fig.height=9}
paste("River plot of CLscientificWeight_ton of small pelagic between CLvesselFlagCountry (left) and CLlandingCountry (right). Width of line is proportional to landings", sep="")  
    
cl %>%
  filter(CatchGroup == 'small pelagic')%>%
  group_by(CLyear, CLlandingCountry, CLvesselFlagCountry) %>%
  summarise(CLscientificWeight_ton = sum(CLscientificWeight_ton))-> cl_river

result<-func_riverplot(df = cl_river,
            left = 'CLvesselFlagCountry',
            right = 'CLlandingCountry',
            value = 'CLscientificWeight_ton')
result
```

### Spatial distribution of landings, small pelagics
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6}
# do we need information on for how many rows(%) there was a missing CLscientificWeight_ton? <-------------------------- to do

# data prep
cl %>%
  filter(CatchGroup == 'small pelagic') %>%
  group_by(CLyear, CLstatisticalRectangle) %>%
  summarise(CLscientificWeight_ton = sum(CLscientificWeight_ton)) %>%
  mutate(pr= CLscientificWeight_ton/sum(CLscientificWeight_ton, na.rm = TRUE)*100,
         analysis_type = 'sum',
         type_of_threshold = 'none',
         value_of_threshold = NA)-> df

# map
result = choroplethMap_func2(
  df,
  var_name = 'CLscientificWeight_ton',
  var_spatial_name = 'CLstatisticalRectangle',
  facet_name = 'CLyear',
  spatial_dataset_name = 'StatRectshp',
  spatial_dataset_var_name = 'ICESNAME',
  spatial_dataset_labels = FALSE,
  saveResults = FALSE,
  outputPath,
  displayInR = TRUE,
  extraShp_name = 'FAOshp',
  var_name_new = NA,
  addToTitle = NA,
  RCGregion = 'BA'#<-why not regionselected
)

result[[1]]
```

## Demersal landings (without flatfish)
### Landings by country, demersal (without flatfish)
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6}

barplot(data = cl %>%
  filter(CatchGroup=='demersal'), 
      x = "CLlandingCountry",
      y = "CLscientificWeight_1000ton",
      title = "Landings (1000 t) by Country",
      ylab = "Sum of Landings (1000 t)",
      col_cou = T )
```

### Landings by species, demersal (without flatfish) {.tabset}
#### species
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6}
sub_cl_top<- cl%>%
  filter(CatchGroup=='demersal')%>%
  group_by(CLyear, SpeciesLaName) %>%
  summarise(CLscientificWeight_1000ton = sum(CLscientificWeight_1000ton))%>%
  top_n(20, wt=CLscientificWeight_1000ton)

barplot(data = sub_cl_top, 
      x = "SpeciesLaName",
      y = "CLscientificWeight_1000ton",
      title = "Landings (1000 t) by Species",
      ylab = "Sum of Landings (1000 t)")
```

#### species and country
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6}
#data prep
sub_cl_2 <- cl%>%
  filter(CatchGroup == 'demersal') %>%
  group_by(CLyear, SpeciesLaName, CLlandingCountry) %>%
  summarise(CLscientificWeight_1000ton_total = sum(CLscientificWeight_1000ton))

sub_cl_top$Top <- "TOP"
sub_cl_2_top <- left_join(sub_cl_2,sub_cl_top,by="SpeciesLaName")

sub_cl_2_top <- sub_cl_2_top %>%
  filter(Top=='TOP')

barplot(data = sub_cl_2_top, 
      x = "SpeciesLaName",
      y = "CLscientificWeight_1000ton",
      group = "CLlandingCountry",
      title = "Landings (1000 t) by Species and Country",
      ylab = "Proportion of Landings (1000 t)",
      asPct = T)
```

### Landings by fleet, demersal (without flatfish) {.tabset}
#### fleet
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6}

sub_cl_top<- cl%>%
  filter(CatchGroup=='demersal')%>%
  group_by(CLyear, FlagCountry_Loa) %>%
  summarise(CLscientificWeight_1000ton = sum(CLscientificWeight_1000ton))%>%
  top_n(20, wt=CLscientificWeight_1000ton)

barplot(data = sub_cl_top, 
      x = "FlagCountry_Loa",
      y = "CLscientificWeight_1000ton",
      title = "Landings (1000 t) by Species",
      ylab = "Sum of Landings (1000 t)")
```

#### country and fleet
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6}

barplot(data = cl[CatchGroup=='demersal',],
      x = "CLvesselLengthCategory",
      y = "CLscientificWeight_1000ton",
      group = "CLlandingCountry",
      title = "Landings (1000 t) by Vessel Length Category and Country",
      ylab = "Proportion of Landings (1000 t)",
      asPct = T)
```

#### fleet and country
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6}

barplot(data = cl[CatchGroup=='demersal',],
      x = "CLlandingCountry",
      y = "CLscientificWeight_1000ton",
      group = "CLvesselLengthCategory",
      title = "Landings (1000 t) by Country and Vessel Length Category",
      ylab = "Proportion of Landings (1000 t)",
      asPct = T)
```

### Landings by area, demersal (without flatfish) {.tabset}
#### area
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6}
barplot(data = cl[CatchGroup=='demersal',], 
      x = "CLarea",
      y = "CLscientificWeight_1000ton",
      title = "Landings (1000 t) by Area",
      ylab = "Sum of Landings (1000 t)")

```

#### area and country
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6}
barplot(data = cl[CatchGroup=='demersal',],
      x = "CLarea",
      y = "CLscientificWeight_1000ton",
      group = "CLlandingCountry",
      title = "Landings (1000 t) by Area and Country",
      ylab = "Proportion of Landings (1000 t)",
      asPct = T)

```

#### country and area
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6}
barplot(data = cl[CatchGroup=='demersal',],
      x = "CLlandingCountry",
      y = "CLscientificWeight_1000ton",
      group = "CLarea",
      title = "Landings (1000 t) by Country and Area",
      ylab = "Proportion of Landings (1000 t)",
      asPct = T)

```

#### map area
#### map area and flag country

### Landings by metier, demersal (without flatfish) {.tabset}
#### metier lvl5
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=7,fig.height=7}
#data prep
sub_cl_top <- cl%>%
  filter(CatchGroup == 'demersal')%>%
  mutate(CLmetier5 = substr(CLmetier6, 1, 7))%>%
  group_by(CLyear, CLmetier5) %>%
  summarise(CLscientificWeight_1000ton = sum(CLscientificWeight_1000ton)) %>%
  top_n(20)

barplot(data = sub_cl_top,
      x = "CLmetier5",
      y = "CLscientificWeight_1000ton",
      title = "Landings (1000 t) by Metier Lvl5",
      ylab = "Sum of Landings (1000 t)")
```

#### metier lvl5 and country
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=7,fig.height=7}
#data prep
sub_cl_2 <- cl%>%
  filter(CatchGroup == 'demersal') %>%
    mutate(CLmetier5 = substr(CLmetier6, 1, 7))%>%
  group_by(CLyear, CLmetier5, CLlandingCountry) %>%
  summarise(CLscientificWeight_1000ton_total = sum(CLscientificWeight_1000ton))

sub_cl_top$Top <- "TOP"
sub_cl_2_top <- left_join(sub_cl_2,sub_cl_top,by="CLmetier5")

sub_cl_2_top <- sub_cl_2_top %>%
  filter(Top=='TOP')

barplot(data = sub_cl_2_top, 
      x = "CLmetier5",
      y = "CLscientificWeight_1000ton",
      group = "CLlandingCountry",
      title = "Landings (1000 t) by Metier Lvl5 and Country",
      ylab = "Proportion of Landings (1000 t)",
      asPct = T)

```

#### metier lvl6
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6}
sub_cl_top <- cl%>%
  filter(CatchGroup == 'demersal')%>%
  group_by(CLyear, CLmetier6) %>%
  summarise(CLscientificWeight_1000ton = sum(CLscientificWeight_1000ton)) %>%
  top_n(20, wt=CLscientificWeight_1000ton)

barplot(data = sub_cl_top, 
      x = "CLmetier6",
      y = "CLscientificWeight_1000ton",
      title = "Landings (1000 t) by Metier Lvl6",
      ylab = "Sum of Landings (1000 t)")
```

#### metier lvl6 and country
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6}
sub_cl_2<- cl%>%
  filter(CatchGroup == 'demersal') %>%
  group_by(CLyear, CLmetier6, CLlandingCountry) %>%
  summarise(CLscientificWeight_1000ton_total = sum(CLscientificWeight_1000ton))

sub_cl_top$Top <- "TOP"
sub_cl_2_top <- left_join(sub_cl_2,sub_cl_top, by = "CLmetier6")

sub_cl_2_top <- sub_cl_2_top %>%
  filter(Top=='TOP')

barplot(data = sub_cl_2_top, 
        x = "CLmetier6",
        y = "CLscientificWeight_1000ton_total",
        title = "Landings (1000 t) by Metier Lvl6 and Country",
        group = "CLlandingCountry",
        ylab = "Proportion of Landings (1000 t)",
        asPct = T)
```

### Landings by harbour, demersal (without flatfish) {.tabset}
#### harbour
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6}
sub_cl_top  <- cl %>%
  filter(CatchGroup == 'demersal') %>%
  group_by(CLyear, CLlandingLocation) %>%
  summarise(CLscientificWeight_1000ton = sum(CLscientificWeight_1000ton)) %>%
  top_n(20, wt=CLscientificWeight_1000ton)

barplot(data = sub_cl_top, 
      x = "CLlandingLocation",
      y = "CLscientificWeight_1000ton",
      title = "Landings (1000 t) by Harbours",
      ylab = "Sum of Landings (1000 t)")
```

#### harbour and flag country
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6}
sub_cl_2<- cl%>%
  filter(CatchGroup == 'demersal')%>%
  group_by(CLyear, CLlandingLocation, CLvesselFlagCountry) %>%
  summarise(CLscientificWeight_1000ton_total = sum(CLscientificWeight_1000ton))

sub_cl_top$Top <- "TOP"

sub_cl_2_top <- left_join(sub_cl_2,sub_cl_top,by = "CLlandingLocation")

sub_cl_2_top <- sub_cl_2_top %>%
  filter(Top=='TOP')

barplot(data = sub_cl_2_top, 
        x = "CLlandingLocation",
        y = "CLscientificWeight_1000ton_total",
        title = "Landings (1000 t) by Harbour and Flag Country",
        group = "CLvesselFlagCountry",
        ylab = "Proportion of Landings (1000 t)",
        asPct = T)
```

#### map - harbour
#### map - harbour and flag country

### Landings abroad, demersal (without flatfish)
```{r riverplot aborad demersal, echo = FALSE, warning = FALSE, message = FALSE,results = "asis", dpi=100, fig.width=9,fig.height=9}
paste("River plot of CLscientificWeight_ton of demersal between CLvesselFlagCountry (left) and CLlandingCountry (right). Width of line is proportional to landings", sep="")  
    
cl %>%
  filter(CatchGroup == 'demersal')%>%
  group_by(CLyear, CLlandingCountry, CLvesselFlagCountry) %>%
  summarise(CLscientificWeight_ton = sum(CLscientificWeight_ton))-> cl_river

result<-func_riverplot(df = cl_river,
            left = 'CLvesselFlagCountry',
            right = 'CLlandingCountry',
            value = 'CLscientificWeight_ton')
result
```

### Spatial distribution of landings, demersal (without flatfish)
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6}
# do we need information on for how many rows(%) there was a missing CLscientificWeight_ton? <-------------------------- to do

# data prep
cl %>%
  filter(CatchGroup == 'demersal') %>%
  group_by(CLyear, CLstatisticalRectangle) %>%
  summarise(CLscientificWeight_ton = sum(CLscientificWeight_ton)) %>%
  mutate(pr= CLscientificWeight_ton/sum(CLscientificWeight_ton, na.rm = TRUE)*100,
         analysis_type = 'sum',
         type_of_threshold = 'none',
         value_of_threshold = NA)-> df

# map
result = choroplethMap_func2(
  df,
  var_name = 'CLscientificWeight_ton',
  var_spatial_name = 'CLstatisticalRectangle',
  facet_name = 'CLyear',
  spatial_dataset_name = 'StatRectshp',
  spatial_dataset_var_name = 'ICESNAME',
  spatial_dataset_labels = FALSE,
  saveResults = FALSE,
  outputPath,
  displayInR = TRUE,
  extraShp_name = 'FAOshp',
  var_name_new = NA,
  addToTitle = NA,
  RCGregion = 'BA'#<-why not regionselected
)

result[[1]]
```

## Flatfish landings
### Landings by country, flatfish
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6}

barplot(data = cl[CatchGroup=='flatfish',], 
      x = "CLlandingCountry",
      y = "CLscientificWeight_1000ton",
      title = "Landings (1000 t) by Country",
      ylab = "Sum of Landings (1000 t)",
      col_cou = T )
```

### Landings by species, flatfish {.tabset}
#### species
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6}

barplot(data = cl[CatchGroup=='flatfish',], 
      x = "SpeciesLaName",
      y = "CLscientificWeight_1000ton",
      title = "Landings (1000 t) by Species",
      ylab = "Sum of Landings (1000 t)")
```

#### species and country
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6}
barplot(data = cl[CatchGroup=='flatfish',], 
      x = "SpeciesLaName",
      y = "CLscientificWeight_1000ton",
      group = "CLlandingCountry",
      title = "Landings (1000 t) by Species and Country",
      ylab = "Proportion of Landings (1000 t)",
      asPct = T)
```

### Landings by fleet, flatfish {.tabset}
#### fleet
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6}

sub_cl_top<- cl%>%
  filter(CatchGroup=='flatfish')%>%
  group_by(CLyear, FlagCountry_Loa) %>%
  summarise(CLscientificWeight_1000ton = sum(CLscientificWeight_1000ton))%>%
  top_n(20, wt=CLscientificWeight_1000ton)

barplot(data = sub_cl_top, 
      x = "FlagCountry_Loa",
      y = "CLscientificWeight_1000ton",
      title = "Landings (1000 t) by Species",
      ylab = "Sum of Landings (1000 t)")
```

#### country and fleet
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6}

barplot(data = cl[CatchGroup=='flatfish',],
      x = "CLvesselLengthCategory",
      y = "CLscientificWeight_1000ton",
      group = "CLlandingCountry",
      title = "Landings (1000 t) by Vessel Length Category and Country",
      ylab = "Proportion of Landings (1000 t)",
      asPct = T)
```

#### fleet and country
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6}

barplot(data = cl[CatchGroup=='flatfish',],
      x = "CLlandingCountry",
      y = "CLscientificWeight_1000ton",
      group = "CLvesselLengthCategory",
      title = "Landings (1000 t) by Country and Vessel Length Category",
      ylab = "Proportion of Landings (1000 t)",
      asPct = T)
```

### Landings by area, flatfish {.tabset}
#### area
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6}
barplot(data = cl[CatchGroup=='flatfish',], 
      x = "CLarea",
      y = "CLscientificWeight_1000ton",
      title = "Landings (1000 t) by Area",
      ylab = "Sum of Landings (1000 t)")

```

#### area and country
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6}
barplot(data = cl[CatchGroup=='flatfish',],
      x = "CLarea",
      y = "CLscientificWeight_1000ton",
      group = "CLlandingCountry",
      title = "Landings (1000 t) by Area and Country",
      ylab = "Proportion of Landings (1000 t)",
      asPct = T)

```

#### country and area
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6}
barplot(data = cl[CatchGroup=='flatfish',],
      x = "CLlandingCountry",
      y = "CLscientificWeight_1000ton",
      group = "CLarea",
      title = "Landings (1000 t) by Country and Area",
      ylab = "Proportion of Landings (1000 t)",
      asPct = T)

```

#### map area
#### map area and flag country

### Landings by metier, flatfish {.tabset}
#### metier lvl5
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=7,fig.height=7}
#data prep
sub_cl_top <- cl%>%
  filter(CatchGroup == 'flatfish')%>%
  mutate(CLmetier5 = substr(CLmetier6, 1, 7))%>%
  group_by(CLyear, CLmetier5) %>%
  summarise(CLscientificWeight_1000ton = sum(CLscientificWeight_1000ton)) %>%
  top_n(20)

barplot(data = sub_cl_top,
      x = "CLmetier5",
      y = "CLscientificWeight_1000ton",
      title = "Landings (1000 t) by Metier Lvl5",
      ylab = "Sum of Landings (1000 t)")
```

#### metier lvl5 and country
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=7,fig.height=7}
#data prep
sub_cl_2 <- cl%>%
  filter(CatchGroup == 'flatfish') %>%
    mutate(CLmetier5 = substr(CLmetier6, 1, 7))%>%
  group_by(CLyear, CLmetier5, CLlandingCountry) %>%
  summarise(CLscientificWeight_1000ton_total = sum(CLscientificWeight_1000ton))

sub_cl_top$Top <- "TOP"
sub_cl_2_top <- left_join(sub_cl_2,sub_cl_top,by="CLmetier5")

sub_cl_2_top <- sub_cl_2_top %>%
  filter(Top=='TOP')

barplot(data = sub_cl_2_top, 
      x = "CLmetier5",
      y = "CLscientificWeight_1000ton",
      group = "CLlandingCountry",
      title = "Landings (1000 t) by Metier Lvl5 and Country",
      ylab = "Proportion of Landings (1000 t)",
      asPct = T)

```

#### metier lvl6
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6}
sub_cl_top <- cl%>%
  filter(CatchGroup == 'flatfish')%>%
  group_by(CLyear, CLmetier6) %>%
  summarise(CLscientificWeight_1000ton = sum(CLscientificWeight_1000ton)) %>%
  top_n(20, wt=CLscientificWeight_1000ton)

barplot(data = sub_cl_top, 
      x = "CLmetier6",
      y = "CLscientificWeight_1000ton",
      title = "Landings (1000 t) by Metier Lvl6",
      ylab = "Sum of Landings (1000 t)")
```

#### metier lvl6 and country
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6}
sub_cl_2<- cl%>%
  filter(CatchGroup == 'flatfish') %>%
  group_by(CLyear, CLmetier6, CLlandingCountry) %>%
  summarise(CLscientificWeight_1000ton_total = sum(CLscientificWeight_1000ton))

sub_cl_top$Top <- "TOP"
sub_cl_2_top <- left_join(sub_cl_2,sub_cl_top, by = "CLmetier6")

sub_cl_2_top <- sub_cl_2_top %>%
  filter(Top=='TOP')

barplot(data = sub_cl_2_top, 
        x = "CLmetier6",
        y = "CLscientificWeight_1000ton_total",
        title = "Landings (1000 t) by Metier Lvl6 and Country",
        group = "CLlandingCountry",
        ylab = "Proportion of Landings (1000 t)",
        asPct = T)
```


### Landings by harbour, flatfish {.tabset}
#### harbour
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6}
sub_cl_top  <- cl %>%
  filter(CatchGroup == 'flatfish') %>%
  group_by(CLyear, CLlandingLocation) %>%
  summarise(CLscientificWeight_1000ton = sum(CLscientificWeight_1000ton)) %>%
  top_n(20, wt=CLscientificWeight_1000ton)

barplot(data = sub_cl_top, 
      x = "CLlandingLocation",
      y = "CLscientificWeight_1000ton",
      title = "Landings (1000 t) by Harbours",
      ylab = "Sum of Landings (1000 t)")
```

#### harbour and flag country
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6}
sub_cl_2<- cl%>%
  filter(CatchGroup == 'flatfish')%>%
  group_by(CLyear, CLlandingLocation, CLvesselFlagCountry) %>%
  summarise(CLscientificWeight_1000ton_total = sum(CLscientificWeight_1000ton))

sub_cl_top$Top <- "TOP"

sub_cl_2_top <- left_join(sub_cl_2,sub_cl_top,by = "CLlandingLocation")

sub_cl_2_top <- sub_cl_2_top %>%
  filter(Top=='TOP')

barplot(data = sub_cl_2_top, 
        x = "CLlandingLocation",
        y = "CLscientificWeight_1000ton_total",
        title = "Landings (1000 t) by Harbour and Flag Country",
        group = "CLvesselFlagCountry",
        ylab = "Proportion of Landings (1000 t)",
        asPct = T)
```

#### map - harbour
#### map - harbour and flag country

### Landings abroad, flatfish
```{r riverplot aborad flatfish, echo = FALSE, warning = FALSE, message = FALSE,results = "asis", dpi=100, fig.width=9,fig.height=9}
paste("River plot of CLscientificWeight_ton of flatfish between CLvesselFlagCountry (left) and CLlandingCountry (right). Width of line is proportional to landings", sep="")  
    
cl %>%
  filter(CatchGroup == 'flatfish')%>%
  group_by(CLyear, CLlandingCountry, CLvesselFlagCountry) %>%
  summarise(CLscientificWeight_ton = sum(CLscientificWeight_ton))-> cl_river

result<-func_riverplot(df = cl_river,
            left = 'CLvesselFlagCountry',
            right = 'CLlandingCountry',
            value = 'CLscientificWeight_ton')
result
```

### Spatial distribution of landings, flatfish
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6}
# do we need information on for how many rows(%) there was a missing CLscientificWeight_ton? <-------------------------- to do

# data prep
cl %>%
  filter(CatchGroup == 'flatfish') %>%
  group_by(CLyear, CLstatisticalRectangle) %>%
  summarise(CLscientificWeight_ton = sum(CLscientificWeight_ton)) %>%
  mutate(pr= CLscientificWeight_ton/sum(CLscientificWeight_ton, na.rm = TRUE)*100,
         analysis_type = 'sum',
         type_of_threshold = 'none',
         value_of_threshold = NA)-> df

# map
result = choroplethMap_func2(
  df,
  var_name = 'CLscientificWeight_ton',
  var_spatial_name = 'CLstatisticalRectangle',
  facet_name = 'CLyear',
  spatial_dataset_name = 'StatRectshp',
  spatial_dataset_var_name = 'ICESNAME',
  spatial_dataset_labels = FALSE,
  saveResults = FALSE,
  outputPath,
  displayInR = TRUE,
  extraShp_name = 'FAOshp',
  var_name_new = NA,
  addToTitle = NA,
  RCGregion = 'BA'#<-why not regionselected
)

result[[1]]
```

# Effort (CE)

## Effort by country {.tabset}
### number of trips
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6}

barplot(data = ce, 
      x = "CEvesselFlagCountry",
      y = "CEnumberOfDominantTrips",
      title = "Number of trips by Country",
      ylab = "Sum of Number of trips")


```

### days at sea
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6}

barplot(data = ce, 
      x = "CEvesselFlagCountry",
      y = "CEscientificDaysAtSea",
      title = "Days at Sea by Country",
      ylab = "Sum of days at Sea")


```

### KW-days
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6}

barplot(data = ce, 
      x = "CEvesselFlagCountry",
      y = "CEscientifickWDaysAtSea_1000x",
      title = "KW-Days*1000 at Sea by Country",
      ylab = "Sum of KW-Days*1000 at Sea")


```

### GT-days
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6}

barplot(data = ce, 
      x = "CEvesselFlagCountry",
      y = "CEgTDaysAtSea_1000x",
      title = "GT-Days*1000 at Sea by Country",
      ylab = "Sum of GT-Days*1000 at Sea")


```
## Effort by fleet {.tabset}
### number of trips
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6}
sub_ce_top<- ce%>%
  group_by(CEyear, FlagCountry_Loa) %>%
  summarise(CEnumberOfDominantTrips = sum(CEnumberOfDominantTrips))%>%
  top_n(20, wt=CEnumberOfDominantTrips)
barplot(data = sub_ce_top, 
      x = "FlagCountry_Loa",
      y = "CEnumberOfDominantTrips",
      title = "Number of trips by Fleet",
      ylab = "Sum of number of trips")
```

### number of trips by country and fleet
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6}

barplot(data = ce,
      x = "CEvesselLengthCategory",
      y = "CEnumberOfDominantTrips",
      group = "CEvesselFlagCountry",
      title = "Number of trips by Vessel Length Category and Country",
      ylab = "Proportion of number of trips",
      asPct = T)
```

### number of trips by fleet and country
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6}

barplot(data = ce,
      x = "CEvesselFlagCountry",
      y = "CEnumberOfDominantTrips",
      group = "CEvesselLengthCategory",
      title = "Number of trips by Country an Vessel Length Category",
      ylab = "Proportion of number of trips",
      asPct = T)
```

## Effort by area
### Below 10 meters {.tabset}
#### area
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6}

barplot(data = ce%>%filter(CEvesselLengthCategory %in% c("VL0006", "VL0608", "VL0810")), 
      x = "CEarea",
      y = "CEnumberOfDominantTrips",
      title = "Number of trips by Area",
      ylab = "Sum of Number of trips")

```

#### area and country
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6}

barplot(data = ce%>%filter(CEvesselLengthCategory %in% c("VL0006", "VL0608", "VL0810")), 
      x = "CEarea",
      y = "CEnumberOfDominantTrips",
      title = "Number of trips by Area",
      ylab = "Sum of Number of trips")

```

#### area and country
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6}

barplot(data = ce%>%filter(CEvesselLengthCategory %in% c("VL0006", "VL0608", "VL0810")),
      x = "CEarea",
      y = "CEnumberOfDominantTrips",
      group = "CEvesselFlagCountry",
      title = "Number of trips by Area and Country",
      ylab = "Proportion of Number of trips",
      asPct = T)

```


### 10 meters and above {.tabset}
#### area

```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6}

barplot(data = ce%>%filter(CEvesselLengthCategory %in% c("VL1012", "VL1215", "VL1518","VL1824","VL2440","VL40XX")), 
      x = "CEarea",
      y = "CEnumberOfDominantTrips",
      title = "Number of trips by Area",
      ylab = "Sum of Number of trips")

```

#### area and country
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6}

barplot(data = ce%>%filter(CEvesselLengthCategory %in% c("VL1012", "VL1215", "VL1518","VL1824","VL2440","VL40XX")),
      x = "CEarea",
      y = "CEnumberOfDominantTrips",
      group = "CEvesselFlagCountry",
      title = "Number of trips by Area and Country",
      ylab = "Proportion of Number of trips",
      asPct = T)

```

#### country and area
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6}

barplot(data = ce%>%filter(CEvesselLengthCategory %in% c("VL1012", "VL1215", "VL1518","VL1824","VL2440","VL40XX")),
      x = "CEvesselFlagCountry",
      y = "CEnumberOfDominantTrips",
      group = "CEarea",
      title = "Number of trips by Country and Area",
      ylab = "Proportion of Number of trips",
      asPct = T)

```

## Effort by metier
### Below 10 meters  {.tabset}
#### metier lvl5
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=7,fig.height=7}
#data prep
sub_ce_top <- ce%>%
  filter(CEvesselLengthCategory %in% c("VL0006", "VL0608", "VL0810"))%>%
  mutate(CEmetier5 = substr(CEmetier6, 1, 7))%>%
  group_by(CEyear, CEmetier5) %>%
  summarise(CEnumberOfDominantTrips = sum(CEnumberOfDominantTrips)) %>%
  top_n(20)

barplot(data = sub_ce_top,
      x = "CEmetier5",
      y = "CEnumberOfDominantTrips",
      title = "Number of trips by Metier Lvl5",
      ylab = "Sum of Number of trips")
```

#### metier lvl5 and country
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=7,fig.height=7}
#data prep
sub_ce_2 <- ce%>%
  filter(CEvesselLengthCategory %in% c("VL0006", "VL0608", "VL0810"))%>%
    mutate(CEmetier5 = substr(CEmetier6, 1, 7))%>%
  group_by(CEyear, CEmetier5, CEvesselFlagCountry) %>%
  summarise(CEnumberOfDominantTrips_total = sum(CEnumberOfDominantTrips))

sub_ce_top$Top <- "TOP"
sub_ce_2_top <- left_join(sub_ce_2,sub_ce_top,by="CEmetier5")

sub_ce_2_top <- sub_ce_2_top %>%
  filter(Top=='TOP')

barplot(data = sub_ce_2_top, 
      x = "CEmetier5",
      y = "CEnumberOfDominantTrips",
      group = "CEvesselFlagCountry",
      title = "Number of trips by Metier Lvl5 and Country",
      ylab = "Proportion of Number of trips",
      asPct = T)

```

#### statistical rectangle

### 10 meteres and above  {.tabset}
#### metier lvl5
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=7,fig.height=7}
#data prep
sub_ce_top <- ce%>%
  filter(CEvesselLengthCategory %in% c("VL1012", "VL1215", "VL1518","VL1824","VL2440","VL40XX"))%>%
  mutate(CEmetier5 = substr(CEmetier6, 1, 7))%>%
  group_by(CEyear, CEmetier5) %>%
  summarise(CEnumberOfDominantTrips = sum(CEnumberOfDominantTrips)) %>%
  top_n(20)

barplot(data = sub_ce_top,
      x = "CEmetier5",
      y = "CEnumberOfDominantTrips",
      title = "Number of trips by Metier Lvl5",
      ylab = "Sum of Number of trips")
```

#### metier lvl5 and country
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=7,fig.height=7}
#data prep
sub_ce_2 <- ce%>%
  filter(CEvesselLengthCategory %in% c("VL1012", "VL1215", "VL1518","VL1824","VL2440","VL40XX"))%>%
    mutate(CEmetier5 = substr(CEmetier6, 1, 7))%>%
  group_by(CEyear, CEmetier5, CEvesselFlagCountry) %>%
  summarise(CEnumberOfDominantTrips_total = sum(CEnumberOfDominantTrips))

sub_ce_top$Top <- "TOP"
sub_ce_2_top <- left_join(sub_ce_2,sub_ce_top,by="CEmetier5")

sub_ce_2_top <- sub_ce_2_top %>%
  filter(Top=='TOP')

barplot(data = sub_ce_2_top, 
      x = "CEmetier5",
      y = "CEnumberOfDominantTrips",
      group = "CEvesselFlagCountry",
      title = "Number of trips by Metier Lvl5 and Country",
      ylab = "Proportion of Number of trips",
      asPct = T)

```

#### statistical rectangle

## Effort by harbour
### Below 10 meters {.tabset}
#### harbour
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=7,fig.height=7}
#data prep
sub_ce_top <- ce%>%
  filter(CEvesselLengthCategory %in% c("VL0006", "VL0608", "VL0810"))%>%
  group_by(CEyear, CElandingLocation) %>%
  summarise(CEnumberOfDominantTrips = sum(CEnumberOfDominantTrips)) %>%
  top_n(20)

barplot(data = sub_ce_top,
      x = "CElandingLocation",
      y = "CEnumberOfDominantTrips",
      title = "Number of trips by Harbours",
      ylab = "Sum of Number of trips")
```

#### harbour and country
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=7,fig.height=7}
#data prep
sub_ce_2 <- ce%>%
  filter(CEvesselLengthCategory %in% c("VL0006", "VL0608", "VL0810"))%>%
  group_by(CEyear, CElandingLocation, CEvesselFlagCountry) %>%
  summarise(CEnumberOfDominantTrips_total = sum(CEnumberOfDominantTrips))

sub_ce_top$Top <- "TOP"
sub_ce_2_top <- left_join(sub_ce_2,sub_ce_top,by="CElandingLocation")

sub_ce_2_top <- sub_ce_2_top %>%
  filter(Top=='TOP')

barplot(data = sub_ce_2_top, 
      x = "CElandingLocation",
      y = "CEnumberOfDominantTrips",
      group = "CEvesselFlagCountry",
      title = "Number of trips by Harbours and Country",
      ylab = "Proportion of Number of trips",
      asPct = T)

```

#### map - harbour

### 10 meteres and above {.tabset}
#### harbour
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=7,fig.height=7}
#data prep
sub_ce_top <- ce%>%
  filter(CEvesselLengthCategory %in% c("VL1012", "VL1215", "VL1518","VL1824","VL2440","VL40XX"))%>%
  group_by(CEyear, CElandingLocation) %>%
  summarise(CEnumberOfDominantTrips = sum(CEnumberOfDominantTrips)) %>%
  top_n(20)

barplot(data = sub_ce_top,
      x = "CElandingLocation",
      y = "CEnumberOfDominantTrips",
      title = "Number of trips by Harbours",
      ylab = "Sum of Number of trips")
```

#### harbour and country
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=7,fig.height=7}
#data prep
sub_ce_2 <- ce%>%
  filter(CEvesselLengthCategory %in% c("VL1012", "VL1215", "VL1518","VL1824","VL2440","VL40XX"))%>%
  group_by(CEyear, CElandingLocation, CEvesselFlagCountry) %>%
  summarise(CEnumberOfDominantTrips_total = sum(CEnumberOfDominantTrips))

sub_ce_top$Top <- "TOP"
sub_ce_2_top <- left_join(sub_ce_2,sub_ce_top,by="CElandingLocation")

sub_ce_2_top <- sub_ce_2_top %>%
  filter(Top=='TOP')

barplot(data = sub_ce_2_top, 
      x = "CElandingLocation",
      y = "CEnumberOfDominantTrips",
      group = "CEvesselFlagCountry",
      title = "Number of trips by Harbours and Country",
      ylab = "Proportion of Number of trips",
      asPct = T)

```

#### map - harbour

## Spatal distribution on effort {.tabset}
### Below 10 meters

```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6}
# data prep
ce %>%
  filter(CEvesselLengthCategory %in% c("VL0006", "VL0608", "VL0810")) %>% 
  group_by(CEyear, CEstatisticalRectangle) %>%
  summarise(CEnumberOfDominantTrips = sum(CEnumberOfDominantTrips)) %>%
  mutate(pr= CEnumberOfDominantTrips/sum(CEnumberOfDominantTrips, na.rm = TRUE)*100,
         analysis_type = 'sum',
         type_of_threshold = 'none',
         value_of_threshold = NA)-> df

# map
result = choroplethMap_func2(
  df,
  var_name = 'CEnumberOfDominantTrips',
  var_spatial_name = 'CEstatisticalRectangle',
  facet_name = 'CEyear',
  spatial_dataset_name = 'StatRectshp',
  spatial_dataset_var_name = 'ICESNAME',
  spatial_dataset_labels = FALSE,
  saveResults = FALSE,
  outputPath,
  displayInR = TRUE,
  extraShp_name = 'FAOshp',
  var_name_new = NA,
  addToTitle = 'Below 10 meters',
  RCGregion = 'BA'
)

result[[1]]
```

### 10 meters and above

```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6}
# data prep
ce %>%
  filter(CEvesselLengthCategory %in% c("VL1012", "VL1215", "VL1518","VL1824","VL2440","VL40XX")) %>% 
  group_by(CEyear, CEstatisticalRectangle) %>%
  summarise(CEnumberOfDominantTrips = sum(CEnumberOfDominantTrips)) %>%
  mutate(pr= CEnumberOfDominantTrips/sum(CEnumberOfDominantTrips, na.rm = TRUE)*100,
         analysis_type = 'sum',
         type_of_threshold = 'none',
         value_of_threshold = NA)-> df

# map
result = choroplethMap_func2(
  df,
  var_name = 'CEnumberOfDominantTrips',
  var_spatial_name = 'CEstatisticalRectangle',
  facet_name = 'CEyear',
  spatial_dataset_name = 'StatRectshp',
  spatial_dataset_var_name = 'ICESNAME',
  spatial_dataset_labels = FALSE,
  saveResults = FALSE,
  outputPath,
  displayInR = TRUE,
  extraShp_name = 'FAOshp',
  var_name_new = NA,
  addToTitle = '10 meters and above',
  RCGregion = 'BA'
)

result[[1]]
```

## Appendix A. Dates of data extraction
## Appendix B. Catch groups
```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", dpi=100, fig.width=6,fig.height=6}
# data prep
cl%>%
  mutate(Region = params$region,
         CLyear = as.factor(CLyear))%>%
  group_by(Region,CLyear,SpeciesLaName,CatchGroup)%>%
  summarise(CLscientificWeight_ton_total=sum(CLscientificWeight_ton))%>%
  mutate(CLscientificWeight_ton_total = round(CLscientificWeight_ton_total,0))%>%
  arrange(CatchGroup,SpeciesLaName, .locale = 'en')%>%
  rename(Period = CLyear,
         Species = SpeciesLaName,
         `Catch group` = CatchGroup,
         `Landings (t)` = CLscientificWeight_ton_total) -> df

  ft <- flextable(df)
  ft <- fontsize(ft, part = "all", size = 8)
  ft <- bold(ft,part="header")
  
  autofit(ft)
```

## Appendix C. Mean Landings per stock, put years here
## Appendix D. Summary information of the landings abroad (ton), by country and area
## Appendix E. Glossary for the country codes

